### 2023-01-31 template/gusample.tex
Added template

% File 'gusample.tex' -- Mark Maloof, Michael A. Covington, Isidor Ruderfer
% (Revised 15 December 2010)
% This is an example of how to format a thesis or dissertation using LaTeX 2e
% with 'guthesis.sty' VERSION 3.4 OR LATER.

\documentclass[12pt]{report}

\usepackage{url}
\usepackage[numbers,sort]{natbib}
\usepackage[dvips]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}

% If there are any other \usepackage commands, put them here.

\usepackage{guthesis} % Must be the last package

\newtheorem{theorem}{Theorem}[section]
\newenvironment{proof}[0]{\textit{Proof.}}{}
\newcommand{\qed}{\hfill $\Box$}

% To comment out multiple lines of text.
\long\def\comment#1{}

\title{Example of a Thesis \\
       Formatted with LaTeX \\
       Using the Georgetown University \\
       Style Macro Package, Version \guthesisversion}

\author{Marcus A. Maloof}

\previousdegree{B.S.}

\thisdegree{Master of Science}  % or Doctor of Philosophy, etc.

\thisdiscipline{Computer Science}

\thesistype{Thesis}     % or Dissertation

% defense or approval date, not today's date...
\thesisday{15}
\thesismonth{December}
\thesisyear{2010}

\professor{Abraham Baldwin}
%\secondprofessor{Alonzo Church}   % Only if you have 2 major professors!

\fulltitle{Example of a Thesis Formatted with LaTeX Using the Georgetown
           University Style Macro Package, Version \gustyversion}

\indexwords{Word~processing, Computer~typesetting, Computer~graphics,
            Style~sheets, Typography, Dissertations, Theses~(academic)}

\dean{Timothy A.\ Barbari}

\memberi{Benjamin Franklin}
\memberii{Isaac Newton}
% Use \memberiii, \memberiv, \memberv for up to 3 more members if needed.

\begin{document}

\pagenumbering{roman}

\maketitle    % Creates title page, copyright page if any, and approval page.

\begin{abstract}
This is the abstract, a brief summary of the contents of the entire thesis.
It is limited to 350 words.

The abstract page(s) are not numbered and are not necessarily included
in the bound copies.  Likewise, the signature page is not counted in
page numbering because not all copies contain it.

Throughout this sample thesis, {\bf please note
that the layout obtained with \LaTeX\ is not meant to be a
perfect duplicate of the Microsoft Word examples in the \emph{Graduate
School Style Manual.}}  \LaTeX\ has additional typographic tools at its
disposal, such as {\sc small capitals} and various subtle adjustments
of spacing, which are used by the Georgetown \LaTeX\ style sheet in
accordance with the standard practices of the book-printing industry.

The index words at the bottom of the abstract should be chosen carefully,
preferably with the help of one or two of your colleagues.
They are the words by which people will find your thesis when searching
the scientific literature.
If you want to get credit for your ideas, be sure to choose a good set of
index words so that people doing related work will know about yours.
\end{abstract}

\chapter*{Dedication}

The Dedication is optional, but if it is included, it should have
a roman numeral page number but not be included in the table of
contents.  To achieve that, we declare it as a \verb"\chapter*" in \LaTeX.

\pseudochapter{Acknowledgments}

In a real thesis, this section would contain acknowledgments such
as, ``This work was funded by National Science Foundation Grant
Number AAA-00-00000 (Benjamin Franklin, Principal Investigator),''
and ``I would like to thank John Doe for helping me proofread my
thesis and Mary Roe for drawing my graphs.''

The acknowledgments are included in the table of contents but do
not have a chapter number.  To achieve that, we
declare them to be a \verb"\pseudochapter" (which is defined only in
\verb"guthesis.sty").

I (Mark Maloof) would like to thank Michael Covington for developing
this \LaTeX\ style sheet for the University of Georgia.
Zachary Hunter deserves special thanks for revising the UGA style
file to work with the new version of \LaTeX\ (2e) as well as the
previous version (2.09).
The revisions in
Version 3.0 of \verb"guthesis.sty" are
largely the work of Isidor Ruderfer.
Other credits appear in the style sheet itself.

\pseudochapter{Preface}

If your thesis has a preface, this is where it goes.
A preface is not an introduction, and most theses do not need them.

\tableofcontents

\listoffigures  % Optional - Omit this line if you don't want a list of figures.
\listoftables   % Optional - Omit this line if you don't want a list of tables.

\newpage

\pagenumbering{arabic}  % Ordinary pages have Arabic numerals.

\chapter{What \LaTeX\ is all about}

This document is an example of how to format a thesis or dissertation
using \LaTeX\  and get results acceptable at Georgetown University.

\LaTeX\ (with its parent \TeX)
has two major advantages for academic use.  First, to a remarkable
degree it makes design decisions automatically.  The author supplies
only the words of a text, and \LaTeX\ places them on the page in an
aesthetic manner, avoiding rivers and awkward breaks.  In this respect
LaTeX is like a very intelligent typist or typesetter.

Second, \LaTeX\ can typeset complex mathematical formulas such as
\[
\sum_{i=1}^{\infty} x^{y+z} = \frac{p+q+r}{s+t+u+v}
\]
both displayed (as shown above) and in the text, as in
$\sum_{i=1}^{\infty} x^{y+z} = \frac{p+q+r}{s+t+u+v}$.
This makes \TeX\ and \LaTeX\ indispensable for mathematicians, physicists,
and the like.

LaTeX also has built--in formats for other kinds of displayed material
such as verse,
\begin{verse}
Freude, sch\"{o}ne G\"{o}tterfunken  \\
Tochter aus Elysium,                 \\
Wir betreten, feuertrunken,          \\
Himmlische, dein Heiligum!          \\
Deine Zauber binden wieder            \\
Was der Mode streng geteilt\dots
\end{verse}
and direct quotations:
\begin{quote}
The society that scorns excellence in plumbing, because plumbing is a
humble activity, and tolerates shoddiness in philosophy, because
philosophy is an exalted activity, will have neither good plumbing nor
good philosophy.  Neither its pipes nor its theories will hold water.\\
\hspace*{\fill} --- John Gardner, {\em Excellence}
\end{quote}
If you wish, quotes and other displayed material can be single--spaced;
here is an example of how that is achieved:
\begin{verse}
\begin{singlespace}
Yes, I wrote ``The Purple Cow.'' \\
I'm sorry now I wrote it. \\
But I can tell you anyhow \\
I'll kill you if you quote it! \\
\hfill --- Anonymous?
\end{singlespace}
\end{verse}
Well, maybe it's not as anonymous as it looks.

Computer scientists use LaTeX's ``verbatim'' format to display portions
of computer programs in text, like this:
\begin{verbatim}
1   GO TO 2
2   GO TO 1
3   PRINT "THIS STATEMENT WILL NEVER EXECUTE"
4   END
\end{verbatim}
There you have it.%
\footnote{This is a footnote. Notice that footnotes are single--spaced
even though the text is double--spaced. Long footnotes are discouraged;
either make important points in the text or leave them out.}

Whenever you quote parts of a computer program in English text, they
should be set off by using typewriter type.  The \verb"PRINT" statement
in the program above will never execute because the \verb"GO TO"
statement above it keeps execution from reaching it.

\chapter{Five Important Notes}

\section{\LaTeX\ is not a typewriter --- nor an ordinary word processor}

\emph{The format that you get with \LaTeX\ is more elegant
than the simpler format in the Graduate School style manual and is not
intended to match it perfectly.}

\LaTeX\ makes available to you \emph{all} of the tools of fine book printing.
For example, \LaTeX\ has more degrees of
vertical spacing available than other word processors do, and it uses them
effectively.  Likewise, \LaTeX\ provides {\sc Small Capitals} for situations
where other software would only provide ALL CAPITALS.

The format produced by \verb"guthesis.sty" has been reviewed by the Graduate School.
If your thesis fails the format check, make sure you have followed the
instructions for \verb"guthesis.sty" (contained in the file \verb"gusample.tex")
and the instructions for \LaTeX.

\section{You can't do without the book!}

\emph{You are not expected to be able to use \LaTeX\ without a manual.}
Don't even try --- you'll waste a lot of time.
The definitive manual for \LaTeX\ is:
\begin{quote}
Lamport, Leslie (1994) \emph{\LaTeX: A Document Preparation System.}
2nd ed.
Reading, MA: Addison-Wesley.
\end{quote}
Alternatively, there is a good manual available on line whose author is
named Oetiker.
There are several versions.  Use a search engine to search for
``LaTeX Oetiker'' and you'll find it.

\section{The {\tt guthesis.sty} style sheet adds to \LaTeX\ but does not replace it}

``How do I do so-and-so in \verb"guthesis.sty"?''  Almost always the same way as
in plain \LaTeX.
The Georgetown University style sheet, called \verb"guthesis.sty", adds features
to \LaTeX; it does not take away what is already there.

\section{Ragged right margins are optional}

{\raggedright
\parindent 0.25in
This section is typeset in ``ragged right'' format, in which \LaTeX\ has
been told not to force a straight right margin.

``Ragged right'' is preferable if your thesis contains a large number of
words likely to be hyphenated incorrectly, formulas, web addresses, or
the like.  To get it, put the two lines
\begin{verbatim}
\raggedright
\parindent 0.25pt
\end{verbatim}
anywhere after the {\tt documentclass} command and before
\verb"\begin{document}".

You can also reduce the amount of hyphenation, without eliminating it
totally, by following the instructions in the \LaTeX\ manual.
} % raggedright

\section{Please let \LaTeX\ do the layout...}

Please do not use \verb"\vspace", \verb"\hspace", and other \TeX\ commands
that specify the precise location or spacing of items on the page.
Leave the layout to \LaTeX\ and \verb"guthesis.sty".
Otherwise, very ugly things can happen.

Your thesis is like a volume in a series.
It should look like the other theses and dissertations that were typeset
using the same technology.
Just as different volumes of the \emph{Encyclopaedia Britannica} have exactly
the same margins and typography, so should different theses from the same
university, as far as technology permits.

\section{Please use floating figures and tables...}

Please use the \verb"figure" and \verb"table" environments for your figures
and tables.
A picture or table should not interrupt the text the way a mathematical
formula does.
Instead, it should ``float'' to the nearest convenient location---which
\LaTeX\ will take care of automatically---and should be identified by
number.

\chapter{Frequently Asked Questions About Typing Georgetown Theses with
\LaTeX\ and {\tt guthesis.sty}}

\section{\LaTeX\ itself}

\subsection{What is \LaTeX?}

\LaTeX, by Leslie Lamport, is an extension of \TeX, the computer typesetting
system designed by Donald Knuth.  This software system is used to typeset
books, journals, papers, and theses in the mathematical sciences.
Knuth and Lamport had two goals in designing it:
\begin{itemize}
\item To use the computer to equal the quality of the best conventional
typesetting.
No longer does ``word processing'' mean ``a poor substitute for real
printing.''
\item To separate the jobs of the \emph{author} and the \emph{typesetter.}
\end{itemize}
Other word processors turn the screen into a blank piece of paper and let
you type on it.  \LaTeX\ is not your \emph{typewriter,} it's your
\emph{typist.}  For example, to mark the beginning of a chapter, you
type something like this:
\begin{verbatim}
\chapter{Literature Review}
\end{verbatim}
and \LaTeX\ automatically determines what a chapter heading should look like.
It does this by consulting a \emph{style sheet.}  You do not have to worry
about whether you've hit Enter the same number of times at the beginning of
each chapter, or whether all the chapter headings are centered and the
margins are correct.  That's the (automated) typist's job.

\subsection{How is ``\LaTeX'' pronounced?}

The X in \TeX\ is actually a Greek chi, with the sound of \emph{ch} in
Scottish \emph{loch} or German \emph{ach}.  Thus, \TeX\ is pronounced
``tekh.''  It is short for Greek \emph{tekhn\={e}} ``art, craft.''

\LaTeX\ is pronounced \emph``lah-tekh'' in the Northeast, \emph``lay-tekh''
in England and the South, and several different ways in the West.

\subsection{What's it like to run \LaTeX?}

\LaTeX\ is \emph{not} a single integrated piece of software.  It has several
parts.  The normal process for typing and printing a paper is as follows.
On finding an error or discovering that a change is needed, you can go back
to any earlier step at any time.
\begin{enumerate}
\item Use a text editor (Windows Notepad or whatever text editor you like)
to type your document on a file whose name ends in {\.tex}.
\item Go to a command prompt and run {\tt latex} to create a {\tt .dvi} file.
\item Optionally, preview the {\tt .dvi} file on-screen.  Some of us skip
this step.
\item Run {\tt dvipdf} to convert the {\tt .dvi} file to PDF.
\item Use Adobe Reader to view the PDF file and print it, if desired.
\end{enumerate}

\subsection{Who benefits the most from using \LaTeX?}

Those who need to typeset mathematical formulas or computer programs;
those whose theses are likely to be published
by a book publisher; and those who plan to submit their theses electronically.

\subsection{Who should \emph{not} use \LaTeX?}

If you consider yourself a ``computer dummy'' and can use only the simplest
software, or if you do not have the time or patience to learn a new set of
technical skills, you won't like \LaTeX.  On the other hand, you probably
will not type your thesis correctly with a conventional word processor
either.  (Let's face it, typing a thesis correctly is a technical challenge,
no matter what software you do it with!)  You should hire a typist.

\section{\LaTeX\ versions}

\subsection{What are Mik\TeX, em\TeX, te\TeX, etc.?}

These are implementations of \LaTeX\ for particular computers, incorporating
Knuth and Lamport's original computer programs plus various tools to make
them easier to use or more versatile.
All of them are 100\% compatible with the original \LaTeX.

\subsection{Is there \LaTeX\ for Macintosh, Linux, Amiga, Sun, BeBox...?}

Yes.  \LaTeX\ has been ported to a huge variety of computers and produces
\emph{identical} output on all of them, using \emph{identical} file formats.
If you have Linux, you almost certainly already have \LaTeX.

\subsection{What is \LaTeXe?}

The version of \LaTeX\ that has been in use for the last several years.
It was preceded by \LaTeX\ 2.09.  Those are the only two version of
\LaTeX\ that have been distributed widely.  There will eventually be
a \LaTeX\ 3, but not very soon.

\subsection{Where do I get \LaTeX?}

You can download it free of charge from various sites;
Be careful about Googling \LaTeX.
It's best to go to the \TeX\ Users Group web site:
\url{http://www.tug.org}.

\subsection{Where is the documentation for \LaTeX?}

In the book \emph{LaTeX: A Document Preparation System,} by Leslie Lamport,
2nd edition, published by Addison-Wesley.  \textbf{You must buy this book.}
Other books about \LaTeX\ are useful but are not the official guide.

\subsection{Where can I get help with \LaTeX?}

First, read Lamport's book.  \emph{You cannot get along without it.}

Second, you can ask questions on the newsgroups {\tt comp.text.tex}
(international).

Third, if you have problems that are specific to {\tt guthesis.sty},
and particularly if {\tt guthesis.sty} does not appear to be meeting
Georgetown's thesis format requirements, please contact me
(Mark Maloof, maloof@cs.georgetown.edu).

\section{The Georgetown University style sheet}

\subsection{What is {\tt guthesis.sty}?}

A style sheet for \LaTeX\ that makes it follow the format for
Georgetown University theses and dissertations.

\subsection{Where do I get {\tt guthesis.sty} and how do I install it?}

Download it from \texttt{http://www.cs.georgetown.edu/academics/guthesis.zip}.

Install it by putting it in the same directory as your thesis, or in
directory {\tt texmf/tex/latex} of your \TeX\ system.

\subsection{How do I use {\tt guthesis.sty}?}

For a quick summary, see Fig.\ \ref{gutemplate}.
For details, see the file {\tt gusample.tex}.
For a skeleton document, see the file {\tt template.tex}.

\begin{figure}
\begin{center}
\begin{minipage}{5in}
\tiny
\begin{verbatim}
     \documentclass[12pt]{report}
     \usepackage{guthesis}

     % The following 2 lines are OPTIONAL to turn off all hypenation
     % and print with "ragged" right margins
     \raggedright
     \parindent 0.25in

     \title{Title of Thesis \\
            Broken into Lines \\
            As Appropriate}

     \fulltitle{Title of Thesis Not Broken Into Lines}

     \author{Your Name Here}

     \previousdegree{B.A., Name of University, 1977 \\
                     M.S., Some Other University, 1978}

     \thisdegree{Master of Science} % or Doctor of Philosophy, etc.
     \thesistype{Thesis}        % or Dissertation
     \thesisday{5}              % put the day of defense or approval here...
     \thesismonth{May}          % put the month of defense or approval here...
     \thesisyear{2005}          % put the year of defense or approval here...

     \indexwords{keywords for indexing your thesis in library catalogs}

     \professor{Abraham Baldwin}     % Major Professor
     \secondprofessor{Alonzo Church} % Co-Major Professor if you have one
     \memberi{Benjamin Franklin}     % Committee member
     \memberii{Isaac Newton}         % Committee member
     % Use \memberiii, \memberiv, \memberv for up to 3 more members if needed.

     \dean{Timothy A.\ Barbari}       % Dean of the Graduate School

     \begin{document}
     \pagenumbering{roman}   % Use Roman numerals until chapters start.

     \begin{abstract}
     Text of abstract goes here.
     \end{abstract}

     \maketitle    % Creates title page, copyright page if any, and approval page.

     \chapter*{Dedication}
     Dedication, if any, goes here.
     It is a "\chapter*" so it is not in the table of contents.

     \pseudochapter{Acknowledgments}
     Text of acknowledgments goes here.
     It is a "\pseudochapter" so it goes in the table of contents but has no chapter number.

     \tableofcontents
     \listoffigures   % Optional - Omit this line if you don't want a list of figures.
     \listoftables    % Optional - Omit this line if you don't want a list of tables.

     \newpage
     \pagenumbering{arabic}  % Ordinary pages have Arabic numerals.

     \chapter{Title of Chapter Goes Here}
     Text of first chapter goes here.

     \chapter{Title of Chapter Goes Here}
     Text of second chapter goes here.

     \appendices  % Indicates that appendices follow.  If there's only one, use \appendix instead.

     \chapter{Title of First Appendix}
     Text of first appendix goes here.

     \chapter{Title of Second Appendix}
     Text of second appendix goes here.

     \bibliographystyle{plainnat}
     \bibliography{thesis}  % Pulls entries from thesis.bib

     \end{document}
\end{verbatim}
\end{minipage}
\end{center}
\caption{Template for formatting a thesis with {\tt guthesis.sty}.}
\label{gutemplate}
\end{figure}

\subsection{Do I have to get {\tt guthesis.sty} before typing my thesis?}

No.  You can type your thesis using the \LaTeX\ {\tt report} documentclass
(described in Lamport's book); this will enable you to produce neat,
single-spaced copies of the work in progress.  When it's finished, get
{\tt guthesis.sty} and make the small additions to your thesis that are described
there.

\subsection{What are the required parts of a thesis typed with {\tt guthesis.sty}?}

They are described in {\tt guthesis.sty} itself, which you can read with your
text editor.
Alternatively, you can use {\tt gusample.tex} as sample to imitate.

\section{Troubleshooting}

\subsection{Why is the text too high or low on the page?}

See Appendix A, p.\ \pageref{mgins}.

\subsection{Why is there a space before a footnote number?}

If your footnote numbers come out positioned like this $^8$ rather than
this$^8$, it's because you're leaving a space before the
\verb.\footnote. command.
\begin{verbatim}
Type like this.\footnote{Here's the note.}
Not like this. \footnote{Here's the note.}
\end{verbatim}
A useful trick is to put \verb"%" at the end of one line (to comment out
all the remaining blank space) and then \verb"\footnote" at the beginning
of the next line.

\subsection{Why is my table of contents blank or incorrect?}

You must run \LaTeX\ twice in order to get a correct table of contents.
The first time, it keeps records of where things are; the second time,
it actually generates the table of contents.  If the table of contents
is long, you may need to run \LaTeX\ three times to ensure that adequate
space is left for it.

\subsection{Why is there too much space after some of the periods?}

\LaTeX\ normally assumes that every period marks the end of a sentence,
so it leaves extra space after it.  You should normally use a required
space (\verb.~.) after every period that does not mark the end of a sentence.
Type ``\verb"T.~S.~Eliot"'' to print ``T.~S.~Eliot'' or the like.

Beginning with {\tt guthesis.sty} version 2.0 (December 2001), this is no longer
a problem because {\tt guthesis.sty} tells \LaTeX\ not to treat periods specially;
the same amount of space follows each word whether or not it ends with a
period.  This is known as ``French spacing'' and is an accepted practice
in the printing industry.

\subsection{Why do some words hang out past the right margin?}

When \LaTeX\ cannot break a line satisfactorily, it leaves a word sticking
out into the margin and gives you an ``Overfull hbox'' error message.
It is up to you to rearrange the text so that it fits.

\subsection{What is an overfull hbox?}

See previous question.

\subsection{What is a ``Package hyperref warning''?}

Most people now use the \verb"hyperref" package to generate hyperlinks to
their chapters and sections in the eventual PDF output.

This is good, but \verb"hyperref" complains violently if there is anything
other than plain text in a section title.
It also complains if you use \verb"\pseudochapter".
Just ignore the warnings.

\section{Character set and typography}

\subsection{How do I type a percent sign?}

See Lamport's book.  A quick answer:  Type ``\verb.\%.''.

\subsection{How do I type a tilde ($\sim$)?}

This character often occurs in web addresses.
In \LaTeX, when you type ``\verb.~.'' you get a blank.
(Specifically, you get a ``required space,'' a space that cannot be
broken across a line break.)
To get ``$\sim$'' type ``\verb.$\sim$.''.
Also see the {\tt url} package, which lets you write
\verb|\url{http://www.cs.georgetown.edu/~maloof}|, typeset as
\url{http://www.cs.georgetown.edu/~maloof}.

\subsection{What are \textit{italics} used for?}

All of the things that would be underlined in a handwritten document,
including titles of books, foreign words, and the like.

In linguistics, it is normal to put foreign words in italics and their
definitions in single quotes.  For example, Agatha Christie's famous
detective is named after the French word \emph{poireau} `leek'.

\subsection{What is \underline{underlining} used for?}

Almost nothing.  Roman type is not normally underlined; use italics instead.

\subsection{What is \mbox{\tt typewriter} \mbox{\tt type} used for?}

Computer program languages, whether displayed or quoted in text.  For
example, here is part of a program written in C:
\begin{verbatim}
for ( i = 100; i > 0; i-- ) {
   printf("%d bottles of beer on the wall...\n", i);
}
\end{verbatim}
It demonstrates how to use the \verb"for" statement to count down from
100 to 1.

\subsection{What is the \mbox{\tt verbatim} environment used for?}

Computer programs, as just demonstrated.

\subsection{What is \mbox{\sf sans-serif type} used for?}

Almost nothing except labels within illustrations.

\section{Bibliographies}

\subsection{How do I type the bibliography?}

See Lamport's book \cite{lamport.94}
and the examples in {\tt gusample.tex}.
\LaTeX\ lets you refer to bibliography items in your text
with markers such as
\verb|\cite{lamport.94}|.
then have \LaTeX\ automatically turn these into bracketed numbers in
the bibliography.

With {\tt guthesis.sty}, simply use the \verb.thebibliography. environment
exactly as Lamport describes it.  This will produce a bibliography in
the form of an unnumbered chapter at the end of your thesis.

\subsection{What if each chapter has its own bibliography?}

If you have bibliographies at the ends of the individual chapters, use the
environment {\tt chapterbibliography} instead of {\tt thebibliography}.
It works \emph{exactly} the same way except that the bibliography
becomes a normally numbered section, not an unnumbered chapter.
There is an example of this in {\tt gusample.tex}.

The {\tt chapterbibliography} environment is provided by {\tt guthesis.sty}.

\subsection{What if I don't like bracketed numbers?}

Here is an example of a trick to get \LaTeX\ to print a bibliography without
bracketed numbers.  Basically, you are telling \LaTeX\ to put the author's
name in place of the bracketed number.  Note that this involves using
\verb.\item. rather than \verb.\bibitem..
\begin{verbatim}
\begin{thebibliography}{}

\item[Covington, Michael A.]
\emph{Natural Language Processing for Prolog Programmers.}
Englewood Cliffs, N.J.: Prentice Hall, 1994.

\item[O'Keefe, Richard A.]
\emph{The Craft of Prolog.}
Cambridge, MA: MIT Press, 1991.

\end{thebibliography}
\end{verbatim}
When doing this,
don't use the \verb"\cite" command; instead, handle your references manually.
You can do \emph{exactly} the same thing with \texttt{chapterbibliography}.

\section{Layout and illustrations}

\subsection{How do I turn off justification?}

Justification means printing with a straight right margins.  It is not required
for Georgetown University theses, and if your text contains many formulas, web
addresses, or other unbreakable items, you may get considerably neater results
by turning it off.  To do this, issue the command
\begin{verbatim}
\raggedright
\end{verbatim}
immediately after \verb.\begin{document}..

You may need to turn off justification only within a bibliography.
In that case, you should put the \verb.\raggedright. command right after
\verb.\begin{thebibliography}.
or right after
\verb.\begin{chapterbibliography}.
as the case may be.  It will then affect only the bibliography.

\subsection{How do I put a picture into my thesis?}

See Lamport's book.  Here's the basic process...
\begin{enumerate}

\item Learn the difference between a vector (``draw'') program and a bitmap
(``paint'') program.  Vector programs,
such as xfig, OpenOffice Draw, Corel Draw, and Micrografx Windows Draw,
tell the computer to draw lines at particular positions;
they are the right tool for generating diagrams of all types.  Bitmap
programs are \emph{only} for working with digitized photographs and the
like; their output has an unpleasant stairstep appearance when enlarged
or resized.

\item Produce professional-quality artwork.  (You may want to hire a
professional illustrator.)
Artwork in your thesis should look as good as the artwork in published books.

\item Save your artwork as an encapsulated PostScript (EPS) file
\emph{with no TIFF header}.
(The drawing software may ask you whether you want a TIFF header; say no.)

\item Use the \texttt{graphics} package (described in Lamport's book) or the
\texttt{epsf} package to incorporate your art into your \LaTeX\ document.
One way to do this is as follows:
\begin{enumerate}
\item Add the command \verb.\usepackage{graphicx}. right after
\verb.\documentclass..
\item Use the command \verb"\centerline{\includegraphics{xxxxxxx.eps}}"
(with the appropriate filename substituted) to put the picture in your
document.  Normally this will be within a \verb.figure. environment as
described in Lamport's book.
\end{enumerate}
\end{enumerate}

\subsection{How do I put a Windows screen shot into my thesis?}

When writing about software, you many need a picture of the computer screen
with a program running.
Under Windows 95 and up, you can ``take a picture'' of the screen, by
pressing Print Screen
(or Alt-Print Screen if you only need the current window).
This puts a copy of the screen into the Windows clipboard.  Then open up
your favorite paint program (bitmap program) and choose Paste.  Edit
the picture to your satisfaction, save it, and export it as encapsulated
PostScript.  For the rest of the process, see the previous question.

\chapter{The Craft of Scholarly Typing}

\section{An exhortation}

If you have come to the University for a graduate degree, scholarly writing
is one of the crafts
in which you are being trained.
This includes scholarly typing and word processing.
We assume that you will be writing about your subject for the rest of your
life.
This is more likely to be true than you realize.

\LaTeX\ provides you with all the tools of fine book printing.
This includes quite a few things that were not available on typewriters.
Accordingly, when using \LaTeX, you must learn some new things about printed
language.

\section{Some common punctuation errors}

\subsection{Hyphens and dashes}

\LaTeX\ distinguishes four kinds of horizontal lines between characters.

\begin{itemize}
\item The minus sign, $-$ (typed \verb"$-$"),
is used only in math mode.  Always go into math mode when you want to mark
a number as negative.

\item The hyphen, - (typed \verb"-"), is used between parts of a word, as in
``so-called'' or ``heavy-handed.''

\item The short dash (en dash), -- (typed \verb"--"), goes between numbers
in sequences, as in ``1861--65.''

\item The long dash (em dash), --- (typed \verb"---"), goes between parts
of sentences and may be set off by spaces --- like this.
In good writing, it is uncommon; as alternatives, consider using a semicolon
or starting a new sentence.
\end{itemize}

\subsection{Quotation marks}

In \LaTeX\, you must type your quotation marks \verb"``like this''" in order
to get them to print correctly ``like this.''  It is not correct to type
"like this."

Periods and commas ``slide under'' quotation marks so that they adhere to
the words within them.
Correct usage looks ``like this.''  Incorrect usage looks ``like this''.

In computer science and linguistics, this rule sometimes does not apply,
because it may be important to show that the period or comma is not part
of the quoted material.  If you cannot get around this by rearranging the
sentence, it is acceptable to put the period or comma outside the quotes.

Single quotation marks (`like this') are used in linguistics to give the
meanings of words.  Thus, French \emph{chateau} `castle' comes from Latin
\emph{castellum} `fortress.'

\subsection{Punctuation around mathematical formulae}

Do not let the punctuation of your sentence intrude into a displayed
mathematical formula.
When a sentence ends with a displayed formula, end the sentence with a colon.
Thus we conclude:
\[
a = \sum_{x=1}^\infty p(x) = q(x)
\]
The formula does not end with a period.

\section{Knowing the character set}

Part of knowing your subject is knowing its notation.
If you are vague on the difference between $\emptyset$ and $\phi$, or
$\omega$ and $w$, consult some well-produced reference books
(not scruffily typed conference papers).

Remember that in good printing, \emph{underlining is almost never used.}
Underlining is the handwritten way of indicating italics.
Now that you have italics, use them.
Instead of wavy underlining (for vectors, etc.), use boldface.

\section{Figures and tables}

In a well-produced book, figures and tables do not interrupt the text like
mathematical formulae.
Instead, they ``float'' to the nearest convenient location and are identified
by number.
If there is no convenient place at the top or bottom of a page, they are
placed on a separate page.

\emph{See Lamport's book to learn how to control the placement of figures
and tables.}
Nothing is added or changed by {\tt guthesis.sty} --- \LaTeX\ still works exactly
the way Lamport says.

\begin{figure}
\begin{center}
\framebox{A picture could go here.}
\end{center}
\caption{This is an example of a figure.}
\label{myfig}
\end{figure}

\begin{figure}
\begin{center}
\framebox{A picture could go here.}
\end{center}
\caption{This is another example of a figure.}
\label{myfigtwo}
\end{figure}

Near here, you will see Figures~\ref{myfig} and~\ref{myfigtwo}.  Note that
each picture's caption comes below it.  That is achieved by putting
the \verb"\caption" command \emph{after} the figure.

\begin{table}
\caption{Some institutions and their mascots.}
\label{mytb}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
\bf Institution & \bf Location & \bf Mascot \\
\hline
University of Georgia  & Athens & Bulldawg \\
Georgetown University  & Washington  & Bulldog \\
Georgia Tech  & Atlanta  & Insect \\
UCSC  &  Santa Cruz  & Banana Slug\\
\hline
\end{tabular}
\end{center}
\end{table}

Near here, you will also see Table~\ref{mytb}.  Its caption
comes above it.  This is achieved by putting
the \verb"\caption" command \emph{before} the table.

\chapter{More Nonsense about \LaTeX}

In this chapter, we talk about more \LaTeX\ things.
Suspendisse potenti. Proin justo lorem, rutrum ac, facilisis in,
malesuada sed, ligula. Mauris lobortis lacus at nibh. Aenean vitae
odio vel odio placerat hendrerit. Suspendisse lacus lacus, tempor id,
pharetra eget, ornare sit amet, pede. Sed aliquet, justo ac elementum
pretium, arcu leo placerat est, a luctus purus diam eget arcu. Nam
augue diam, mollis a, scelerisque eget, aliquet condimentum, pede.
Vestibulum tristique lectus sed augue.

\section{Introduction}\label{sec:intro}

Aenean ut mauris luctus mauris interdum convallis. Nunc vestibulum
sodales nulla. Nulla vitae massa. Maecenas vel tellus vitae elit mattis
adipiscing. In pulvinar felis sed est. Mauris non mi. Duis ultrices dolor
ut orci. Quisque lacinia arcu et purus. Sed euismod metus nec augue.

Cum sociis natoque penatibus et magnis dis parturient montes, nascetur
ridiculus mus. Nunc dolor leo, aliquam a, placerat sit amet, accumsan
eget, dolor. Sed lacinia augue in magna. Fusce sed enim. Vestibulum et
mauris. Phasellus in lectus. Pellentesque eu elit in dolor ullamcorper
sodales. Vestibulum interdum ornare ligula. Mauris felis odio, rhoncus
sed, adipiscing fermentum, tincidunt eu, metus. Suspendisse viverra
rhoncus purus.

Fusce euismod nisi at libero malesuada consectetuer. Proin laoreet, nunc
quis hendrerit gravida, neque leo placerat sapien, et semper tortor leo
et urna. Ut tincidunt posuere tortor. Sed tristique, odio at luctus
facilisis, nulla quam rhoncus tortor, at congue lacus elit nec metus.
Sed tempor sapien ut elit. Donec ac turpis feugiat nisi porta vehicula.

\comment{
This is an example of a block comment
}

\section{Problem Statement}\label{sec:problem}

This is a test.  Blah, blah, blah. $\Pr(A) = \Pr(A) + \Pr(B|A)$.
We discuss this issue in Section~\ref{sec:method}.  Indeed, we have
\[
\sum^{n}_{k = 1}{f(k)} \; ,
\]
where $f(k)$ is my favorite function.

\section{Related Work}\label{sec:related}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit \cite{breiman.ml.96}.
Phasellus non erat eu dui dignissim dictum.
Integer iaculis nulla at nisl \cite{jaynes.mebm.90}.
Proin ut enim non ipsum varius laoreet \cite{muslea.aaai.00,sahai.00}.
Integer feugiat, ante fringilla blandit
convallis, leo sapien egestas velit, non condimentum nulla sem vitae
risus. Mauris aliquam auctor quam. Sed ac enim. Donec mattis dui id
ligula. Integer vel sem eget ante cursus tristique. Nullam vel orci
vitae sem interdum placerat. In eget lectus. Donec blandit. Quisque
lacus urna, malesuada vel, mollis sit amet, rutrum nec, est. Proin
blandit ornare nibh. Duis et felis \cite{pfleger.tr.97}.

\section{Approach}\label{sec:approach}

Here is an example of code:

\begin{verbatim}
int main()
{
  cout << "testing" << endl;
  return 0;
} // main
\end{verbatim}
Text.
Plain text. {\em Emphasized text.} {\it Italicized text.}
{\bf Boldfaced text}.  {\tt typewriter text.} {\large Large text.}
Our results appear in Table~\ref{tab:results}.
In their paper \cite{muslea.aaai.00},
they discuss a lot of interesting things.

Em dash --- which is followed by an en dash -- and then we have
eloquently-hyphenated words, which are not to be confused with
the minus sign: $-$.  All are different \cite{shamos.phd.78}.

Here is a quote:
\begin{quote}
Ask not what your country can do for you.  Ask what you can do
for your country.
\end{quote}

In Figure~\ref{alg:min}, we present an algorithm for finding the
minimum component of a vector.
But there are other ways to present algorithms.
Some have started using the {\tt algorithm} and {\tt algorithmic}
packages.
See Algorithm~\ref{alg:pair} as an example.
Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Nam iaculis,
felis nec semper malesuada, quam metus placerat ligula, id euismod purus
eros eget justo. Pellentesque ipsum. In hac habitasse platea dictumst.
Ut pede pede, sagittis sit amet, dapibus eu, tristique in, ipsum
\cite{kolter.icml.05}.

\begin{figure}[t]
\begin{quote}
\begin{tabbing}
XX\=XX\=XX\=XX\=XX\=XXXXXXXXXXXXXXXXXX\= \kill
 \> {\sf Algorithm}\,$( \; \vec{x} \; )$ \\[\smallskipamount]
 \>\> $\vec{x}$: vector of numbers \\
 \>\> $i$: index of minimum value \\
 \>\> $\mbox{\em min}$: minimum value \\[\smallskipamount]
\parbox{3ex}{\hfill 1.} \>\> $m \leftarrow \infty$ \\
\parbox{3ex}{\hfill 2.} \>\> {\bf for} $j \leftarrow 1, \ldots, n$
\>\>\>\> // Loop over components \\
\parbox{3ex}{\hfill 3.} \>\>\> {\bf if} $( \vec{x}_{j} < \mbox{\em min} )$ \\
\parbox{3ex}{\hfill 4.} \>\>\>\> $\mbox{\em min} \leftarrow \vec{x}_{j}$ \\
\parbox{3ex}{\hfill 5.} \>\>\>\> $i \leftarrow j$ \\
\parbox{3ex}{\hfill 6.} \>\>\> {\bf end}; \\
\parbox{3ex}{\hfill 7.} \>\> {\bf end}; \\
\parbox{3ex}{\hfill 8.} \>\> {\bf return} $i$ \\
\> {\bf end.}
\end{tabbing}
\end{quote}
\caption{Algorithm for finding the minimum component of a vector.}
\label{alg:min}
\end{figure}

\paragraph{Paragraph.} Something you may never use, kind of like
Latin.\footnote{And footnotes.}
Aliquam fermentum velit tristique turpis. Mauris mollis dapibus purus.
Quisque vulputate ullamcorper purus. Quisque aliquam rhoncus felis.
Aenean fringilla mattis mi. Ut ut massa a sem fermentum venenatis.
Fusce ut risus. Maecenas ut nisl. Praesent felis erat, tincidunt ac,
placerat vel, sodales vel, justo. Vivamus semper sollicitudin est.
Morbi id eros eu tellus dignissim viverra \cite{breiman.ml.96}.

\begin{algorithm}[tb]
  \caption{Paired Learner}
  \label{alg:pair}
  \begin{algorithmic}[1]
    \STATE {\bfseries Input:} $\{ \vec{x}_t, y_t \}^{T}_{t=1}$, $w$, $\theta$
    \vskip 0.3em
    \STATE $\{ \vec{x}_t, y_t \}^{T}_{t=1}$: training data
    \STATE $w$: window size for the reactive learner
    \STATE $\theta$: threshold for creating a new stable learner
    \vskip 0.3em
    \STATE Let $S$ be a stable learner
    \STATE Let $R_{w}$ be a $w$-reactive learner
    \STATE Let $C$ be a circular list of $w$ bits, each initially $0$
    \FOR{ $t \leftarrow 1$ {\bfseries to} $T$ }
    \STATE $\hat{y}_{S} \leftarrow S.\mbox{\sf Classify}( \vec{x}_{t} )$
    \STATE {\bfseries output} $\hat{y}_{S}$
    \STATE $\hat{y}_{R} \leftarrow R_{w}.\mbox{\sf Classify}( \vec{x}_{t} )$
    \IF{ $\hat{y}_{S} \neq y_{t} \wedge \hat{y}_{R} = y_{t}$ }
    \STATE $C.\mbox{\sf set}( t )$
    \ELSE
    \STATE $C.\mbox{\sf unset}( t )$
    \ENDIF
    \IF{ $\theta < C.\mbox{\sf proportionOfSetBits}()$ }
    \STATE $S \leftarrow \mbox{\bf new } \mbox{\sf StableLearner}()$
    \STATE $S \leftarrow R_{w}.\mbox{\sf getConceptDescription}()$
    \STATE $C.\mbox{\sf unsetAll}()$
    \ENDIF
    \STATE $S.\mbox{\sf Train}( \vec{x}_{t}, y_{t} )$
    \STATE $R_{w}.\mbox{\sf Train}( \vec{x}_{t}, y_{t} )$
    \ENDFOR
  \end{algorithmic}
\end{algorithm}

Text.  See Figure~\ref{fig:design}.
Nullam massa est, facilisis at, egestas non, lobortis at, felis.
Vestibulum eu velit ut justo commodo pretium. Quisque commodo velit
vel sem. Cum sociis natoque penatibus et magnis dis parturient montes,
nascetur ridiculus mus. Donec nec magna. Aliquam erat volutpat.

\begin{theorem}[Kolter and Maloof \cite{kolter.icml.05}]
\label{addexp.d-mistake-1}
For any time steps $\mathrm{t_1} < \mathrm{t_2}$, if we stipulate that
$\beta + 2\gamma < 1$, then the number of mistakes that \textbf{AddExp.D}
will make between time steps $\mathrm{t_1}$ and $\mathrm{t_2}$ can be
bounded by
\[
M_{t_2} - M_{t_1} \leq
\frac{\log (W_{t_1} / W_{t_2})}{\log (2/(1+\beta+2\gamma))} \; .
\]
\end{theorem}

\begin{proof}
\textbf{AddExp.D} operates by multiplying the weights of the experts that
predicted incorrectly by $\beta$.  If we assume that a mistake is made at
time step $t$ then we know that at least $1/2$ of the weight in the
ensemble predicted incorrectly.  In addition, a new expert will be added
with weight $\gamma W_t$.  So we can bound the weight with
\[
W_{t+1} \leq \frac{1}{2}W_t + \frac{\beta}{2}W_t + \gamma W_t =
\frac{1+\beta +2\gamma}{2} W_t \; .
\]
Applying this function recursively leads to:
\[
W_{t_2} \leq \frac{1+\beta+2\gamma}{2}^{M_{t_2} - M_{t_1}} W_{t_1} \; .
\]
Taking the logarithm and rearranging terms gives the desired bound, which
will h old since the requirement that $\beta + 2\gamma < 1$ ensures that
$(1 + \beta + 2\gamma)/2 < 1$. \qed
\end{proof}

\section{Experimental Study}\label{sec:study}

Always put something here, even if it just informs the reader of what
comes next.
Integer odio lorem, aliquam id, dignissim in, varius at, neque. Class
aptent taciti sociosqu ad litora torquent per conubia nostra, per
inceptos himenaeos. Maecenas vitae massa ultrices lorem aliquam pharetra.
In hac habitasse platea dictumst. Nunc consectetuer sapien. Maecenas ut
felis. Sed blandit congue mauris. Donec ornare laoreet tortor. Cum sociis
natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
Fusce id neque ac enim lobortis aliquet. Sed a purus ac nunc feugiat
interdum. Suspendisse risus. Donec pulvinar, turpis at rutrum porta,
justo massa iaculis quam, vel pharetra leo magna et metus. Etiam tellus
dolor, volutpat et, dignissim vel, iaculis in, sem. Donec ante est,
ultricies non, eleifend in, pretium id, nisl. Fusce vitae nunc.
Vivamus egestas. Vestibulum nibh. Aliquam rutrum imperdiet diam.

\begin{figure}[t]
\centerline{\includegraphics[width=1.0in]{state.eps}}
\caption{A pretty picture.} \label{fig:design}
\end{figure}

\subsection{Method}\label{sec:method}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Sed vitae risus.
Vivamus dapibus, quam vehicula eleifend vestibulum, pede magna iaculis
leo, quis convallis nisl mauris id arcu. Morbi tincidunt odio at libero.
Mauris molestie. Proin placerat, neque sit amet eleifend ullamcorper,
arcu sem ornare arcu, a adipiscing metus felis eu turpis. Integer bibendum
nisi placerat quam. Donec id enim. Sed neque ipsum, ullamcorper vitae,
bibendum nec, pharetra quis, quam. Curabitur suscipit aliquet ligula.
Aenean pede.

Cras molestie turpis ac lorem. Vivamus molestie porta purus. Nulla
facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
Fusce fermentum, ante in vestibulum auctor, turpis tellus aliquam est,
in accumsan massa tortor id magna. Mauris sit amet libero. Donec orci dui,
interdum in, sollicitudin id, adipiscing quis, nulla. Sed ante orci,
sagittis at, egestas ut, egestas nec, leo. Cras malesuada dolor sed diam.
Ut lobortis velit sodales nunc.

\input table.tex

Duis vestibulum lacus eget dolor. Proin at quam. Phasellus viverra molestie
nisl. In non elit et felis commodo suscipit. Phasellus consectetuer purus.
Donec lobortis sagittis ante. Vestibulum hendrerit blandit quam.
Pellentesque habitant morbi tristique senectus et netus et malesuada fames
ac turpis egestas. Duis vel quam. Proin dictum. Donec laoreet scelerisque
nisi. Sed at urna et justo vulputate tristique. Aenean interdum. Quisque
in tortor. Morbi eget purus. Vestibulum ante ipsum primis in faucibus orci
luctus et ultrices posuere cubilia Curae; Etiam semper.

\begin{figure}
\centerline{\includegraphics[scale=1.0]{plots/stagger.stagger.ps}}
\caption{Results.} \label{fig:results}
\end{figure}

\subsection{Results}\label{sec:results}

In Table~\ref{tab:results}, we present the results of our study.
In Figure~\ref{fig:results}, we present the results of our study.
Aliquam fermentum velit tristique turpis. Mauris mollis dapibus purus.
Quisque vulputate ullamcorper purus. Quisque aliquam rhoncus felis.
Aenean fringilla mattis mi. Ut ut massa a sem fermentum venenatis.
Fusce ut risus. Maecenas ut nisl. Praesent felis erat, tincidunt ac,
placerat vel, sodales vel, justo. Vivamus semper sollicitudin est.
Morbi id eros eu tellus dignissim viverra.

\subsection{Analysis}\label{sec:analysis}

Nulla odio. Phasellus congue malesuada quam. Pellentesque non lectus
at nisi venenatis faucibus. Proin gravida diam vitae pede. Morbi sit
amet dolor. Pellentesque feugiat tortor ut est. Ut sodales augue non
velit.

Duis arcu. Nam ac mauris. Pellentesque eleifend tellus ac eros.
Maecenas varius massa eu nunc mollis imperdiet. Donec interdum, lorem
in vestibulum feugiat, elit arcu fringilla ante, et sollicitudin ipsum
sapien a turpis. Proin sit amet nisl id metus hendrerit volutpat.

\section{Conclusion}\label{sec:conclusion}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.  Duis cursus.
Duis consectetuer, lacus id vehicula viverra, dolor quam dignissim pede,
nec ultrices metus tortor quis turpis.
Praesent non orci non est tincidunt mollis.
Nullam pellentesque auctor orci.
Morbi aliquam.
Cum sociis natoque penatibus et magnis dis parturient montes, nascetur
ridiculus mus.

In auctor ornare risus.
Nulla id magna nec pede elementum rhoncus.
Suspendisse ultricies mattis lacus.
Cras pulvinar pede nec dolor.
Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
Suspendisse potenti.
Sed pede massa, scelerisque id, tempor ac, vestibulum nec, est.
Maecenas molestie tincidunt orci.
Donec ac leo quis libero iaculis semper.
Aenean ligula pede, semper eu, tristique eu, aliquam in, nisi.
Curabitur sagittis condimentum ligula.
Nunc interdum suscipit libero.

\appendices  % Indicates that appendices follow.
% If there's only one, use \appendix instead.

\chapter{Important Note About Margins}
\label{mgins}

\section{General tactics}
No two printers are alike.  Please print a few pages and \emph{measure} them.
\LaTeX\ can send commands to your printer, but it can't see whether they are
being obeyed!

Check the {\tt dvips} problem described below.
If, after tackling that,
you still need to make adjustments to get correct margins on paper
(1.5 inches on the left and 1 inch on the right),
add commands such as:
\begin{verbatim}
\hoffset = 0.5in    % shift 0.5 inch to the right
\voffset = -0.1in   % shift 0.1 inch up
\end{verbatim}
in your \verb".tex" file right after after \verb"\usepackage{gu}".

\section{The A4 problem}

If your printouts are consistently too high or too low on the page,
and you are generating PostScript files
using the {\tt dvips} command, you are probably generating output for
A4 (11.7-inch) paper.

That is the size of paper used in Europe.
American (``letter'') paper is only 11 inches long and is the size specified
for Georgetown theses and dissertations (and their electronic images).

As a quick check, try
typing the {\tt dvips} command with the argument {\tt -tletter}, like this:
\begin{flushleft}
{\tt dvips -tletter {\it filename}}
\end{flushleft}
If that cures the problem, you can fix it permanently by editing the file
{\tt config.ps} to make letter size (11-inch) paper the default.
See the {\tt dvips} documentation for details.

\chapter{Customizing the Table of Contents}

On rare occasions the table of contents will not come out formatted
the way you'd like.  Here's how to control it. \emph{Most people will
not need to do this} and can ignore these notes.

Every time you run \LaTeX, it writes the table of contents on a file
whose name ends in \verb".toc", and reads and prints the \verb".toc" file
from the \emph{previous} run.
That's why you have to run \LaTeX\ twice to get a correct table of contents.

If you need to alter your table of contents (e.g., by inserting a
page break), you can edit the \verb".toc" file in between two runs of \LaTeX.
For example, you can insert \verb"\newpage" to generate a page break.
Note that this change will not last because \LaTeX\ will write a new
\verb".toc" file ever time it runs.

Alternatively, you can add a command to your \verb".tex" file that will
add something to the contents.  For example, just before beginning
a particular chapter, you can execute the command:
\begin{verbatim}
\addtocontents{toc}{\newpage}
\end{verbatim}
to cause a page break at the corresponding place in the table of
contents.

\chapter{Common PDF Problems}

When you convert your thesis from PostScript to PDF (with
Adobe Acrobat Distiller or other suitable software), you may discover
two problems.

\section{Text shrinks when converted to PDF}

This may mean that your PostScript file was formatted for A4
(11.7-inch) paper, and PDF is shrinking it to fit on American 11-inch
paper.  See p.\ \pageref{mgins}.

\section{Type looks blurred or pixellated}

This generally means you are using the old bitmap versions of the
\TeX\ fonts rather than the PostScript versions.  As a quick check, try
adding the command \verb"\usepackage{times}" right after \verb"\documentclass".
This will change the typeface.  If the new typeface looks a lot
smoother, you've identified the problem but not cured it.

To get the PostScript \TeX\ fonts, get your system support people to
reconfigure {\tt dvips}, or download and install a newer version,
or simply run \LaTeX\ on a computer that has more up-to-date software.

Please note that PDF conversion is not affected by \verb"guthesis.sty" and the
author of \verb"guthesis.sty" cannot undertake to solve other problems with it.

\chapter{How to Cite Web Pages}

Your bibliography entries should follow whatever format is standard in your
field.
If completely stymied, see the \emph{Chicago Manual of Style} (which gives
\emph{two} formats, one for humanities and one for sciences; don't mix them
up) or the \emph{Publication Manual} of the American Psychological Association.

Even so, you will probably still be in doubt about how to cite web pages.
The way I see it, the Web is not a publisher.  Thus, a web address is not
a sufficient citation for a web page.
Instead, you must cite the document itself (indicating where and when it
originated) and then add information about the web address.

If the paper has been published, and you got a copy from the author's web
site, your job is easy.  Just do something like this:
\begin{quote}
Newton, Isaac (1672) On the refraction of coloured light.
\emph{Journal of Irreproducible Results} 23:456-789.
Web: \url{http://www.trinity.cam.ac.uk/new\-ton/colour.pdf}.
\end{quote}
That is, add the web information at the end of a normal citation.

If the paper is available only on the author's web site (at an institution
or corporation), cite the institution or corporation as the publisher,
something like this:
\begin{quote}
Newton, Isaac (1672)  On the refraction of coloured light.  Trinity College,
Cambridge.  Web: \url{http://www.trinity.cam.ac.uk/newton/colour.pdf}.
\end{quote}
The idea is to cite it just like a privately distributed paper except that
you add the web address.

If the web site \emph{is} a publisher (e.g., an online journal), then it
will probably give instructions for citation.
Do not copy numbers into a bibliography entry if you don't know what they
mean.

Consult your major professor for more advice, since the details will depend
on other aspects of your bibliography format.

Note that the character $\sim$ in web addresses is typed \verb"$\sim$",
unless you use the {\tt url} package.

Note also that by itself, \LaTeX\ will not hyphenate a URL.  It is up to you
to indicate with the symbol \verb"\-" the places where hyphens are permitted.
Always hyphenate within words, not between compound words, so that the reader
will know that the hyphen was not present in the original.

\bibliographystyle{plainnat}
\bibliography{gusample}

\typeout{***}
\typeout{*** Note!}
\typeout{*** Because this document has a table of contents,}
\typeout{*** you must run LaTeX TWICE to get it to print correctly.}
\typeout{***}

\end{document}

### 2023-01-31 paper.tex
Setting up initial file
Paper changes
Basic paper setup

--- 2023-01-31 template/gusample.tex
@@
 
-\usepackage{guthesis} % Must be the last package
+\usepackage{template/guthesis} % Must be the last package
 
@@
 
-\title{Example of a Thesis \\
-       Formatted with LaTeX \\
-       Using the Georgetown University \\
-       Style Macro Package, Version \guthesisversion}
+\title{Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking}
 
-\author{Marcus A. Maloof}
+\author{Eliana V. Troper}
 
-\previousdegree{B.S.}
+\previousdegree{A.B.}
 
@@
 % defense or approval date, not today's date...
-\thesisday{15}
-\thesismonth{December}
-\thesisyear{2010}
+\thesisday{11}
+\thesismonth{April}
+\thesisyear{2023}
 
-\professor{Abraham Baldwin}
+\professor{Micah Sherr}
 %\secondprofessor{Alonzo Church}   % Only if you have 2 major professors!
 
-\fulltitle{Example of a Thesis Formatted with LaTeX Using the Georgetown
-           University Style Macro Package, Version \gustyversion}
+\fulltitle{Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking}
 
+% TODO: Update this
 \indexwords{Word~processing, Computer~typesetting, Computer~graphics,
@@
 
-\dean{Timothy A.\ Barbari}
+\dean{Alexander Sens}
 
-\memberi{Benjamin Franklin}
-\memberii{Isaac Newton}
+\memberi{Lisa Singh}
+\memberii{Benjamin Ujcich}
 % Use \memberiii, \memberiv, \memberv for up to 3 more members if needed.
@@
 \begin{abstract}
-This is the abstract, a brief summary of the contents of the entire thesis.
-It is limited to 350 words.
-
-The abstract page(s) are not numbered and are not necessarily included
-in the bound copies.  Likewise, the signature page is not counted in
-page numbering because not all copies contain it.
-
-Throughout this sample thesis, {\bf please note
-that the layout obtained with \LaTeX\ is not meant to be a
-perfect duplicate of the Microsoft Word examples in the \emph{Graduate
-School Style Manual.}}  \LaTeX\ has additional typographic tools at its
-disposal, such as {\sc small capitals} and various subtle adjustments
-of spacing, which are used by the Georgetown \LaTeX\ style sheet in
-accordance with the standard practices of the book-printing industry.
-
-The index words at the bottom of the abstract should be chosen carefully,
-preferably with the help of one or two of your colleagues.
-They are the words by which people will find your thesis when searching
-the scientific literature.
-If you want to get credit for your ideas, be sure to choose a good set of
-index words so that people doing related work will know about yours.
+TODO: Optional for master's thesis but these are nice (max 350 words)
 \end{abstract}
@@
 
-The Dedication is optional, but if it is included, it should have
-a roman numeral page number but not be included in the table of
-contents.  To achieve that, we declare it as a \verb"\chapter*" in \LaTeX.
+TODO: Optional
 
@@
 
-In a real thesis, this section would contain acknowledgments such
-as, ``This work was funded by National Science Foundation Grant
-Number AAA-00-00000 (Benjamin Franklin, Principal Investigator),''
-and ``I would like to thank John Doe for helping me proofread my
-thesis and Mary Roe for drawing my graphs.''
-
-The acknowledgments are included in the table of contents but do
-not have a chapter number.  To achieve that, we
-declare them to be a \verb"\pseudochapter" (which is defined only in
-\verb"guthesis.sty").
-
-I (Mark Maloof) would like to thank Michael Covington for developing
-this \LaTeX\ style sheet for the University of Georgia.
-Zachary Hunter deserves special thanks for revising the UGA style
-file to work with the new version of \LaTeX\ (2e) as well as the
-previous version (2.09).
-The revisions in
-Version 3.0 of \verb"guthesis.sty" are
-largely the work of Isidor Ruderfer.
-Other credits appear in the style sheet itself.
-
-\pseudochapter{Preface}
-
-If your thesis has a preface, this is where it goes.
-A preface is not an introduction, and most theses do not need them.
+TODO
 
@@
 
-\chapter{What \LaTeX\ is all about}
+\chapter{Introduction}
 
-This document is an example of how to format a thesis or dissertation
-using \LaTeX\  and get results acceptable at Georgetown University.
+TODO
 
-\LaTeX\ (with its parent \TeX)
-has two major advantages for academic use.  First, to a remarkable
-degree it makes design decisions automatically.  The author supplies
-only the words of a text, and \LaTeX\ places them on the page in an
-aesthetic manner, avoiding rivers and awkward breaks.  In this respect
-LaTeX is like a very intelligent typist or typesetter.
+\chapter{Background}
 
-Second, \LaTeX\ can typeset complex mathematical formulas such as
-\[
-\sum_{i=1}^{\infty} x^{y+z} = \frac{p+q+r}{s+t+u+v}
-\]
-both displayed (as shown above) and in the text, as in
-$\sum_{i=1}^{\infty} x^{y+z} = \frac{p+q+r}{s+t+u+v}$.
-This makes \TeX\ and \LaTeX\ indispensable for mathematicians, physicists,
-and the like.
+TODO
 
-LaTeX also has built--in formats for other kinds of displayed material
-such as verse,
-\begin{verse}
-Freude, sch\"{o}ne G\"{o}tterfunken  \\
-Tochter aus Elysium,                 \\
-Wir betreten, feuertrunken,          \\
-Himmlische, dein Heiligum!          \\
-Deine Zauber binden wieder            \\
-Was der Mode streng geteilt\dots
-\end{verse}
-and direct quotations:
-\begin{quote}
-The society that scorns excellence in plumbing, because plumbing is a
-humble activity, and tolerates shoddiness in philosophy, because
-philosophy is an exalted activity, will have neither good plumbing nor
-good philosophy.  Neither its pipes nor its theories will hold water.\\
-\hspace*{\fill} --- John Gardner, {\em Excellence}
-\end{quote}
-If you wish, quotes and other displayed material can be single--spaced;
-here is an example of how that is achieved:
-\begin{verse}
-\begin{singlespace}
-Yes, I wrote ``The Purple Cow.'' \\
-I'm sorry now I wrote it. \\
-But I can tell you anyhow \\
-I'll kill you if you quote it! \\
-\hfill --- Anonymous?
-\end{singlespace}
-\end{verse}
-Well, maybe it's not as anonymous as it looks.
+\section{What is censorship circumvention?}
 
-Computer scientists use LaTeX's ``verbatim'' format to display portions
-of computer programs in text, like this:
-\begin{verbatim}
-1   GO TO 2
-2   GO TO 1
-3   PRINT "THIS STATEMENT WILL NEVER EXECUTE"
-4   END
-\end{verbatim}
-There you have it.%
-\footnote{This is a footnote. Notice that footnotes are single--spaced
-even though the text is double--spaced. Long footnotes are discouraged;
-either make important points in the text or leave them out.}
+TODO
 
-Whenever you quote parts of a computer program in English text, they
-should be set off by using typewriter type.  The \verb"PRINT" statement
-in the program above will never execute because the \verb"GO TO"
-statement above it keeps execution from reaching it.
+\subsection{Current theory of censorship circumvention}
 
-\chapter{Five Important Notes}
+TODO
 
-\section{\LaTeX\ is not a typewriter --- nor an ordinary word processor}
+\subsection{Ethics}
 
-\emph{The format that you get with \LaTeX\ is more elegant
-than the simpler format in the Graduate School style manual and is not
-intended to match it perfectly.}
+TODO
 
-\LaTeX\ makes available to you \emph{all} of the tools of fine book printing.
-For example, \LaTeX\ has more degrees of
-vertical spacing available than other word processors do, and it uses them
-effectively.  Likewise, \LaTeX\ provides {\sc Small Capitals} for situations
-where other software would only provide ALL CAPITALS.
+\subsection{Origination of censorship circumvention}
 
-The format produced by \verb"guthesis.sty" has been reviewed by the Graduate School.
-If your thesis fails the format check, make sure you have followed the
-instructions for \verb"guthesis.sty" (contained in the file \verb"gusample.tex")
-and the instructions for \LaTeX.
+TODO
 
-\section{You can't do without the book!}
+\subsection{Taxonomy of censorship circumvention}
 
-\emph{You are not expected to be able to use \LaTeX\ without a manual.}
-Don't even try --- you'll waste a lot of time.
-The definitive manual for \LaTeX\ is:
-\begin{quote}
-Lamport, Leslie (1994) \emph{\LaTeX: A Document Preparation System.}
-2nd ed.
-Reading, MA: Addison-Wesley.
-\end{quote}
-Alternatively, there is a good manual available on line whose author is
-named Oetiker.
-There are several versions.  Use a search engine to search for
-``LaTeX Oetiker'' and you'll find it.
+TODO
 
-\section{The {\tt guthesis.sty} style sheet adds to \LaTeX\ but does not replace it}
+\section{Prior techniques}
 
-``How do I do so-and-so in \verb"guthesis.sty"?''  Almost always the same way as
-in plain \LaTeX.
-The Georgetown University style sheet, called \verb"guthesis.sty", adds features
-to \LaTeX; it does not take away what is already there.
+TODO
 
-\section{Ragged right margins are optional}
+\subsection{[Point to point obfuscation]}
 
-{\raggedright
-\parindent 0.25in
-This section is typeset in ``ragged right'' format, in which \LaTeX\ has
-been told not to force a straight right margin.
+TODO
 
-``Ragged right'' is preferable if your thesis contains a large number of
-words likely to be hyphenated incorrectly, formulas, web addresses, or
-the like.  To get it, put the two lines
-\begin{verbatim}
-\raggedright
-\parindent 0.25pt
-\end{verbatim}
-anywhere after the {\tt documentclass} command and before
-\verb"\begin{document}".
+\subsubsection{OBFS and Scramblesuit}
 
-You can also reduce the amount of hyphenation, without eliminating it
-totally, by following the instructions in the \LaTeX\ manual.
-} % raggedright
+TODO
 
-\section{Please let \LaTeX\ do the layout...}
+\subsection{[P2P and P2P-like]}
 
-Please do not use \verb"\vspace", \verb"\hspace", and other \TeX\ commands
-that specify the precise location or spacing of items on the page.
-Leave the layout to \LaTeX\ and \verb"guthesis.sty".
-Otherwise, very ugly things can happen.
+TODO
 
-Your thesis is like a volume in a series.
-It should look like the other theses and dissertations that were typeset
-using the same technology.
-Just as different volumes of the \emph{Encyclopaedia Britannica} have exactly
-the same margins and typography, so should different theses from the same
-university, as far as technology permits.
+\subsubsection{Snowflake}
 
-\section{Please use floating figures and tables...}
+TODO
 
-Please use the \verb"figure" and \verb"table" environments for your figures
-and tables.
-A picture or table should not interrupt the text the way a mathematical
-formula does.
-Instead, it should ``float'' to the nearest convenient location---which
-\LaTeX\ will take care of automatically---and should be identified by
-number.
+\subsubsection{MassBrowser}
 
-\chapter{Frequently Asked Questions About Typing Georgetown Theses with
-\LaTeX\ and {\tt guthesis.sty}}
+TODO
 
-\section{\LaTeX\ itself}
+\subsection{High-reliability channels}
 
-\subsection{What is \LaTeX?}
+TODO
 
-\LaTeX, by Leslie Lamport, is an extension of \TeX, the computer typesetting
-system designed by Donald Knuth.  This software system is used to typeset
-books, journals, papers, and theses in the mathematical sciences.
-Knuth and Lamport had two goals in designing it:
-\begin{itemize}
-\item To use the computer to equal the quality of the best conventional
-typesetting.
-No longer does ``word processing'' mean ``a poor substitute for real
-printing.''
-\item To separate the jobs of the \emph{author} and the \emph{typesetter.}
-\end{itemize}
-Other word processors turn the screen into a blank piece of paper and let
-you type on it.  \LaTeX\ is not your \emph{typewriter,} it's your
-\emph{typist.}  For example, to mark the beginning of a chapter, you
-type something like this:
-\begin{verbatim}
-\chapter{Literature Review}
-\end{verbatim}
-and \LaTeX\ automatically determines what a chapter heading should look like.
-It does this by consulting a \emph{style sheet.}  You do not have to worry
-about whether you've hit Enter the same number of times at the beginning of
-each chapter, or whether all the chapter headings are centered and the
-margins are correct.  That's the (automated) typist's job.
+\subsubsection{Domain fronting}
 
-\subsection{How is ``\LaTeX'' pronounced?}
+TODO
 
-The X in \TeX\ is actually a Greek chi, with the sound of \emph{ch} in
-Scottish \emph{loch} or German \emph{ach}.  Thus, \TeX\ is pronounced
-``tekh.''  It is short for Greek \emph{tekhn\={e}} ``art, craft.''
+\subsubsection{Raven}
 
-\LaTeX\ is pronounced \emph``lah-tekh'' in the Northeast, \emph``lay-tekh''
-in England and the South, and several different ways in the West.
+TODO
 
-\subsection{What's it like to run \LaTeX?}
+\subsection{Decoy routing}
 
-\LaTeX\ is \emph{not} a single integrated piece of software.  It has several
-parts.  The normal process for typing and printing a paper is as follows.
-On finding an error or discovering that a change is needed, you can go back
-to any earlier step at any time.
-\begin{enumerate}
-\item Use a text editor (Windows Notepad or whatever text editor you like)
-to type your document on a file whose name ends in {\.tex}.
-\item Go to a command prompt and run {\tt latex} to create a {\tt .dvi} file.
-\item Optionally, preview the {\tt .dvi} file on-screen.  Some of us skip
-this step.
-\item Run {\tt dvipdf} to convert the {\tt .dvi} file to PDF.
-\item Use Adobe Reader to view the PDF file and print it, if desired.
-\end{enumerate}
+TODO
 
-\subsection{Who benefits the most from using \LaTeX?}
+\section{Real world observations}
 
-Those who need to typeset mathematical formulas or computer programs;
-those whose theses are likely to be published
-by a book publisher; and those who plan to submit their theses electronically.
+TODO
 
-\subsection{Who should \emph{not} use \LaTeX?}
+\subsection{Real world vs. academic theory}
 
-If you consider yourself a ``computer dummy'' and can use only the simplest
-software, or if you do not have the time or patience to learn a new set of
-technical skills, you won't like \LaTeX.  On the other hand, you probably
-will not type your thesis correctly with a conventional word processor
-either.  (Let's face it, typing a thesis correctly is a technical challenge,
-no matter what software you do it with!)  You should hire a typist.
+TODO
 
-\section{\LaTeX\ versions}
+\chapter{System design}
 
-\subsection{What are Mik\TeX, em\TeX, te\TeX, etc.?}
+TODO
 
-These are implementations of \LaTeX\ for particular computers, incorporating
-Knuth and Lamport's original computer programs plus various tools to make
-them easier to use or more versatile.
-All of them are 100\% compatible with the original \LaTeX.
+\section{Theory and goals}
 
-\subsection{Is there \LaTeX\ for Macintosh, Linux, Amiga, Sun, BeBox...?}
+TODO
 
-Yes.  \LaTeX\ has been ported to a huge variety of computers and produces
-\emph{identical} output on all of them, using \emph{identical} file formats.
-If you have Linux, you almost certainly already have \LaTeX.
+\section{Implementation}
 
-\subsection{What is \LaTeXe?}
+TODO
 
-The version of \LaTeX\ that has been in use for the last several years.
-It was preceded by \LaTeX\ 2.09.  Those are the only two version of
-\LaTeX\ that have been distributed widely.  There will eventually be
-a \LaTeX\ 3, but not very soon.
+\chapter{System evaluation}
 
-\subsection{Where do I get \LaTeX?}
+TODO
 
-You can download it free of charge from various sites;
-Be careful about Googling \LaTeX.
-It's best to go to the \TeX\ Users Group web site:
-\url{http://www.tug.org}.
+\section{Performance}
 
-\subsection{Where is the documentation for \LaTeX?}
+TODO
 
-In the book \emph{LaTeX: A Document Preparation System,} by Leslie Lamport,
-2nd edition, published by Addison-Wesley.  \textbf{You must buy this book.}
-Other books about \LaTeX\ are useful but are not the official guide.
+\section{Bootstrapping availability}
 
-\subsection{Where can I get help with \LaTeX?}
+TODO
 
-First, read Lamport's book.  \emph{You cannot get along without it.}
+\chapter{Conclusion}
 
-Second, you can ask questions on the newsgroups {\tt comp.text.tex}
-(international).
+TODO
 
-Third, if you have problems that are specific to {\tt guthesis.sty},
-and particularly if {\tt guthesis.sty} does not appear to be meeting
-Georgetown's thesis format requirements, please contact me
-(Mark Maloof, maloof@cs.georgetown.edu).
+\section{Future work}
 
-\section{The Georgetown University style sheet}
-
-\subsection{What is {\tt guthesis.sty}?}
-
-A style sheet for \LaTeX\ that makes it follow the format for
-Georgetown University theses and dissertations.
-
-\subsection{Where do I get {\tt guthesis.sty} and how do I install it?}
-
-Download it from \texttt{http://www.cs.georgetown.edu/academics/guthesis.zip}.
-
-Install it by putting it in the same directory as your thesis, or in
-directory {\tt texmf/tex/latex} of your \TeX\ system.
-
-\subsection{How do I use {\tt guthesis.sty}?}
-
-For a quick summary, see Fig.\ \ref{gutemplate}.
-For details, see the file {\tt gusample.tex}.
-For a skeleton document, see the file {\tt template.tex}.
-
-\begin{figure}
-\begin{center}
-\begin{minipage}{5in}
-\tiny
-\begin{verbatim}
-     \documentclass[12pt]{report}
-     \usepackage{guthesis}
-
-     % The following 2 lines are OPTIONAL to turn off all hypenation
-     % and print with "ragged" right margins
-     \raggedright
-     \parindent 0.25in
-
-     \title{Title of Thesis \\
-            Broken into Lines \\
-            As Appropriate}
-
-     \fulltitle{Title of Thesis Not Broken Into Lines}
-
-     \author{Your Name Here}
-
-     \previousdegree{B.A., Name of University, 1977 \\
-                     M.S., Some Other University, 1978}
-
-     \thisdegree{Master of Science} % or Doctor of Philosophy, etc.
-     \thesistype{Thesis}        % or Dissertation
-     \thesisday{5}              % put the day of defense or approval here...
-     \thesismonth{May}          % put the month of defense or approval here...
-     \thesisyear{2005}          % put the year of defense or approval here...
-
-     \indexwords{keywords for indexing your thesis in library catalogs}
-
-     \professor{Abraham Baldwin}     % Major Professor
-     \secondprofessor{Alonzo Church} % Co-Major Professor if you have one
-     \memberi{Benjamin Franklin}     % Committee member
-     \memberii{Isaac Newton}         % Committee member
-     % Use \memberiii, \memberiv, \memberv for up to 3 more members if needed.
-
-     \dean{Timothy A.\ Barbari}       % Dean of the Graduate School
-
-     \begin{document}
-     \pagenumbering{roman}   % Use Roman numerals until chapters start.
-
-     \begin{abstract}
-     Text of abstract goes here.
-     \end{abstract}
-
-     \maketitle    % Creates title page, copyright page if any, and approval page.
-
-     \chapter*{Dedication}
-     Dedication, if any, goes here.
-     It is a "\chapter*" so it is not in the table of contents.
-
-     \pseudochapter{Acknowledgments}
-     Text of acknowledgments goes here.
-     It is a "\pseudochapter" so it goes in the table of contents but has no chapter number.
-
-     \tableofcontents
-     \listoffigures   % Optional - Omit this line if you don't want a list of figures.
-     \listoftables    % Optional - Omit this line if you don't want a list of tables.
-
-     \newpage
-     \pagenumbering{arabic}  % Ordinary pages have Arabic numerals.
-
-     \chapter{Title of Chapter Goes Here}
-     Text of first chapter goes here.
-
-     \chapter{Title of Chapter Goes Here}
-     Text of second chapter goes here.
-
-     \appendices  % Indicates that appendices follow.  If there's only one, use \appendix instead.
-
-     \chapter{Title of First Appendix}
-     Text of first appendix goes here.
-
-     \chapter{Title of Second Appendix}
-     Text of second appendix goes here.
-
-     \bibliographystyle{plainnat}
-     \bibliography{thesis}  % Pulls entries from thesis.bib
-
-     \end{document}
-\end{verbatim}
-\end{minipage}
-\end{center}
-\caption{Template for formatting a thesis with {\tt guthesis.sty}.}
-\label{gutemplate}
-\end{figure}
-
-\subsection{Do I have to get {\tt guthesis.sty} before typing my thesis?}
-
-No.  You can type your thesis using the \LaTeX\ {\tt report} documentclass
-(described in Lamport's book); this will enable you to produce neat,
-single-spaced copies of the work in progress.  When it's finished, get
-{\tt guthesis.sty} and make the small additions to your thesis that are described
-there.
-
-\subsection{What are the required parts of a thesis typed with {\tt guthesis.sty}?}
-
-They are described in {\tt guthesis.sty} itself, which you can read with your
-text editor.
-Alternatively, you can use {\tt gusample.tex} as sample to imitate.
-
-\section{Troubleshooting}
-
-\subsection{Why is the text too high or low on the page?}
-
-See Appendix A, p.\ \pageref{mgins}.
-
-\subsection{Why is there a space before a footnote number?}
-
-If your footnote numbers come out positioned like this $^8$ rather than
-this$^8$, it's because you're leaving a space before the
-\verb.\footnote. command.
-\begin{verbatim}
-Type like this.\footnote{Here's the note.}
-Not like this. \footnote{Here's the note.}
-\end{verbatim}
-A useful trick is to put \verb"%" at the end of one line (to comment out
-all the remaining blank space) and then \verb"\footnote" at the beginning
-of the next line.
-
-\subsection{Why is my table of contents blank or incorrect?}
-
-You must run \LaTeX\ twice in order to get a correct table of contents.
-The first time, it keeps records of where things are; the second time,
-it actually generates the table of contents.  If the table of contents
-is long, you may need to run \LaTeX\ three times to ensure that adequate
-space is left for it.
-
-\subsection{Why is there too much space after some of the periods?}
-
-\LaTeX\ normally assumes that every period marks the end of a sentence,
-so it leaves extra space after it.  You should normally use a required
-space (\verb.~.) after every period that does not mark the end of a sentence.
-Type ``\verb"T.~S.~Eliot"'' to print ``T.~S.~Eliot'' or the like.
-
-Beginning with {\tt guthesis.sty} version 2.0 (December 2001), this is no longer
-a problem because {\tt guthesis.sty} tells \LaTeX\ not to treat periods specially;
-the same amount of space follows each word whether or not it ends with a
-period.  This is known as ``French spacing'' and is an accepted practice
-in the printing industry.
-
-\subsection{Why do some words hang out past the right margin?}
-
-When \LaTeX\ cannot break a line satisfactorily, it leaves a word sticking
-out into the margin and gives you an ``Overfull hbox'' error message.
-It is up to you to rearrange the text so that it fits.
-
-\subsection{What is an overfull hbox?}
-
-See previous question.
-
-\subsection{What is a ``Package hyperref warning''?}
-
-Most people now use the \verb"hyperref" package to generate hyperlinks to
-their chapters and sections in the eventual PDF output.
-
-This is good, but \verb"hyperref" complains violently if there is anything
-other than plain text in a section title.
-It also complains if you use \verb"\pseudochapter".
-Just ignore the warnings.
-
-\section{Character set and typography}
-
-\subsection{How do I type a percent sign?}
-
-See Lamport's book.  A quick answer:  Type ``\verb.\%.''.
-
-\subsection{How do I type a tilde ($\sim$)?}
-
-This character often occurs in web addresses.
-In \LaTeX, when you type ``\verb.~.'' you get a blank.
-(Specifically, you get a ``required space,'' a space that cannot be
-broken across a line break.)
-To get ``$\sim$'' type ``\verb.$\sim$.''.
-Also see the {\tt url} package, which lets you write
-\verb|\url{http://www.cs.georgetown.edu/~maloof}|, typeset as
-\url{http://www.cs.georgetown.edu/~maloof}.
-
-\subsection{What are \textit{italics} used for?}
-
-All of the things that would be underlined in a handwritten document,
-including titles of books, foreign words, and the like.
-
-In linguistics, it is normal to put foreign words in italics and their
-definitions in single quotes.  For example, Agatha Christie's famous
-detective is named after the French word \emph{poireau} `leek'.
-
-\subsection{What is \underline{underlining} used for?}
-
-Almost nothing.  Roman type is not normally underlined; use italics instead.
-
-\subsection{What is \mbox{\tt typewriter} \mbox{\tt type} used for?}
-
-Computer program languages, whether displayed or quoted in text.  For
-example, here is part of a program written in C:
-\begin{verbatim}
-for ( i = 100; i > 0; i-- ) {
-   printf("%d bottles of beer on the wall...\n", i);
-}
-\end{verbatim}
-It demonstrates how to use the \verb"for" statement to count down from
-100 to 1.
-
-\subsection{What is the \mbox{\tt verbatim} environment used for?}
-
-Computer programs, as just demonstrated.
-
-\subsection{What is \mbox{\sf sans-serif type} used for?}
-
-Almost nothing except labels within illustrations.
-
-\section{Bibliographies}
-
-\subsection{How do I type the bibliography?}
-
-See Lamport's book \cite{lamport.94}
-and the examples in {\tt gusample.tex}.
-\LaTeX\ lets you refer to bibliography items in your text
-with markers such as
-\verb|\cite{lamport.94}|.
-then have \LaTeX\ automatically turn these into bracketed numbers in
-the bibliography.
-
-With {\tt guthesis.sty}, simply use the \verb.thebibliography. environment
-exactly as Lamport describes it.  This will produce a bibliography in
-the form of an unnumbered chapter at the end of your thesis.
-
-\subsection{What if each chapter has its own bibliography?}
-
-If you have bibliographies at the ends of the individual chapters, use the
-environment {\tt chapterbibliography} instead of {\tt thebibliography}.
-It works \emph{exactly} the same way except that the bibliography
-becomes a normally numbered section, not an unnumbered chapter.
-There is an example of this in {\tt gusample.tex}.
-
-The {\tt chapterbibliography} environment is provided by {\tt guthesis.sty}.
-
-\subsection{What if I don't like bracketed numbers?}
-
-Here is an example of a trick to get \LaTeX\ to print a bibliography without
-bracketed numbers.  Basically, you are telling \LaTeX\ to put the author's
-name in place of the bracketed number.  Note that this involves using
-\verb.\item. rather than \verb.\bibitem..
-\begin{verbatim}
-\begin{thebibliography}{}
-
-\item[Covington, Michael A.]
-\emph{Natural Language Processing for Prolog Programmers.}
-Englewood Cliffs, N.J.: Prentice Hall, 1994.
-
-\item[O'Keefe, Richard A.]
-\emph{The Craft of Prolog.}
-Cambridge, MA: MIT Press, 1991.
-
-\end{thebibliography}
-\end{verbatim}
-When doing this,
-don't use the \verb"\cite" command; instead, handle your references manually.
-You can do \emph{exactly} the same thing with \texttt{chapterbibliography}.
-
-\section{Layout and illustrations}
-
-\subsection{How do I turn off justification?}
-
-Justification means printing with a straight right margins.  It is not required
-for Georgetown University theses, and if your text contains many formulas, web
-addresses, or other unbreakable items, you may get considerably neater results
-by turning it off.  To do this, issue the command
-\begin{verbatim}
-\raggedright
-\end{verbatim}
-immediately after \verb.\begin{document}..
-
-You may need to turn off justification only within a bibliography.
-In that case, you should put the \verb.\raggedright. command right after
-\verb.\begin{thebibliography}.
-or right after
-\verb.\begin{chapterbibliography}.
-as the case may be.  It will then affect only the bibliography.
-
-\subsection{How do I put a picture into my thesis?}
-
-See Lamport's book.  Here's the basic process...
-\begin{enumerate}
-
-\item Learn the difference between a vector (``draw'') program and a bitmap
-(``paint'') program.  Vector programs,
-such as xfig, OpenOffice Draw, Corel Draw, and Micrografx Windows Draw,
-tell the computer to draw lines at particular positions;
-they are the right tool for generating diagrams of all types.  Bitmap
-programs are \emph{only} for working with digitized photographs and the
-like; their output has an unpleasant stairstep appearance when enlarged
-or resized.
-
-\item Produce professional-quality artwork.  (You may want to hire a
-professional illustrator.)
-Artwork in your thesis should look as good as the artwork in published books.
-
-\item Save your artwork as an encapsulated PostScript (EPS) file
-\emph{with no TIFF header}.
-(The drawing software may ask you whether you want a TIFF header; say no.)
-
-\item Use the \texttt{graphics} package (described in Lamport's book) or the
-\texttt{epsf} package to incorporate your art into your \LaTeX\ document.
-One way to do this is as follows:
-\begin{enumerate}
-\item Add the command \verb.\usepackage{graphicx}. right after
-\verb.\documentclass..
-\item Use the command \verb"\centerline{\includegraphics{xxxxxxx.eps}}"
-(with the appropriate filename substituted) to put the picture in your
-document.  Normally this will be within a \verb.figure. environment as
-described in Lamport's book.
-\end{enumerate}
-\end{enumerate}
-
-\subsection{How do I put a Windows screen shot into my thesis?}
-
-When writing about software, you many need a picture of the computer screen
-with a program running.
-Under Windows 95 and up, you can ``take a picture'' of the screen, by
-pressing Print Screen
-(or Alt-Print Screen if you only need the current window).
-This puts a copy of the screen into the Windows clipboard.  Then open up
-your favorite paint program (bitmap program) and choose Paste.  Edit
-the picture to your satisfaction, save it, and export it as encapsulated
-PostScript.  For the rest of the process, see the previous question.
-
-\chapter{The Craft of Scholarly Typing}
-
-\section{An exhortation}
-
-If you have come to the University for a graduate degree, scholarly writing
-is one of the crafts
-in which you are being trained.
-This includes scholarly typing and word processing.
-We assume that you will be writing about your subject for the rest of your
-life.
-This is more likely to be true than you realize.
-
-\LaTeX\ provides you with all the tools of fine book printing.
-This includes quite a few things that were not available on typewriters.
-Accordingly, when using \LaTeX, you must learn some new things about printed
-language.
-
-\section{Some common punctuation errors}
-
-\subsection{Hyphens and dashes}
-
-\LaTeX\ distinguishes four kinds of horizontal lines between characters.
-
-\begin{itemize}
-\item The minus sign, $-$ (typed \verb"$-$"),
-is used only in math mode.  Always go into math mode when you want to mark
-a number as negative.
-
-\item The hyphen, - (typed \verb"-"), is used between parts of a word, as in
-``so-called'' or ``heavy-handed.''
-
-\item The short dash (en dash), -- (typed \verb"--"), goes between numbers
-in sequences, as in ``1861--65.''
-
-\item The long dash (em dash), --- (typed \verb"---"), goes between parts
-of sentences and may be set off by spaces --- like this.
-In good writing, it is uncommon; as alternatives, consider using a semicolon
-or starting a new sentence.
-\end{itemize}
-
-\subsection{Quotation marks}
-
-In \LaTeX\, you must type your quotation marks \verb"``like this''" in order
-to get them to print correctly ``like this.''  It is not correct to type
-"like this."
-
-Periods and commas ``slide under'' quotation marks so that they adhere to
-the words within them.
-Correct usage looks ``like this.''  Incorrect usage looks ``like this''.
-
-In computer science and linguistics, this rule sometimes does not apply,
-because it may be important to show that the period or comma is not part
-of the quoted material.  If you cannot get around this by rearranging the
-sentence, it is acceptable to put the period or comma outside the quotes.
-
-Single quotation marks (`like this') are used in linguistics to give the
-meanings of words.  Thus, French \emph{chateau} `castle' comes from Latin
-\emph{castellum} `fortress.'
-
-\subsection{Punctuation around mathematical formulae}
-
-Do not let the punctuation of your sentence intrude into a displayed
-mathematical formula.
-When a sentence ends with a displayed formula, end the sentence with a colon.
-Thus we conclude:
-\[
-a = \sum_{x=1}^\infty p(x) = q(x)
-\]
-The formula does not end with a period.
-
-\section{Knowing the character set}
-
-Part of knowing your subject is knowing its notation.
-If you are vague on the difference between $\emptyset$ and $\phi$, or
-$\omega$ and $w$, consult some well-produced reference books
-(not scruffily typed conference papers).
-
-Remember that in good printing, \emph{underlining is almost never used.}
-Underlining is the handwritten way of indicating italics.
-Now that you have italics, use them.
-Instead of wavy underlining (for vectors, etc.), use boldface.
-
-\section{Figures and tables}
-
-In a well-produced book, figures and tables do not interrupt the text like
-mathematical formulae.
-Instead, they ``float'' to the nearest convenient location and are identified
-by number.
-If there is no convenient place at the top or bottom of a page, they are
-placed on a separate page.
-
-\emph{See Lamport's book to learn how to control the placement of figures
-and tables.}
-Nothing is added or changed by {\tt guthesis.sty} --- \LaTeX\ still works exactly
-the way Lamport says.
-
-\begin{figure}
-\begin{center}
-\framebox{A picture could go here.}
-\end{center}
-\caption{This is an example of a figure.}
-\label{myfig}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\framebox{A picture could go here.}
-\end{center}
-\caption{This is another example of a figure.}
-\label{myfigtwo}
-\end{figure}
-
-Near here, you will see Figures~\ref{myfig} and~\ref{myfigtwo}.  Note that
-each picture's caption comes below it.  That is achieved by putting
-the \verb"\caption" command \emph{after} the figure.
-
-\begin{table}
-\caption{Some institutions and their mascots.}
-\label{mytb}
-\begin{center}
-\begin{tabular}{|c|c|c|}
-\hline
-\bf Institution & \bf Location & \bf Mascot \\
-\hline
-University of Georgia  & Athens & Bulldawg \\
-Georgetown University  & Washington  & Bulldog \\
-Georgia Tech  & Atlanta  & Insect \\
-UCSC  &  Santa Cruz  & Banana Slug\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Near here, you will also see Table~\ref{mytb}.  Its caption
-comes above it.  This is achieved by putting
-the \verb"\caption" command \emph{before} the table.
-
-\chapter{More Nonsense about \LaTeX}
-
-In this chapter, we talk about more \LaTeX\ things.
-Suspendisse potenti. Proin justo lorem, rutrum ac, facilisis in,
-malesuada sed, ligula. Mauris lobortis lacus at nibh. Aenean vitae
-odio vel odio placerat hendrerit. Suspendisse lacus lacus, tempor id,
-pharetra eget, ornare sit amet, pede. Sed aliquet, justo ac elementum
-pretium, arcu leo placerat est, a luctus purus diam eget arcu. Nam
-augue diam, mollis a, scelerisque eget, aliquet condimentum, pede.
-Vestibulum tristique lectus sed augue.
-
-\section{Introduction}\label{sec:intro}
-
-Aenean ut mauris luctus mauris interdum convallis. Nunc vestibulum
-sodales nulla. Nulla vitae massa. Maecenas vel tellus vitae elit mattis
-adipiscing. In pulvinar felis sed est. Mauris non mi. Duis ultrices dolor
-ut orci. Quisque lacinia arcu et purus. Sed euismod metus nec augue.
-
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur
-ridiculus mus. Nunc dolor leo, aliquam a, placerat sit amet, accumsan
-eget, dolor. Sed lacinia augue in magna. Fusce sed enim. Vestibulum et
-mauris. Phasellus in lectus. Pellentesque eu elit in dolor ullamcorper
-sodales. Vestibulum interdum ornare ligula. Mauris felis odio, rhoncus
-sed, adipiscing fermentum, tincidunt eu, metus. Suspendisse viverra
-rhoncus purus.
-
-Fusce euismod nisi at libero malesuada consectetuer. Proin laoreet, nunc
-quis hendrerit gravida, neque leo placerat sapien, et semper tortor leo
-et urna. Ut tincidunt posuere tortor. Sed tristique, odio at luctus
-facilisis, nulla quam rhoncus tortor, at congue lacus elit nec metus.
-Sed tempor sapien ut elit. Donec ac turpis feugiat nisi porta vehicula.
-
-\comment{
-This is an example of a block comment
-}
-
-\section{Problem Statement}\label{sec:problem}
-
-This is a test.  Blah, blah, blah. $\Pr(A) = \Pr(A) + \Pr(B|A)$.
-We discuss this issue in Section~\ref{sec:method}.  Indeed, we have
-\[
-\sum^{n}_{k = 1}{f(k)} \; ,
-\]
-where $f(k)$ is my favorite function.
-
-\section{Related Work}\label{sec:related}
-
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit \cite{breiman.ml.96}.
-Phasellus non erat eu dui dignissim dictum.
-Integer iaculis nulla at nisl \cite{jaynes.mebm.90}.
-Proin ut enim non ipsum varius laoreet \cite{muslea.aaai.00,sahai.00}.
-Integer feugiat, ante fringilla blandit
-convallis, leo sapien egestas velit, non condimentum nulla sem vitae
-risus. Mauris aliquam auctor quam. Sed ac enim. Donec mattis dui id
-ligula. Integer vel sem eget ante cursus tristique. Nullam vel orci
-vitae sem interdum placerat. In eget lectus. Donec blandit. Quisque
-lacus urna, malesuada vel, mollis sit amet, rutrum nec, est. Proin
-blandit ornare nibh. Duis et felis \cite{pfleger.tr.97}.
-
-\section{Approach}\label{sec:approach}
-
-Here is an example of code:
-
-\begin{verbatim}
-int main()
-{
-  cout << "testing" << endl;
-  return 0;
-} // main
-\end{verbatim}
-Text.
-Plain text. {\em Emphasized text.} {\it Italicized text.}
-{\bf Boldfaced text}.  {\tt typewriter text.} {\large Large text.}
-Our results appear in Table~\ref{tab:results}.
-In their paper \cite{muslea.aaai.00},
-they discuss a lot of interesting things.
-
-Em dash --- which is followed by an en dash -- and then we have
-eloquently-hyphenated words, which are not to be confused with
-the minus sign: $-$.  All are different \cite{shamos.phd.78}.
-
-Here is a quote:
-\begin{quote}
-Ask not what your country can do for you.  Ask what you can do
-for your country.
-\end{quote}
-
-In Figure~\ref{alg:min}, we present an algorithm for finding the
-minimum component of a vector.
-But there are other ways to present algorithms.
-Some have started using the {\tt algorithm} and {\tt algorithmic}
-packages.
-See Algorithm~\ref{alg:pair} as an example.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Nam iaculis,
-felis nec semper malesuada, quam metus placerat ligula, id euismod purus
-eros eget justo. Pellentesque ipsum. In hac habitasse platea dictumst.
-Ut pede pede, sagittis sit amet, dapibus eu, tristique in, ipsum
-\cite{kolter.icml.05}.
-
-\begin{figure}[t]
-\begin{quote}
-\begin{tabbing}
-XX\=XX\=XX\=XX\=XX\=XXXXXXXXXXXXXXXXXX\= \kill
- \> {\sf Algorithm}\,$( \; \vec{x} \; )$ \\[\smallskipamount]
- \>\> $\vec{x}$: vector of numbers \\
- \>\> $i$: index of minimum value \\
- \>\> $\mbox{\em min}$: minimum value \\[\smallskipamount]
-\parbox{3ex}{\hfill 1.} \>\> $m \leftarrow \infty$ \\
-\parbox{3ex}{\hfill 2.} \>\> {\bf for} $j \leftarrow 1, \ldots, n$
-\>\>\>\> // Loop over components \\
-\parbox{3ex}{\hfill 3.} \>\>\> {\bf if} $( \vec{x}_{j} < \mbox{\em min} )$ \\
-\parbox{3ex}{\hfill 4.} \>\>\>\> $\mbox{\em min} \leftarrow \vec{x}_{j}$ \\
-\parbox{3ex}{\hfill 5.} \>\>\>\> $i \leftarrow j$ \\
-\parbox{3ex}{\hfill 6.} \>\>\> {\bf end}; \\
-\parbox{3ex}{\hfill 7.} \>\> {\bf end}; \\
-\parbox{3ex}{\hfill 8.} \>\> {\bf return} $i$ \\
-\> {\bf end.}
-\end{tabbing}
-\end{quote}
-\caption{Algorithm for finding the minimum component of a vector.}
-\label{alg:min}
-\end{figure}
-
-\paragraph{Paragraph.} Something you may never use, kind of like
-Latin.\footnote{And footnotes.}
-Aliquam fermentum velit tristique turpis. Mauris mollis dapibus purus.
-Quisque vulputate ullamcorper purus. Quisque aliquam rhoncus felis.
-Aenean fringilla mattis mi. Ut ut massa a sem fermentum venenatis.
-Fusce ut risus. Maecenas ut nisl. Praesent felis erat, tincidunt ac,
-placerat vel, sodales vel, justo. Vivamus semper sollicitudin est.
-Morbi id eros eu tellus dignissim viverra \cite{breiman.ml.96}.
-
-\begin{algorithm}[tb]
-  \caption{Paired Learner}
-  \label{alg:pair}
-  \begin{algorithmic}[1]
-    \STATE {\bfseries Input:} $\{ \vec{x}_t, y_t \}^{T}_{t=1}$, $w$, $\theta$
-    \vskip 0.3em
-    \STATE $\{ \vec{x}_t, y_t \}^{T}_{t=1}$: training data
-    \STATE $w$: window size for the reactive learner
-    \STATE $\theta$: threshold for creating a new stable learner
-    \vskip 0.3em
-    \STATE Let $S$ be a stable learner
-    \STATE Let $R_{w}$ be a $w$-reactive learner
-    \STATE Let $C$ be a circular list of $w$ bits, each initially $0$
-    \FOR{ $t \leftarrow 1$ {\bfseries to} $T$ }
-    \STATE $\hat{y}_{S} \leftarrow S.\mbox{\sf Classify}( \vec{x}_{t} )$
-    \STATE {\bfseries output} $\hat{y}_{S}$
-    \STATE $\hat{y}_{R} \leftarrow R_{w}.\mbox{\sf Classify}( \vec{x}_{t} )$
-    \IF{ $\hat{y}_{S} \neq y_{t} \wedge \hat{y}_{R} = y_{t}$ }
-    \STATE $C.\mbox{\sf set}( t )$
-    \ELSE
-    \STATE $C.\mbox{\sf unset}( t )$
-    \ENDIF
-    \IF{ $\theta < C.\mbox{\sf proportionOfSetBits}()$ }
-    \STATE $S \leftarrow \mbox{\bf new } \mbox{\sf StableLearner}()$
-    \STATE $S \leftarrow R_{w}.\mbox{\sf getConceptDescription}()$
-    \STATE $C.\mbox{\sf unsetAll}()$
-    \ENDIF
-    \STATE $S.\mbox{\sf Train}( \vec{x}_{t}, y_{t} )$
-    \STATE $R_{w}.\mbox{\sf Train}( \vec{x}_{t}, y_{t} )$
-    \ENDFOR
-  \end{algorithmic}
-\end{algorithm}
-
-Text.  See Figure~\ref{fig:design}.
-Nullam massa est, facilisis at, egestas non, lobortis at, felis.
-Vestibulum eu velit ut justo commodo pretium. Quisque commodo velit
-vel sem. Cum sociis natoque penatibus et magnis dis parturient montes,
-nascetur ridiculus mus. Donec nec magna. Aliquam erat volutpat.
-
-\begin{theorem}[Kolter and Maloof \cite{kolter.icml.05}]
-\label{addexp.d-mistake-1}
-For any time steps $\mathrm{t_1} < \mathrm{t_2}$, if we stipulate that
-$\beta + 2\gamma < 1$, then the number of mistakes that \textbf{AddExp.D}
-will make between time steps $\mathrm{t_1}$ and $\mathrm{t_2}$ can be
-bounded by
-\[
-M_{t_2} - M_{t_1} \leq
-\frac{\log (W_{t_1} / W_{t_2})}{\log (2/(1+\beta+2\gamma))} \; .
-\]
-\end{theorem}
-
-\begin{proof}
-\textbf{AddExp.D} operates by multiplying the weights of the experts that
-predicted incorrectly by $\beta$.  If we assume that a mistake is made at
-time step $t$ then we know that at least $1/2$ of the weight in the
-ensemble predicted incorrectly.  In addition, a new expert will be added
-with weight $\gamma W_t$.  So we can bound the weight with
-\[
-W_{t+1} \leq \frac{1}{2}W_t + \frac{\beta}{2}W_t + \gamma W_t =
-\frac{1+\beta +2\gamma}{2} W_t \; .
-\]
-Applying this function recursively leads to:
-\[
-W_{t_2} \leq \frac{1+\beta+2\gamma}{2}^{M_{t_2} - M_{t_1}} W_{t_1} \; .
-\]
-Taking the logarithm and rearranging terms gives the desired bound, which
-will h old since the requirement that $\beta + 2\gamma < 1$ ensures that
-$(1 + \beta + 2\gamma)/2 < 1$. \qed
-\end{proof}
-
-\section{Experimental Study}\label{sec:study}
-
-Always put something here, even if it just informs the reader of what
-comes next.
-Integer odio lorem, aliquam id, dignissim in, varius at, neque. Class
-aptent taciti sociosqu ad litora torquent per conubia nostra, per
-inceptos himenaeos. Maecenas vitae massa ultrices lorem aliquam pharetra.
-In hac habitasse platea dictumst. Nunc consectetuer sapien. Maecenas ut
-felis. Sed blandit congue mauris. Donec ornare laoreet tortor. Cum sociis
-natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-Fusce id neque ac enim lobortis aliquet. Sed a purus ac nunc feugiat
-interdum. Suspendisse risus. Donec pulvinar, turpis at rutrum porta,
-justo massa iaculis quam, vel pharetra leo magna et metus. Etiam tellus
-dolor, volutpat et, dignissim vel, iaculis in, sem. Donec ante est,
-ultricies non, eleifend in, pretium id, nisl. Fusce vitae nunc.
-Vivamus egestas. Vestibulum nibh. Aliquam rutrum imperdiet diam.
-
-\begin{figure}[t]
-\centerline{\includegraphics[width=1.0in]{state.eps}}
-\caption{A pretty picture.} \label{fig:design}
-\end{figure}
-
-\subsection{Method}\label{sec:method}
-
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Sed vitae risus.
-Vivamus dapibus, quam vehicula eleifend vestibulum, pede magna iaculis
-leo, quis convallis nisl mauris id arcu. Morbi tincidunt odio at libero.
-Mauris molestie. Proin placerat, neque sit amet eleifend ullamcorper,
-arcu sem ornare arcu, a adipiscing metus felis eu turpis. Integer bibendum
-nisi placerat quam. Donec id enim. Sed neque ipsum, ullamcorper vitae,
-bibendum nec, pharetra quis, quam. Curabitur suscipit aliquet ligula.
-Aenean pede.
-
-Cras molestie turpis ac lorem. Vivamus molestie porta purus. Nulla
-facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-Fusce fermentum, ante in vestibulum auctor, turpis tellus aliquam est,
-in accumsan massa tortor id magna. Mauris sit amet libero. Donec orci dui,
-interdum in, sollicitudin id, adipiscing quis, nulla. Sed ante orci,
-sagittis at, egestas ut, egestas nec, leo. Cras malesuada dolor sed diam.
-Ut lobortis velit sodales nunc.
-
-\input table.tex
-
-Duis vestibulum lacus eget dolor. Proin at quam. Phasellus viverra molestie
-nisl. In non elit et felis commodo suscipit. Phasellus consectetuer purus.
-Donec lobortis sagittis ante. Vestibulum hendrerit blandit quam.
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames
-ac turpis egestas. Duis vel quam. Proin dictum. Donec laoreet scelerisque
-nisi. Sed at urna et justo vulputate tristique. Aenean interdum. Quisque
-in tortor. Morbi eget purus. Vestibulum ante ipsum primis in faucibus orci
-luctus et ultrices posuere cubilia Curae; Etiam semper.
-
-\begin{figure}
-\centerline{\includegraphics[scale=1.0]{plots/stagger.stagger.ps}}
-\caption{Results.} \label{fig:results}
-\end{figure}
-
-\subsection{Results}\label{sec:results}
-
-In Table~\ref{tab:results}, we present the results of our study.
-In Figure~\ref{fig:results}, we present the results of our study.
-Aliquam fermentum velit tristique turpis. Mauris mollis dapibus purus.
-Quisque vulputate ullamcorper purus. Quisque aliquam rhoncus felis.
-Aenean fringilla mattis mi. Ut ut massa a sem fermentum venenatis.
-Fusce ut risus. Maecenas ut nisl. Praesent felis erat, tincidunt ac,
-placerat vel, sodales vel, justo. Vivamus semper sollicitudin est.
-Morbi id eros eu tellus dignissim viverra.
-
-\subsection{Analysis}\label{sec:analysis}
-
-Nulla odio. Phasellus congue malesuada quam. Pellentesque non lectus
-at nisi venenatis faucibus. Proin gravida diam vitae pede. Morbi sit
-amet dolor. Pellentesque feugiat tortor ut est. Ut sodales augue non
-velit.
-
-Duis arcu. Nam ac mauris. Pellentesque eleifend tellus ac eros.
-Maecenas varius massa eu nunc mollis imperdiet. Donec interdum, lorem
-in vestibulum feugiat, elit arcu fringilla ante, et sollicitudin ipsum
-sapien a turpis. Proin sit amet nisl id metus hendrerit volutpat.
-
-\section{Conclusion}\label{sec:conclusion}
-
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit.  Duis cursus.
-Duis consectetuer, lacus id vehicula viverra, dolor quam dignissim pede,
-nec ultrices metus tortor quis turpis.
-Praesent non orci non est tincidunt mollis.
-Nullam pellentesque auctor orci.
-Morbi aliquam.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur
-ridiculus mus.
-
-In auctor ornare risus.
-Nulla id magna nec pede elementum rhoncus.
-Suspendisse ultricies mattis lacus.
-Cras pulvinar pede nec dolor.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
-Suspendisse potenti.
-Sed pede massa, scelerisque id, tempor ac, vestibulum nec, est.
-Maecenas molestie tincidunt orci.
-Donec ac leo quis libero iaculis semper.
-Aenean ligula pede, semper eu, tristique eu, aliquam in, nisi.
-Curabitur sagittis condimentum ligula.
-Nunc interdum suscipit libero.
+TODO
 
@@
 
-\chapter{Important Note About Margins}
-\label{mgins}
+\chapter{Sample appendix}
+SAMPLE
+\section{Sample section}
+SAMPLE
 
-\section{General tactics}
-No two printers are alike.  Please print a few pages and \emph{measure} them.
-\LaTeX\ can send commands to your printer, but it can't see whether they are
-being obeyed!
-
-Check the {\tt dvips} problem described below.
-If, after tackling that,
-you still need to make adjustments to get correct margins on paper
-(1.5 inches on the left and 1 inch on the right),
-add commands such as:
-\begin{verbatim}
-\hoffset = 0.5in    % shift 0.5 inch to the right
-\voffset = -0.1in   % shift 0.1 inch up
-\end{verbatim}
-in your \verb".tex" file right after after \verb"\usepackage{gu}".
-
-\section{The A4 problem}
-
-If your printouts are consistently too high or too low on the page,
-and you are generating PostScript files
-using the {\tt dvips} command, you are probably generating output for
-A4 (11.7-inch) paper.
-
-That is the size of paper used in Europe.
-American (``letter'') paper is only 11 inches long and is the size specified
-for Georgetown theses and dissertations (and their electronic images).
-
-As a quick check, try
-typing the {\tt dvips} command with the argument {\tt -tletter}, like this:
-\begin{flushleft}
-{\tt dvips -tletter {\it filename}}
-\end{flushleft}
-If that cures the problem, you can fix it permanently by editing the file
-{\tt config.ps} to make letter size (11-inch) paper the default.
-See the {\tt dvips} documentation for details.
-
-\chapter{Customizing the Table of Contents}
-
-On rare occasions the table of contents will not come out formatted
-the way you'd like.  Here's how to control it. \emph{Most people will
-not need to do this} and can ignore these notes.
-
-Every time you run \LaTeX, it writes the table of contents on a file
-whose name ends in \verb".toc", and reads and prints the \verb".toc" file
-from the \emph{previous} run.
-That's why you have to run \LaTeX\ twice to get a correct table of contents.
-
-If you need to alter your table of contents (e.g., by inserting a
-page break), you can edit the \verb".toc" file in between two runs of \LaTeX.
-For example, you can insert \verb"\newpage" to generate a page break.
-Note that this change will not last because \LaTeX\ will write a new
-\verb".toc" file ever time it runs.
-
-Alternatively, you can add a command to your \verb".tex" file that will
-add something to the contents.  For example, just before beginning
-a particular chapter, you can execute the command:
-\begin{verbatim}
-\addtocontents{toc}{\newpage}
-\end{verbatim}
-to cause a page break at the corresponding place in the table of
-contents.
-
-\chapter{Common PDF Problems}
-
-When you convert your thesis from PostScript to PDF (with
-Adobe Acrobat Distiller or other suitable software), you may discover
-two problems.
-
-\section{Text shrinks when converted to PDF}
-
-This may mean that your PostScript file was formatted for A4
-(11.7-inch) paper, and PDF is shrinking it to fit on American 11-inch
-paper.  See p.\ \pageref{mgins}.
-
-\section{Type looks blurred or pixellated}
-
-This generally means you are using the old bitmap versions of the
-\TeX\ fonts rather than the PostScript versions.  As a quick check, try
-adding the command \verb"\usepackage{times}" right after \verb"\documentclass".
-This will change the typeface.  If the new typeface looks a lot
-smoother, you've identified the problem but not cured it.
-
-To get the PostScript \TeX\ fonts, get your system support people to
-reconfigure {\tt dvips}, or download and install a newer version,
-or simply run \LaTeX\ on a computer that has more up-to-date software.
-
-Please note that PDF conversion is not affected by \verb"guthesis.sty" and the
-author of \verb"guthesis.sty" cannot undertake to solve other problems with it.
-
-\chapter{How to Cite Web Pages}
-
-Your bibliography entries should follow whatever format is standard in your
-field.
-If completely stymied, see the \emph{Chicago Manual of Style} (which gives
-\emph{two} formats, one for humanities and one for sciences; don't mix them
-up) or the \emph{Publication Manual} of the American Psychological Association.
-
-Even so, you will probably still be in doubt about how to cite web pages.
-The way I see it, the Web is not a publisher.  Thus, a web address is not
-a sufficient citation for a web page.
-Instead, you must cite the document itself (indicating where and when it
-originated) and then add information about the web address.
-
-If the paper has been published, and you got a copy from the author's web
-site, your job is easy.  Just do something like this:
-\begin{quote}
-Newton, Isaac (1672) On the refraction of coloured light.
-\emph{Journal of Irreproducible Results} 23:456-789.
-Web: \url{http://www.trinity.cam.ac.uk/new\-ton/colour.pdf}.
-\end{quote}
-That is, add the web information at the end of a normal citation.
-
-If the paper is available only on the author's web site (at an institution
-or corporation), cite the institution or corporation as the publisher,
-something like this:
-\begin{quote}
-Newton, Isaac (1672)  On the refraction of coloured light.  Trinity College,
-Cambridge.  Web: \url{http://www.trinity.cam.ac.uk/newton/colour.pdf}.
-\end{quote}
-The idea is to cite it just like a privately distributed paper except that
-you add the web address.
-
-If the web site \emph{is} a publisher (e.g., an online journal), then it
-will probably give instructions for citation.
-Do not copy numbers into a bibliography entry if you don't know what they
-mean.
-
-Consult your major professor for more advice, since the details will depend
-on other aspects of your bibliography format.
-
-Note that the character $\sim$ in web addresses is typed \verb"$\sim$",
-unless you use the {\tt url} package.
-
-Note also that by itself, \LaTeX\ will not hyphenate a URL.  It is up to you
-to indicate with the symbol \verb"\-" the places where hyphens are permitted.
-Always hyphenate within words, not between compound words, so that the reader
-will know that the hyphen was not present in the original.
+\chapter{Second sample appendix}
+SAMPLE
 
@@
 
-\typeout{***}
-\typeout{*** Note!}
-\typeout{*** Because this document has a table of contents,}
-\typeout{*** you must run LaTeX TWICE to get it to print correctly.}
-\typeout{***}
-
 \end{document}

### 2023-02-01 paper.tex
Sections
Cleanup
Initial drafting

@@
 \usepackage[numbers,sort]{natbib}
-\usepackage[dvips]{graphicx}
+\usepackage{graphicx}
 \usepackage{amsmath}
@@
 
-\usepackage{template/guthesis} % Must be the last package
+\usepackage{lib/style/guthesis} % Must be the last package
 
@@
 
-\fulltitle{Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking}
+\fulltitle{Peering Through Censorship: Tackling Internet Censorship Using P2P Networking}
 
@@
 
-TODO
+People us the internet to communicate and share a variety of content.
+Some entities choose to censor internet connections.
+These entities may range from individual network administrators to a full nation-state.
+In this paper, we explore the background and current state of censorship circumvention, and then design and build a system which tackles several of the limitations present in state of the art systems.
+[LATER: Add xrefs to sections]
+
+We begin by exploring what we mean by censorship circumvention and establishing baseline terminology for this subdiscipline.
+We then explore the present theory behind approaches to censorship circumvention.
+We address the ethics of censorship circumvention as a field, and how the field originated and how that affects the current state of the field.
+
+We then propose several ways to classify existing systems to allow for some comparison between them, and we then explore existing and past systems to understand where the field stands, and where limitations occur.
+We emphasize systems that are either cutting edge or in active use in the real world.
+
+We also provide an overview of the state of peer to peer (P2P) networking, focusing on succesful project operating in the real world.
+We provide a deeper dive into the Interplanetary File System (IPFS) and the underlying networking library, LibP2P.
+These programs are used extensively in out proposed system.
+
+Having outlined what is and has succeeded in censorship circumvention in both the real world and theory, we propose a system that addresses the flaws of the current cutting edge systems.
+We call this system CN.
+[TODO: fn code name] We discuss the architecture of this system, putting a particular emphasis on the underlying data structure and network topology.
+
+We build this system and build a benchmarking tool and other apps on top of this system.
+We use this benchmarking tool to show that the system functions with strong performance.
+We then begin to simulate a censor based upon theoretical and real world adversaries, and then benchmark the system again, showing that even under severely censored circumstances, we are able to maintain [adequate/good/strong] performance.
+We also explore what regions of the world would have to operate in more censored circumstances at present.
+
+We then conclude and offer some opportunities for future work.
 
@@
 
-TODO
+When we discuss the subfield of censorship circumvention when discussing networking and security, we are \emph{not} discussing all forms of censorship that a web user might face - we are discussing censorship on-the-wire of active internet traffic, which usually consists of blocking access to specific services.
+We do not consider a service blocking certain conduct (e.g.
+a social network restricting hate speech) the censorship that we are circumventing.
+We aim to allow a use to connect to any service they would like (notwithstanding technical limitations) - not to allow a user to use any service how they would like.
+Throughout this paper, when we mention censorship, we mean on-the-wire censorship of reaching services.
+
+\subsection{Ethics}
+
+We recognize that some users run heinous services on the web - most of which are illegal in any existing jurisdiction.
+We believe that the best approach for ceasing access to these heinous services is best done through a legal system - ie, investigating and identifying the perpetrator(s), turning off the service directly, and prosecuting any perpetrator(s) of said acts.
+We note that most morally reprehensible acts that are frequently associated with anonymity and censorship circumvention systems involve actions that occur in the real world (e.g.
+exploitation of children, weapon/drug/human trafficking all involve actions that occur in the real world either prior to distribution on the internet or triggered by actions on the internet).
+
+The only notable class of crime which can occur without physical, real-world actions is piracy/IP violations.
+We believe that targetted legal actions (e.g.
+DMCA takedowns) can mitigate the issue, and that the cost of further mitigation through censorship would lead to large collateral damage of legal content and a chilling effect of legal speech and usage of the web, and as such the possibility of a circumvention system being used for piracy/IP violations is an acceptable risk given the ability to mitigate damage through the legal system.
+
+\subsection{Threat model and adversary}
+
+Censorship circumvention is an abstract concept, and approaching it in a scientific way requires properly defining and scoping the task.
+We have already defined the task, [TODO: xref] and must now scope the problem.
+We will scope our problem by creating a \textbf{threat model} of the censor we are aiming to thwart, termed \textbf{the adversary}.
+
+An adversary has an \textbf{area of influence}.
+This is an area an adversary controls the network of, and can control (either directly or through compulsion) any service providers within.
+We assume an adversary may have an area of influcence consisting of several nations, with at least one nation outside of the area of influence of \emph{any} censor.\footnote{This does not mean that this nation does not have the technical capability to censor, but rather does not perform any censorship either directly or via threatening a start of censorship.}
+
+Our adversary has effectively infinite resources, but is bound by the laws of physics and as such is bounded by the difficulty of computational problems (and the known solutions to these problems, e.g.
+even if P=NP, the solution is not known, and as such cannot be used).
+These resources may include labor, capital, technical expertise, and total control of the legal system.
+
+We also assume that our adversary has access to the source code of any circumvention system available, and knowledge of the existence of our circumvention system.
+We discuss why security through obscurity cannot be used in an effective circumvention system in [TODO: xref].
+
+We also assume that our adversary only takes actions \textbf{on-the-wire} and at \textbf{service providers} within their area of influence - effectively, the adversary isn't interested in any individual in particular and is performing a dragnet operation, rather than an operation targetting a specific entity.
+We can use a thought experiment to justify this: if an adversary had a person looking over your shoulder or using video surveillance, they could simply look at what you are doing and punish you directly, no need to expend the resources needed to censor the web.
+
+We assume our adversary has some interest in the utility of the internet and certain technologies on the internet.
+This means two things: an adversary will not shut down the internet in it's entirety\footnote{Internet shutdowns are a trivial way to censor forbidden internet usage - at the expense of shutting down any non-forbidden usage.
+[TODO: Discuss prior shut downs in another section and xref]} and an adversary has some threshold of unacceptable collateral damage caused by potential censorship techniques.\footnote{Similar to a full internet shutdown, if an adversary wanted to block all access to a specific HTTP site, they could block \emph{all} HTTP traffic, at the expense of blocking every HTTP site.
+This piecemeal web censorship could even be thwarted with a circumvention system that simply proxies HTTP traffic outside of the area of influence within an unblocked protocol and connects to HTTP sites from outside the area of influcence.
+This starts to show that any non-complete shutdown of internet traffic may have gaps for circumvention techniques.
+We discuss collateral damage further in [TODO: xref].}
+
+Finally, we note that any technique that subverts this adversary will also work when weakening the strength of these assumptions - e.g.
+if the adversary controls one nation instead of several, we have more area to run a circumvention system from; if the adversary is only willing to take actions at service providers and not on-the-wire, anything that can thwart an adversary that takes both actions could trivially thwart the adversary that only performs actions at one.
+We also note that a system could detect the type of actions an adversary is taking and maximize performance based upon what subset of possible actions an adversary is taking - e.g.
+an adversary that is not touching services leaves an easy path for a circumvention system to use - those services themself.
 
@@
 
-\subsection{Ethics}
-
-TODO
+[TODO: Mention parrot is dead]
 
 \subsection{Origination of censorship circumvention}
-
-TODO
-
-\subsection{Taxonomy of censorship circumvention}
 
@@
 TODO
+
+[TODO: Do mention some things like shadowsocks that are in use but are even further from academics]
 
@@
 TODO
+
+[TODO: Iran case study]
 
@@
 
-\chapter{System design}
+\section{P2P networking}
 
@@
 
+\subsection{IPFS}
+
+TODO
+
+\chapter{System design}
+
+We saw that several circumvention systems work given the constraints they were designed for, however, these constraints are either too loose and have known real-world failures under our adversary model, the systems are too difficult to deploy, or they have hit scalability issues.
+
+We propose a system with a clear theoretical backing and acheivable goals based on both theory and real-world observations.
+
 \section{Theory and goals}
 
-TODO
+First, we want to define system goal and highlight some non-goals that are close to censorship circumvention, but are not directly used for them.
+
+We aim to thwart the adversary we outline in [xref]. We will rely heavily on the concept of collateral damage. [TODO: Discuss collateral damage further]
+
+We are \emph{not} aiming to provide anonymity.\footnote{Perhaps our system could be used to access an anonymity system, but we do not want to guarentee anonymity or guarentee that the system will not leak information that may break anonymity, though we are not delibrately trying to break anonymity, we are also not evaluating our system for it at this point.} We feel the need to emphasize this, as most current systems that are functional in the real world are used as pluggable transports by Tor.\footnote{Our system could be used as a PT, as we do have a golang implementation.} [TODO: Evaluate this further - it may actually be the case that it could be safe to use]
+
+\subsection{Comparing existing systems}
+
+Earlier, [TODO: xref] we discussed a variety of censorship circumvention systems.
+Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to acheive and working techniques we may use.
+We present a short summary of previous systems in [TODO: xref table], comparing and contrasting their succesful techniques and transports, and their individual drawbacks.
+
+\begin{table}
+\caption{Comparison of existing systems.}
+\begin{center}
+[TODO: Make table take whole page sideways, make in latex when finalized]
+\makebox[\textwidth]{\includegraphics[width=\paperwidth]{tables/comparison-draft.png}}
+\end{center}
+\end{table}
+
+We see that existing systems are limited by at least one of the following:
+\begin{itemize}
+  \item The bridge distribution problem [TODO: Xref]
+  \item Scalability
+  \item Deployment difficulty
+  \item Low bandwidth
+\end{itemize}
+
+[TODO: More]
 
@@
 
-\bibliographystyle{plainnat}
-\bibliography{gusample}
+\bibliographystyle{plain}
+\bibliography{lib/cites}
 

### 2023-02-01 paper.tex
Forgot to save

@@
 
-We are \emph{not} aiming to provide anonymity.\footnote{Perhaps our system could be used to access an anonymity system, but we do not want to guarentee anonymity or guarentee that the system will not leak information that may break anonymity, though we are not delibrately trying to break anonymity, we are also not evaluating our system for it at this point.} We feel the need to emphasize this, as most current systems that are functional in the real world are used as pluggable transports by Tor.\footnote{Our system could be used as a PT, as we do have a golang implementation.} [TODO: Evaluate this further - it may actually be the case that it could be safe to use]
+We are \emph{not} aiming to provide anonymity.\footnote{Perhaps our system could be used to access an anonymity system, but we do not want to guarentee anonymity or guarentee that the system will not leak information that may break anonymity, though we are not delibrately trying to break anonymity, we are also not evaluating our system for it at this point.} We feel the need to emphasize this, as most current systems that are functional in the real world are used as pluggable transports by Tor.\footnote{Our system could be used as a PT, as we do have a golang implementation, however, evaluating this system for usage as a PT is reserved for future work.}
 

### 2023-02-01 paper.tex
Updates

@@
 
-% TODO: Update this
-\indexwords{Word~processing, Computer~typesetting, Computer~graphics,
-            Style~sheets, Typography, Dissertations, Theses~(academic)}
+\indexwords{[TODO], Theses~(academic)}
 
@@
 
-TODO
+The web arose in a relatively haphazard fashion [TODO: discuss a bit more].
+The web was not a place where adversaries engaged in censorship (if they paid any mind to the web whatsoever).
+Instead, as the web became more prominent and more global, individuals realized that they could be tracked, and that they desired anonymity.
+This led to the development of anonymity software, with Tor being the most prominent example.
+Censorship circumvention arose as a by-product of goals that were not focused on censorship circumvention.
+As primitive censorship began (e.g.
+blocking specific IP addresses of an undesired server), people realized that software that proxies traffic (either in a basic fashion such as a proxy, or a more complex fashion such as Tor) could be used to access services that would otherwise be blocked on a local network.
+
+As this occurred, the web continued to grow in prominence, and the concept of "Web 2.0" arose - regular users could post content to sites such as message boards and social media sites.
+People could organize quickly and effectively across larger distances and with people they had never met in the past.
+Governments took notice.
+These sites began being blocked by these sites.
+Governments and other entities also saw that users were getting around these blocks by using proxies and anonymity software - and so they gathered the IP addresses of these services and blocked them.
+
+At this point, those who used and built the anonymity software recognized that censorship circumvention would be crucial for maintaining access to these tools, and others realized that censorship circumvention in-and-of itself would be useful.
+This effectively led to the rise of a subdiscipline that draws heavily from networking, security, and even game theory, but also exists independently from those subdisciplines, with a variety of stakeholders including governments, NGOs, non-profits, independent programmers, academics, and others interested in developing censorship circumvention techniques.
+This also leads to a relatively unique feature of this discipline - some techniques were developped in academia, some techniques were developped in the real world, and some were developped in both, and ignoring the results from either thread of research and observation can lead to the development of limited systems.
+
+[TODO: Mention Tor PTs independently of specific methods]
 
@@
 TODO
+
+[TODO: Others]
 
@@
 
+Another key observation is that \emph{collateral damage} is the bedrock of the theory behind a circumvention system - as such, any system must be based around maximizing this - the ideal system will make the only feasible way to shut down the system effectively shutting down a large portion of internet traffic.
+
+[TODO: Discuss false positives + the overhead of blocking traffic]
+
 [TODO: More]
+
+We also note that existing systems require a user to download and use specialized software, and that systems usually require using anonymity software such as Tor to reap the benefits of censorship circuvmention.
+While anonymity is a useful [thing] to have in some circumstances on the web, getting the drawbacks of common anonymity software [TODO: outline] is not ideal.
 

### 2023-02-02 paper.tex
Added figures dir

@@
 These entities may range from individual network administrators to a full nation-state.
-In this paper, we explore the background and current state of censorship circumvention, and then design and build a system which tackles several of the limitations present in state of the art systems.
+In this paper, we explore the state of censorship, existing circumvention sytems, and we design and build a system which tackles several of the limitations present in state of the art systems.
 [LATER: Add xrefs to sections]
 
-We begin by exploring what we mean by censorship circumvention and establishing baseline terminology for this subdiscipline.
+We begin by exploring what we mean by censorship circumvention and establishing baseline terminology for this discipline.
 We then explore the present theory behind approaches to censorship circumvention.
@@
 
-TODO
+The term censorship has taken on a life of it's own in the modern social and political context.
+We are \emph{not} exploring the general connotation of censorship, rather, we are exploring a specific type of censorship that existing in a networking (particularly internetworking) context.
 
@@
 
-\subsection{Current theory of censorship circumvention}
-
-TODO
-
-[TODO: Mention parrot is dead]
-
 \subsection{Origination of censorship circumvention}
@@
 [TODO: Mention Tor PTs independently of specific methods]
+
+\subsection{Current theory of censorship circumvention}
+
+TODO
+
+[TODO: Mention parrot is dead]
 

### 2023-02-02 paper.tex
Updates

@@
 \usepackage{algorithmic}
+\usepackage{svg}
 
@@
 We are \emph{not} exploring the general connotation of censorship, rather, we are exploring a specific type of censorship that existing in a networking (particularly internetworking) context.
+We will explore some key concepts and present a short model of networking.
+
+\section{Networking concepts}
+
+We are going to consider the internet as it currently exists, rather than historical states of the internet. Some key concepts:
+
+\begin{itemize}
+  \item Internet Protocol (IP) addresses: These are used to represent endpoints of a connection, and are used for routing.
+Within a network, other identifiers, such as MAC addresses, are used for routing, however, we are focused on routing between networks and will only consider IP based routing as we explore censorship circumvention.
+We will use IPv4 addresses throughout as sample addresses, though conceptually IPv6 addresses function similarly for the focuses of this paper.
+  \item Domain Name System (DNS): DNS resolution is used to map from human-readable and memorizable addresses that map to IP addresses (e.g.
+georgetown.edu resolved to 23.185.0.2 at the time of writing).
+[TODO: Explore the transparency of these, DNSSEC, etc]
+  \item Router: Routers perform routing for networking, as well as other functions that act on network traffic.
+They may be the home of a NAT, a firewall, or censorship software.
+The controller of a router may access and manipulate any traffic which passes through it.
+  \item Firewalls: These are software that may restrict traffic based on rules. These rules may be simple or complex. These have positive uses, such as securing a network from attacks.
+  \item Network address translation (NAT): A NAT is used to map network addresses seen on one side of a router to those seen on the other side of a router.
+These are frequently used to house potentially thousands of devices behind a single internet facing IP address.
+Most humans use devices located behind a NAT.
+\end{itemize}
+
+\begin{figure}
+\begin{center}
+{\includesvg{figures/networking}}
+\end{center}
+\caption{A model of networking, sufficient for exploring censorship circumvention [TODO: Add final arrows, some sample traffic]}
+\end{figure}
 
@@
 
-\subsection{Origination of censorship circumvention}
+[TODO: Basic model + adversary]
+
+\begin{figure}
+\begin{center}
+{\includesvg{figures/networking}}
+\end{center}
+\caption{A model of networking, with our adversary model overlaid [TODO: Once networking diagram is finalized, add an adversary]}
+\end{figure}
+
+\subsection{History and basics}
 
@@
 Instead, as the web became more prominent and more global, individuals realized that they could be tracked, and that they desired anonymity.
-This led to the development of anonymity software, with Tor being the most prominent example.
-Censorship circumvention arose as a by-product of goals that were not focused on censorship circumvention.
-As primitive censorship began (e.g.
-blocking specific IP addresses of an undesired server), people realized that software that proxies traffic (either in a basic fashion such as a proxy, or a more complex fashion such as Tor) could be used to access services that would otherwise be blocked on a local network.
+This led to the development of basic and advanced anonymity software, with proxying being a basic tool for this and Tor being the most prominent example of full fledged anonymity software.
 
@@
 People could organize quickly and effectively across larger distances and with people they had never met in the past.
-Governments took notice.
-These sites began being blocked by these sites.
-Governments and other entities also saw that users were getting around these blocks by using proxies and anonymity software - and so they gathered the IP addresses of these services and blocked them.
+Governments took notice - and censorship began.\footnote{The main justifications censors employ are maintaining law and order, preventing the spread of disinformation, preventing access to "unwholesome" content, or economic protectionism.
+[TODO: Would be cool to cite one or several instances of these justifications coming from the horses mouth]}
+
+When internet censorship arose, basic techniques were used. These include:
+\begin{itemize}
+  \item Blocking specific IPs: Traffic to or from various IP addresses could be dropped. This is simple and low cost.
+  \item Blocking DNS resolution: DNS resolution traffic for specific requests could be dropped (or replaced). This is simple and low cost. [TODO: address DNS encryption and authentication]
+  \item Legal mechanisms: If a service exists within the area an adversary controls, they could simply take down the service itself.
+Since we define the adversary to not control the whole world, we will ignore this form of censorship throughout this paper, as a restricted service could avoid this by relocating out of the sphere of influence of an adversary.
+\end{itemize}
+These techniques are sufficient to cut off access to services for users who are either unaware of a censor, unaware that circumvention is possible, users who do not care about the actions of a censor, or out of laziness.
+A user would have to actively use something that circumvents these simple blocks.
+The solution to avoid IP blocking and censoring DNS results is to proxy a users raw traffic outside of a censored area (either through a basic proxy, or something that provides other features, such as Tor).
+From the view of a censor, a user would not be accessing a restricted service, they would be accessing a proxy service.
+
+\begin{figure}
+\begin{center}
+{\includesvg{figures/networking}}
+\end{center}
+\caption{A model of networking, with our adversary performing basic censorship [TODO: Once networking diagram is finalized, show blocking]}
+\end{figure}
+
+Censorship circumvention arose as a by-product of tools made for purposes that were not focused on censorship circumvention.
+As primitive censorship began, people realized that anonymity software such as Tor or even a basic proxy could be used to access services that would otherwise be blocked.
+The entrances to these proxy services and Tor were accessed via well known IP addresses or DNS names.\footnote{The reason these were well known is that, if you want the public to access your service, they must know how to access these services, including the addresses of your service.
+These must be made public to allow people to access your service.
+A censor has access to public information.} Censors began being blocking access to these services, in additon to their original censorship targets.
+This set off a "censorship arms race."
 
@@
 This effectively led to the rise of a subdiscipline that draws heavily from networking, security, and even game theory, but also exists independently from those subdisciplines, with a variety of stakeholders including governments, NGOs, non-profits, independent programmers, academics, and others interested in developing censorship circumvention techniques.
-This also leads to a relatively unique feature of this discipline - some techniques were developped in academia, some techniques were developped in the real world, and some were developped in both, and ignoring the results from either thread of research and observation can lead to the development of limited systems.
-
-[TODO: Mention Tor PTs independently of specific methods]
+This also leads to a relatively unique feature of this discipline - some techniques were developped in academia, some techniques were developped in the real world, and some were developped in both, and ignoring the results from either thread of research and observation can lead to the development of flawed systems.
 
@@
 
-TODO
+Present censorship circumvention is currently built on two techniques: proxying traffic \emph{out} of the adversaries sphere of influence, and providing access to those proxies.
+If you can provide access to a proxy, then using existing proxying technology is trivial.
+The majority of censorship circumvention theory is focused on providing access to proxies.
+
+The bedrock of the theory underlying succesful provision of access to proxies is collateral damage.
+We begin with a basic model - an adversary will engage in the censorship of service $x$ if $b_x - c_x > 0$, where $b_x$ is the benefit of engaging in censorship of service $x$ and $c_x$ is the cost of engaging in censorship of service $x$.
+We will refine this formula by switching to a focus on censorship techniques - $(b_x1 + b_x2 + ...
++ b_xn) - c_x > 0$, where $b_xn$ is the benefit of censoring service $n$ using method $x$, and $c_x$ is the cost of engaging in censorship method $x$.
+A censor will engage in any censorhip method where the benefit reaped by censoring \emph{any} desired services using that mathod is greater than 0.
+
+We now note that each method may only stop a fraction of users accessing a service using a method - so a more realistic formulation would be $(u_x1*b_x1 + u_x1*b_x2 + ...
++ u_xn*b_xn) - c_x > 0$, where $u_xn$ is the fraction of users accessing a service are blocked from accessing service $n$ using method $x$.
+
+We will now break down cost further.
+$c_x = f_x + m_x$ - where $f_x$ is the fixed cost of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$.
+We will drop $f_x$ from further consideration - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost costs $0$ over the long run.
+We will now explore the marginal cost of $x$.
+Censorship
 
@@
 TODO
+
+[TODO: Mention Tor PTs independently of specific methods]
 

### 2023-02-02 paper.tex
Updates

@@
 The bedrock of the theory underlying succesful provision of access to proxies is collateral damage.
-We begin with a basic model - an adversary will engage in the censorship of service $x$ if $b_x - c_x > 0$, where $b_x$ is the benefit of engaging in censorship of service $x$ and $c_x$ is the cost of engaging in censorship of service $x$.
-We will refine this formula by switching to a focus on censorship techniques - $(b_x1 + b_x2 + ...
-+ b_xn) - c_x > 0$, where $b_xn$ is the benefit of censoring service $n$ using method $x$, and $c_x$ is the cost of engaging in censorship method $x$.
-A censor will engage in any censorhip method where the benefit reaped by censoring \emph{any} desired services using that mathod is greater than 0.
+We begin with a basic model - an adversary will engage in the censorship of service $x$ if $B_x - C_x > 0$, where $B_x$ is the average benefit per user of engaging in censorship of service $x$ and $C_x$ is the average cost of engaging in censorship of service $x$.
+We will refine this formula by switching to a focus on censorship techniques - $(b_{x,1} + b_{x,2} + ...
++ b_{x,n}) - C_x > 0$, where $b_{x,n}$ is the average benefit per user of censoring service $n$ using method $x$.
+A censor will engage in any censorhip method where the average benefit reaped by censoring \emph{any} desired services using that method is greater than the cost.
+Also note that these benefits and costs are based on how they are \emph{perceived} by the censor, not by an objective, bird-eye view of good vs.
+bad, and they may account for a variety of benefits/cost, including direct financial costs, but also including less tangible value such as "stability".
 
-We now note that each method may only stop a fraction of users accessing a service using a method - so a more realistic formulation would be $(u_x1*b_x1 + u_x1*b_x2 + ...
-+ u_xn*b_xn) - c_x > 0$, where $u_xn$ is the fraction of users accessing a service are blocked from accessing service $n$ using method $x$.
+We now note that each method may only stop a fraction of users accessing a service using a method - so a more realistic formulation would be $(u_{x,1}*b_{x,1} + u_{x,2}*b_{x,2} + ...
++ u_{x,n}*b_{x,n}) - C_x > 0$, where $u_{x,n}$ is the fraction of users accessing service $n$ are blocked from accessing service $n$ using method $x$.
 
 We will now break down cost further.
-$c_x = f_x + m_x$ - where $f_x$ is the fixed cost of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$.
-We will drop $f_x$ from further consideration - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost costs $0$ over the long run.
+$C_x = f_x + m_x$ - where $f_x$ is the fixed cost per user of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$ per user.
+We will drop $f_x$ from further consideration (ie, $C_x = m_x$) - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost averages to $0$ over the long run.
 We will now explore the marginal cost of $x$.
-Censorship
+Censorship tools may slow down "good" traffic, and they may erroneously block access to good services.
+Therefore, $C_x = s_x*i_x + (u_{x,1}*c_{x,1} + u_{x,2}*c_{x,2} + ...
++ u_{x,n}*c_{x,n})$, where $c_{x,n}$ is the average cost of blocking service $n$ per user, $u_{x,n}$ is the same as above, $s_x$ is the average fraction of the total value of unblocked traffic retained (due to the reduction in speed caused by enabling method $x$),\footnote{Note that an adversary may engage in multiple stages of filtering, so some subsets of unblocked traffic may experience no slowdown, while some might experience more.
+For the purposes of our analysis, we can use the average across all allowed traffic.}, and $i_x$ is the value per user of access to all unblocked sites.
+Combining the above, we see
+$(u_{x,1}*b_{x,1} + u_{x,1}*b_{x,2} + ... + u_{x,n}*b_{x,n}) - s_x*i_x + (c_{x,1} + c_{x,2} + ...  + c_{x,n}) > 0$, or, more sucintly:
+\begin{equation}
+
+\end{equation}
+
+We could conclude here if a censor engaged in censorship using
 

### 2023-02-02 paper.tex
Stashing paper

@@
 If you can provide access to a proxy, then using existing proxying technology is trivial.
-The majority of censorship circumvention theory is focused on providing access to proxies.
+The majority of censorship circumvention theory is, therefore, focused on providing access to proxies.
 
 The bedrock of the theory underlying succesful provision of access to proxies is collateral damage.
+
+[TODO: Discuss collateral damage more]
+
+\subsubsection{Modeling collateral damage}
+
 We begin with a basic model - an adversary will engage in the censorship of service $x$ if $B_x - C_x > 0$, where $B_x$ is the average benefit per user of engaging in censorship of service $x$ and $C_x$ is the average cost of engaging in censorship of service $x$.
@@
 We now note that each method may only stop a fraction of users accessing a service using a method - so a more realistic formulation would be $(u_{x,1}*b_{x,1} + u_{x,2}*b_{x,2} + ...
-+ u_{x,n}*b_{x,n}) - C_x > 0$, where $u_{x,n}$ is the fraction of users accessing service $n$ are blocked from accessing service $n$ using method $x$.
++ u_{x,n}*b_{x,n}) - C_x > 0$, where $u_{x,n}$ is the fraction of users accessing service $n$ that are blocked from accessing service $n$ using method $x$.
 
@@
 \begin{equation}
+-s_x*i_x + \sum_{s=1}^{n}u_{x,s}*v_{x,s} > 0
+\end{equation}
+where $v_{x,s} = b_{x,s} - c_{x,s}$.
 
+We could conclude here if a censor engaged in censorship solely using a singular method of censorship - however, censors engage in multiple methods of censorship, and the benefit of succesfully blocking a site is not distributed multiple times if it's blocked by multiple methods, the benefit is only achieved based on new users blocked by a method, or, in short, a singular censorship system $x$ will be implemented if:
+\begin{equation}
+-s_x*i_x + \sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} > 0
 \end{equation}
+Note that all variables are the same, except $i_x$ is now the value per user of access to all unblocked sites prior to enabling censorship system $x$ and $\Delta u_{x,s}$ is the change in the fraction of users who can access service $s$ after enabling $x$.
 
-We could conclude here if a censor engaged in censorship using
+We have now established an equation used to determine if a censor will enable an individual system, taking existing sytems (or lack thereof) as a given.
+This is not reflective of reality, where a rational censor will evaluate \emph{all} of their active and potentical circumvention systems in conjunction.
+
+The valuation of a system consisting of censorship systems $1$ through $m$ is as follows:
+\begin{equation}
+\sum_{x=1}^{m}\sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} - i_{x} * \prod_{x=1}^{m}s_x
+\end{equation}
+All variables are the same as previously, except $i_x$ is the value per user of access to all unblocked sites again, $s_x$ is the average fraction of the total value of unblocked traffic retained after enabling all systems $y$ with $0\leq y<x$, and $\Delta  u_{x,s}$ change in fraction of all users blocked using method $x$ that were not already blocked after enabling all systems $y$ with $0\leq y<x$.
+We will define $x=0$ such that this "censorship" system is the null (non-existent) censorship system, and therefore $s_0 = 1$, and $u_{0,s} = 0$.
+
+We assert that a censor is picking from a number of censorship systems that is small enough such that the censor can evaluate the above equation for every possible set of censorship systems in every permutation such that each set only has one of each censorship system in a reasonable amount of time.
+[TODO: Maybe justify a bit more?]
+
+A rational censor will enable the set of censorship systems such that the above equation is maximized given every potential set of circumvention systems.
+
+[TODO: Dig into the base rate fallacy]
+
+\section{Prior techniques}
 
 [TODO: Mention parrot is dead]
-
-\section{Prior techniques}
 
@@
 [TODO: Do mention some things like shadowsocks that are in use but are even further from academics]
+
+[TODO: Mention stego]
 

### 2023-02-03 paper.tex
Paper

@@
 
+\subsection{User model}
+
+[TODO]
+
+[TODO: We should outline that we do not assume unlimited resources for our system.
+We should outline that we expect users to run the software on a phone or basic computer, and that we expect the system to be run by volunteers (who may or may not have significant resource)]
+
+\subsection{System provider model}
+
+[TODO]
+
 \subsection{History and basics}
@@
 
-[TODO: Dig into the base rate fallacy]
+[TODO: Dig into the base rate fallacy, and expound on that with an equation based expansion that fits in the above model]
 
 \section{Prior techniques}
+
+[TODO: For each of these be sure to mention if they work IRL]
 
@@
 [TODO: Mention stego]
+
+[TODO: Discuss fingerprinting, including contemporary examples w/ snowflake]
 
@@
 
-[TODO: Iran case study]
+[TODO: Add a diagram which will be used later to start to show "modifications" from the snowflake model to get our system]
+
+[TODO: Iran case study to highlight scalability]
 
@@
 
-\subsubsection{Raven}
+\subsubsection{Email}
 
-TODO
+[TODO: Mention this w/ raven, bridgedb, etc]
 
@@
 
+\subsubsection{Tapdance}
+
+\subsection{Tunneling and realistic behavior}
+
+\subsubsection{Raven}
+
 \section{Real world observations}
 
-TODO
+[TODO - a bunch of case studies]
 
@@
 
-TODO
+[TODO - may cut this, but this will be drawing conclusions from our examples above, and comparing those adversaries to the adversary model we outlined, and will transition our discussion to OBFS/the bridge distribution problem]
+
+\subsection{The bridge distribution problem}
+
+[TODO - Salmon + that followup paper]
 
@@
 TODO
+
+[TODO: Torrents, Crypto, ???]
 
@@
 
-We saw that several circumvention systems work given the constraints they were designed for, however, these constraints are either too loose and have known real-world failures under our adversary model, the systems are too difficult to deploy, or they have hit scalability issues.
+We saw that several circumvention systems work given the constraints they were designed for, however, these constraints are either too loose and have known real-world failures under our adversary model,\footnote{The bridge distribution problem being the most notable issue for several otherwise effective systems.} the systems are difficult to deploy, or they have scalability issues.
 
-We propose a system with a clear theoretical backing and acheivable goals based on both theory and real-world observations.
+Additionally, usability is also a crucial issue [TODO: COVER THIS IN RELATED WORK], and we identify two crucial issues where at least one of these affects every previously discussed system:
+\begin{itemize}
+  \item Low bandwidth/poor performance: Users want a good experience on the web.
+Some of these methods are completely unusable for proxying the entirety of a web session.
+Additionally, many of these items are tied to usage of Tor.
+While we support usage of Tor, it slows down web browsing even without circumvention tools in use, and usage can [result in broken behavior on some websites/some sites block Tor TODO: explore and cite either in fn or related work].
+  \item Barriers to entry: Every system we've explored that are usable by a layperson require usage in conjunction with Tor - and a layperson must be aware Tor exists, not be biased against it,\footnote{Some individuals believe that Tor is only used by criminals, and while we do not believe this is true, dispelling misinformation at a large scale is a herculean task that we will assume is not accomplishable in the short and medium term [TODO: Citing this would be good]} know how to get it, and not be censored when getting it.\footnote{Acquiring Tor is frequently censored for users, which means that a user \emph{must} acquire it prior to being under a censorship regime, or must have some out of band channel for acquisition.
+[TODO: Worth citing, may be worth bumping up importance]}
+\end{itemize}
+
+Below, we propose a system with a clear theoretical backing and acheivable goals based on both theory and real-world observations. [TODO: xref] We also address these other key issues.
 
@@
 
-We aim to thwart the adversary we outline in [xref]. We will rely heavily on the concept of collateral damage. [TODO: Discuss collateral damage further]
+We aim to thwart the adversary we outline in [TODO: xref]. We will rely heavily on the concept of collateral damage. [TODO: xref]
 
-We are \emph{not} aiming to provide anonymity.\footnote{Perhaps our system could be used to access an anonymity system, but we do not want to guarentee anonymity or guarentee that the system will not leak information that may break anonymity, though we are not delibrately trying to break anonymity, we are also not evaluating our system for it at this point.} We feel the need to emphasize this, as most current systems that are functional in the real world are used as pluggable transports by Tor.\footnote{Our system could be used as a PT, as we do have a golang implementation, however, evaluating this system for usage as a PT is reserved for future work.}
+We are \emph{not} aiming to provide anonymity.\footnote{Perhaps our system could be used to access an anonymity system, but we do not want to guarentee anonymity or guarentee that the system will not leak information that may break anonymity, though we are not delibrately trying to break anonymity, we are also not evaluating our system for it at this point.} We feel the need to emphasize this, as most current systems that are functional in the real world are used purely as a PT by Tor.\footnote{Our system could be used as a PT, as we do have a golang implementation, however, evaluating this system for usage as a PT is reserved for future work.
+[TODO: XREF PTs]}
 
-\subsection{Comparing existing systems}
+We will break down our goals into two sets: accomplishing censorship circumvention, and providing a more usable system for a layperson.
+
+\subsection{Censorship circumvention}
 
 Earlier, [TODO: xref] we discussed a variety of censorship circumvention systems.
-Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to acheive and working techniques we may use.
+Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to acheive, working techniques we may use, and a theory for our systems function.
 We present a short summary of previous systems in [TODO: xref table], comparing and contrasting their succesful techniques and transports, and their individual drawbacks.
@@
 
-Another key observation is that \emph{collateral damage} is the bedrock of the theory behind a circumvention system - as such, any system must be based around maximizing this - the ideal system will make the only feasible way to shut down the system effectively shutting down a large portion of internet traffic.
+Another key observation is that \emph{collateral damage} is the bedrock of the theory behind \emph{all} circumvention systems - as such, any system must be based around maximizing this - the ideal system will make the only feasible way to shut down the system effectively shutting down a large portion of internet traffic.
 
@@
 
+We first note that systems with deployment difficulty (refraction networking) as their primary limitation rely on either a single or handful of \emph{large}, \emph{continuously cooperative} entities (all very large tech corporations).
+This makes the circumvention method brittle - ie, a change of heart of very few entities could negate the effectiveness of this method.
+We believe that not only is this a possibility, but it is a \emph{likely} possibility - we note that adversaries may be as large as a collective of nations in our model - and given the profit maximization of corporations, these entitites will want to perform business in the sphere of influence of our adversary.
+The adversary could pressure the entity to shut down the system in order to perform business within, with, and with citizens of the sphere of influence of the adversary.
+Economic theory implies that this will occur in the long run.
+[TODO: shore this up with both more clear wording and with some cites to examples] Due to this limitation we will not be building on refraction networking for our system.
+
+[TODO: We will not use systems with the bridge distribution problem as their flaw, xref salmon section]
+
+We are now effectively left with techniques with scalability and low bandwidth as our primary limitations to consider.
+Systems with low bandwidth are either directly limited through maximum channel bandwidth,\footnote{Even without system overheads - e.g.
+Raven reduces bandwidth from an already low level to an even \emph{lower} level.} or through financial cost.
+Because of our system and user model, where the system is run with potentially limited resources and users are not charged for usage, we cannot require users to pay to access the system or expect large financial expenditures from our system provider.
+This means we may not use these techniques for the majority of our systems operation (though we may use them for low-bandwidth usage, such as bootstrapping).
+
+We are left with systems whose primary limitation is scalability.
+We see that Snowflake is the only remaining existing system.
+Snowflake was developped primarily in the real world - and we know it works in the real world - but to build off of this success we want to formalize that success and that system design.
+
+We will return to our model of censorship, reprinted below [XREF]:
+\begin{equation}
+\sum_{x=1}^{m}\sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} - i_{x} * \prod_{x=1}^{m}s_x
+\end{equation}
+
+We will now refine our adversary definition further.
+We will assume our adversary has access to any censorship system proposed in the literature \emph{or} in use (either actively, historically, or proposed for use) in the real world.
+We will break down our adversaries into two classes:
+\begin{itemize}
+  \item Has a high tolerance for a low $\prod_{x=1}^{m}s_x$.
+  \item Has a low tolerance for a low $\prod_{x=1}^{m}s_x$.
+\end{itemize}
+We note that both adversaries have been observed in the real world, with [XREF Iran] slowing down \emph{all} traffic notably, and all other adversaries slowing down only limited subsets of traffic at most (e.g.
+[XREF Russia with Twitter]).
+
+We will now assume that all adversaries are rational.
+This allows us to conclude that an adversary has optimized their censorship apparatus by evaluating all possible combinations of censorship systems.
+[TODO: dive a bit more into this in the earlier section, and discuss game theory a bit more] We will let $V_existing = \sum_{x=1}^{m_existing}\sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} - i_{x} * \prod_{x=1}^{m_existing}s_x$ for the optimized set $S$ of censorship apparatuses of size $m_existing$.
+
+We propose a theoretical censorship system, $s_{new}$.
+We will consider $S \cup {s_{new}}$.
+Our censor will reevaluate the utility of their system using every permutation of this larger set.
+This means that they will evaluate adding $s_{new}$ to their system, and keeping all existing systems or removing some of them and adding this new one.
+We will let this new set be $S_{new}$.
+We have two potential cases:
+\begin{itemize}
+  \item $S_{new}$ does not include $s_{new}$ - ie, $S_{new} = S$. In this case, the censor is not engaging any new censorship sytems.
+  \item $S_{new}$ includes $s_{new}$ - ie, they engaged the new system.
+In this case we will assume that they will never disable an old system.
+[TODO: Can we prove that they will never disable an old system?] This means we can evaluate a new system using a simplified formula from earlier:
+  \begin{equation}
+-s_x*i_x + \sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} > 0
+  \end{equation}
+  [TODO: XXX: FIX S REUSE IN FORMULAS]
+\end{itemize}
+
+[TODO: APPLY THE ECONOMIC MODEL OF CENSORSHIP CIRCUMVENTION TO SNOWFLAKE]
+
+We know censors do not censor Snowflake. We can assert the
+
+[We have a value, though abstract, that we can relatively compare to - so long as adjustments to our system have a net 0 or an increase in censorship costs
+
+[TODO: MAKE AN ASSUMPTION - OUR THEORETICAL ADVERSARY CAN BE THOUGHT OF AS HAVING THE CAPABILITIES OF ALL REAL WORLD ADVERSARIES + ACADEMIC ATTACKS - BUT THEY HAVE A UTILITY MODEL BASED ON REAL WORLD COUNTRIES - EXPLORE AN ADVERSARY A LA IRAN WILLING TO SLOW DOWN GENERAL TRAFFIC AND BLOCK A LOT, AND ONE THAT IS MORE SIMILAR TO CHINA - VERY WILLING TO BLOCK, BUT NOT WILLING TO SLOW DOWN TRAFFIC - USE FALSE POSITIVE RATES OF REAL COUNTRIES TO GET A THEORETICAL ADVERSARIES FALSE POSITIVE FUNCTION - JUSTIFY WITH THE RELATIVE LACK OF INTERNET SHUTDOWNS AND UNWILLINGNESS TO USE WANG ET AL FOR OBFS OR ANYTHING WITH SNOWFLAKE]
+
+\subsection{Usability}
+
 We also note that existing systems require a user to download and use specialized software, and that systems usually require using anonymity software such as Tor to reap the benefits of censorship circuvmention.
 While anonymity is a useful [thing] to have in some circumstances on the web, getting the drawbacks of common anonymity software [TODO: outline] is not ideal.
+
+[TODO: More]
 

### 2023-02-07 paper.tex
Some ethics

@@
 We also note that existing systems require a user to download and use specialized software, and that systems usually require using anonymity software such as Tor to reap the benefits of censorship circuvmention.
-While anonymity is a useful [thing] to have in some circumstances on the web, getting the drawbacks of common anonymity software [TODO: outline] is not ideal.
+While anonymity is a useful [thing] to have in some circumstances on the web, getting the drawbacks of common anonymity software [TODO: outline] is not ideal in all use cases, particularly getting users to adopt software.
 
-[TODO: More]
+[TODO: More - draw from usability studies]
 
@@
 
-TODO
+We outlined certain goals we want to achieve based upon successes and limitations. Notably:
+\begin{itemize}
+  \item Building off of a succesful technique, increase collateral damage.
+This can be done by increasing the number of services that would be blocked should an adversary take action, or increasing the slowdown to other traffic.
+  \item Increasing usability, particularly by lowering the barrier to entry for users, enabling easier acquision of the system, and increasing bandwidth for circumvention focused usage.
+\end{itemize}
+
+As we noted above [xref], Snowflake seems to be the most promising style of circumvention system to build off of.
+This leaves us two approaches: stick with WebRTC or build a system with another available transport that models the topology of Snowflake.
+
+[TODO: Find a web study about most used protocols, spend some time discussing why there are not many viable alternatives to WebRTC]
+
+We choose to stick with WebRTC as our primary transport.
+We do this because, as we discussed previously, no adversary present in the real world has a utility function that allows them to censor Snowflake.
+[TODO: Spend some time discussing fingerprinting and why that isn't a long term issue] From this, we can see that the utility of WebRTC must outweigh the drawbacks of restricting it further.
+As such, to build on the success of Snowflake, we choose to instead change the topology
 
@@
 
+\section{Ethics}
+
+In the course of this research, we developped and tested a system performing legal activity without a real-world adversary attempting to censor our traffic, using our own resources or public resources in an acceptable fashion.
+We \emph{emulated} an adversary by taking the most logical steps to censoring our system while mitigating collateral damage.
+As such, performing this research was ethical.
+
+Further exploration of deploying a system like this would be necessary.
+We previously discussed that adversaries may be able to deploy legal apparatuses to censor services within a country, and while we do not expect an adversary to have the ability to do this against most users, we cannot exclude the possibility that an adversary may use legal tools against \emph{some} users of our system.
+
+Our system is distinct from any deployed system: users of our system are also providers of our system.
+An adversary may not distinguish between users and providers of a system, but it is possible that they might, and if they did, they would likely punish "providers" more harshly than simple users.
+
+We see two potential paths towards potentially resolving this issue that would need to be considered before deployment to users in a censored area:
+\begin{itemize}
+  \item Plausibly deniability: If the system performs these actions without a users input, without informing a user, this provides them with plausible deniability.
+This would allow users to plead ignorance should an adversary attempt to punish them.
+Additionally, having a "killer app" that is useful to users \emph{regardless} of the ability to use circumvention would further enhance this path: if users use this system for reasons besides censorship circumvention, then users would be able to say they didn't know or care that the system provided censorship circumvention - they thought they were just using another app, not a circumvention system.
+  \item Clear disclosure to users: Clearly disclosing to users how the system works means that users, who know their circumstances better than we could, could make the ideal decision for themselves to use the system.
+This may turn some users off of using the system, but it pushes the full decision to use the system onto users themselves, and would eliminate any uncertainty for users about what they were doing, and that they may be at risk doing it.
+The downside, of course, is that an adversary who catches a user using the system could take action against a user and the user would be unable to argue that they \emph{accidentally} were providing a circumvention service.
+\end{itemize}
+
+Beyond these two paths, we could also provide users with the ability to disable provision of services to other users.
+While this path could be explored further, the notable benefits (both scalability and increased collateral damage) provided by this system over Snowflake dissapear if users in a censored region opt out of being providers.
+
 \section{Future work}
 
-TODO
+[Evaluation of the average "value" of a user in the network, and ideal node balances, etc]
+
+[Plausable deniability]
+
+[Analyze what is lost when doing circumvention without anonymity]
+
+[Roll items into IPFS]
+
+[IPFS improvements: Authenticated pubsub]
+
+[Add support for PTs]
+
+[Add support for usage as a PT]
+
+[Add a Tor download]
+
+[Privacy enhancements]
 

### 2023-02-07 paper.tex
More stuff

@@
 \newtheorem{theorem}{Theorem}[section]
+\newtheorem*{adversary}{Adversary}
 \newenvironment{proof}[0]{\textit{Proof.}}{}
@@
 
-TODO
+Having built our system, we will perform an evaluation of our system.
+Demonstrating that the system as designed is viable [shows that a system that improves on Snowflake is not just theoretical, but also practicle].
+
+[More]
 
@@
 
-TODO
+Demonstrating performance is a key measure to show our system works and that it is possible to bootstrap with limited resources.
+
+We first show that our system \emph{under no censorship} functions [TODO: good description of the final results]
+
+[TODO: Describe how the benchmarking app works]
+
+[TODO: a table, likely a full page sideways, will exist here outlining the results of our benchmarking app]
+
+[TODO: Walk through results]
+
+\section{Performance under censorship}
+
+Having demonstrated basic functionality, we will show that our system not only works, but works [TODO: well (verify)] under some of the more extreme censorship that could occur.
+To do this, we take steps a censor would likely take to attack this system.
+
+\subsection{Blocking bootstrapping nodes}
+
+The easiest vector of attack a censor could take to attempt to block our system is to block the IPs and DNS records of the bootstrapping nodes used for the system.
+We discuss this method of attack in the real world more in [TODO: xref bootstrapping availability AND system design AND related work], as well as our mitigations for the attack.
+
+We perform the same benchmarking test without using any default bootstrapping nodes.
+We do this by using a stand-in for a high value channel, which connects to the system and performs bootstrapping \emph{without} using the default nodes.
+[POTENTIAL EXPANSION: Don't just do a stand-in, actually do it using raven] [POTENTIAL EXPANSION: FIREWALL THE NODES as extra proof] We perform the same tests as above.
+
+[TODO: a table, likely a full page sideways, will exist here outlining the results of our benchmarking app]
+
+[TODO: Walk through results]
+
+\subsection{Blocking \emph{all} transports except WebRTC and a high value channel}
+
+Instead of iterating through all potential censorship apparatuses that are more powerful than simply blocking the bootstrapping nodes, we outline a \emph{very} strong adversary willing to engage in massive censorship and show that our system still survives.
+\begin{adversary}
+An adversary is dealing with serious turmoil within their borders.
+They decide that all non-essential web traffic is to be shutdown.
+They designate email and video chats as essential for their own communication, and as such allow access to email and WebRTC.
+They block all other traffic, excluding some auxilary traffic that are used related to those (e.g.
+DNS, STUN, TURN).
+\end{adversary}
+Note that this means that our adversary is blocking bootstrapping nodes as well.
+
+We perform the same benchmarking test as before, without using any default bootstrapping nodes \emph{and} without using any transport besides our stand-in for a high value channel and WebRTC.
+[POTENTIAL EXPANSION: Don't just do a stand-in, actually do it using raven] [POTENTIAL EXPANSION: FIREWALL THIS - will be harder than before since will need to whitelist DNS/STUN/TURN/ETC]
+
+[TODO: a table, likely a full page sideways, will exist here outlining the results of our benchmarking app]
+
+[TODO: Walk through results]
+
+\subsection{A more advanced adversary?}
+
+We see that no real-world adversary has a utility function which allows them to block Snowflake.
+This does not mean that an adversary may not be able to build a more advanced censorship system.
+We believe that the changes that we have made to the model setup in Snowflake drastically increases the costs [TODO: Either outline or xref] to censor our system over Snowflake, and as such an adversary would not just have to build a system that could censor Snowflake with acceptable collateral damage, but they would also have to build one \emph{significantly better} [TODO: Describe more precisely] than that to stop our system.
+That may happen in the future, but [discuss current literature on traffic analysis + false positives rate or xref those].
 
@@
 
-TODO
+[TODO: Section using RIPE probes]
+
+[TODO: Tie into getting the network bootstrapped/security through obscurity]
 
@@
 This may turn some users off of using the system, but it pushes the full decision to use the system onto users themselves, and would eliminate any uncertainty for users about what they were doing, and that they may be at risk doing it.
-The downside, of course, is that an adversary who catches a user using the system could take action against a user and the user would be unable to argue that they \emph{accidentally} were providing a circumvention service.
+The downside, of course, is that an adversary who catches a user using the system could take action against a user and the user would be unable to argue that they \emph{unintentionally} were providing a circumvention service.
 \end{itemize}
@@
 Beyond these two paths, we could also provide users with the ability to disable provision of services to other users.
-While this path could be explored further, the notable benefits (both scalability and increased collateral damage) provided by this system over Snowflake dissapear if users in a censored region opt out of being providers.
+While this path could be explored further, the notable benefits (both scalability and increased collateral damage) provided by this system over Snowflake partially or fully dissapear if users in a censored region opt out of being providers.
+
+While we believe that one of these paths (clear disclosure) would allow for an ethical deployment of our system, a deeper exploration of the alternative would be worthwhile to evaluate.
 

### 2023-02-07 paper.tex
Spelling

@@
-% File 'gusample.tex' -- Mark Maloof, Michael A. Covington, Isidor Ruderfer
-% (Revised 15 December 2010)
-% This is an example of how to format a thesis or dissertation using LaTeX 2e
-% with 'guthesis.sty' VERSION 3.4 OR LATER.
-
 \documentclass[12pt]{report}
@@
 % If there are any other \usepackage commands, put them here.
+\usepackage{amsthm}
 
@@
 \newtheorem{theorem}{Theorem}[section]
-\newtheorem*{adversary}{Adversary}
-\newenvironment{proof}[0]{\textit{Proof.}}{}
-\newcommand{\qed}{\hfill $\Box$}
+\newtheorem{adversary}{Adversary Model}
 
@@
 \professor{Micah Sherr}
-%\secondprofessor{Alonzo Church}   % Only if you have 2 major professors!
 
@@
 \memberii{Benjamin Ujcich}
-% Use \memberiii, \memberiv, \memberv for up to 3 more members if needed.
 
@@
 These entities may range from individual network administrators to a full nation-state.
-In this paper, we explore the state of censorship, existing circumvention sytems, and we design and build a system which tackles several of the limitations present in state of the art systems.
+In this paper, we explore the state of censorship, existing circumvention systems, and we design and build a system which tackles several of the limitations present in state of the art systems.
 [LATER: Add xrefs to sections]
@@
 
-We also provide an overview of the state of peer to peer (P2P) networking, focusing on succesful project operating in the real world.
+We also provide an overview of the state of peer to peer (P2P) networking, focusing on successful project operating in the real world.
 We provide a deeper dive into the Interplanetary File System (IPFS) and the underlying networking library, LibP2P.
@@
 The term censorship has taken on a life of it's own in the modern social and political context.
-We are \emph{not} exploring the general connotation of censorship, rather, we are exploring a specific type of censorship that existing in a networking (particularly internetworking) context.
+We are \emph{not} exploring the general connotation of censorship, rather, we are exploring a specific type of censorship that existing in a networking (particularly inter-networking) context.
 We will explore some key concepts and present a short model of networking.
@@
 We will use IPv4 addresses throughout as sample addresses, though conceptually IPv6 addresses function similarly for the focuses of this paper.
-  \item Domain Name System (DNS): DNS resolution is used to map from human-readable and memorizable addresses that map to IP addresses (e.g.
+  \item Domain Name System (DNS): DNS resolution is used to map from human-readable and memorable addresses that map to IP addresses (e.g.
 georgetown.edu resolved to 23.185.0.2 at the time of writing).
@@
 We recognize that some users run heinous services on the web - most of which are illegal in any existing jurisdiction.
-We believe that the best approach for ceasing access to these heinous services is best done through a legal system - ie, investigating and identifying the perpetrator(s), turning off the service directly, and prosecuting any perpetrator(s) of said acts.
+We believe that the best approach for ceasing access to these heinous services is best done through a legal system - IE, investigating and identifying the perpetrator(s), turning off the service directly, and prosecuting any perpetrator(s) of said acts.
 We note that most morally reprehensible acts that are frequently associated with anonymity and censorship circumvention systems involve actions that occur in the real world (e.g.
@@
 The only notable class of crime which can occur without physical, real-world actions is piracy/IP violations.
-We believe that targetted legal actions (e.g.
-DMCA takedowns) can mitigate the issue, and that the cost of further mitigation through censorship would lead to large collateral damage of legal content and a chilling effect of legal speech and usage of the web, and as such the possibility of a circumvention system being used for piracy/IP violations is an acceptable risk given the ability to mitigate damage through the legal system.
+We believe that targeted legal actions (e.g.
+DMCA take-downs) can mitigate the issue, and that the cost of further mitigation through censorship would lead to large collateral damage of legal content and a chilling effect of legal speech and usage of the web, and as such the possibility of a circumvention system being used for piracy/IP violations is an acceptable risk given the ability to mitigate damage through the legal system.
 
@@
 This is an area an adversary controls the network of, and can control (either directly or through compulsion) any service providers within.
-We assume an adversary may have an area of influcence consisting of several nations, with at least one nation outside of the area of influence of \emph{any} censor.\footnote{This does not mean that this nation does not have the technical capability to censor, but rather does not perform any censorship either directly or via threatening a start of censorship.}
+We assume an adversary may have an area of influence consisting of several nations, with at least one nation outside of the area of influence of \emph{any} censor.\footnote{This does not mean that this nation does not have the technical capability to censor, but rather does not perform any censorship either directly or via threatening a start of censorship.}
 
@@
 
-We also assume that our adversary only takes actions \textbf{on-the-wire} and at \textbf{service providers} within their area of influence - effectively, the adversary isn't interested in any individual in particular and is performing a dragnet operation, rather than an operation targetting a specific entity.
+We also assume that our adversary only takes actions \textbf{on-the-wire} and at \textbf{service providers} within their area of influence - effectively, the adversary isn't interested in any individual in particular and is performing a dragnet operation, rather than an operation targeting a specific entity.
 We can use a thought experiment to justify this: if an adversary had a person looking over your shoulder or using video surveillance, they could simply look at what you are doing and punish you directly, no need to expend the resources needed to censor the web.
@@
 [TODO: Discuss prior shut downs in another section and xref]} and an adversary has some threshold of unacceptable collateral damage caused by potential censorship techniques.\footnote{Similar to a full internet shutdown, if an adversary wanted to block all access to a specific HTTP site, they could block \emph{all} HTTP traffic, at the expense of blocking every HTTP site.
-This piecemeal web censorship could even be thwarted with a circumvention system that simply proxies HTTP traffic outside of the area of influence within an unblocked protocol and connects to HTTP sites from outside the area of influcence.
+This piecemeal web censorship could even be thwarted with a circumvention system that simply proxies HTTP traffic outside of the area of influence within an unblocked protocol and connects to HTTP sites from outside the area of influence.
 This starts to show that any non-complete shutdown of internet traffic may have gaps for circumvention techniques.
@@
 These must be made public to allow people to access your service.
-A censor has access to public information.} Censors began being blocking access to these services, in additon to their original censorship targets.
+A censor has access to public information.} Censors began being blocking access to these services, in addition to their original censorship targets.
 This set off a "censorship arms race."
@@
 This effectively led to the rise of a subdiscipline that draws heavily from networking, security, and even game theory, but also exists independently from those subdisciplines, with a variety of stakeholders including governments, NGOs, non-profits, independent programmers, academics, and others interested in developing censorship circumvention techniques.
-This also leads to a relatively unique feature of this discipline - some techniques were developped in academia, some techniques were developped in the real world, and some were developped in both, and ignoring the results from either thread of research and observation can lead to the development of flawed systems.
+This also leads to a relatively unique feature of this discipline - some techniques were developed in academia, some techniques were developed in the real world, and some were developed in both, and ignoring the results from either thread of research and observation can lead to the development of flawed systems.
 
@@
 
-The bedrock of the theory underlying succesful provision of access to proxies is collateral damage.
+The bedrock of the theory underlying successful provision of access to proxies is collateral damage.
 
@@
 + b_{x,n}) - C_x > 0$, where $b_{x,n}$ is the average benefit per user of censoring service $n$ using method $x$.
-A censor will engage in any censorhip method where the average benefit reaped by censoring \emph{any} desired services using that method is greater than the cost.
-Also note that these benefits and costs are based on how they are \emph{perceived} by the censor, not by an objective, bird-eye view of good vs.
-bad, and they may account for a variety of benefits/cost, including direct financial costs, but also including less tangible value such as "stability".
+A censor will engage in any censorship method where the average benefit reaped by censoring \emph{any} desired services using that method is greater than the cost.
+Also note that these benefits and costs are based on how they are \emph{perceived} by the censor, not by an objective, bird-eye view of good and bad, and they may account for a variety of benefits/cost, including direct financial costs, but also including less tangible value such as "stability".
 
@@
 $C_x = f_x + m_x$ - where $f_x$ is the fixed cost per user of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$ per user.
-We will drop $f_x$ from further consideration (ie, $C_x = m_x$) - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost averages to $0$ over the long run.
+We will drop $f_x$ from further consideration (IE, $C_x = m_x$) - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost averages to $0$ over the long run.
 We will now explore the marginal cost of $x$.
@@
 Combining the above, we see
-$(u_{x,1}*b_{x,1} + u_{x,1}*b_{x,2} + ... + u_{x,n}*b_{x,n}) - s_x*i_x + (c_{x,1} + c_{x,2} + ...  + c_{x,n}) > 0$, or, more sucintly:
+$(u_{x,1}*b_{x,1} + u_{x,1}*b_{x,2} + ... + u_{x,n}*b_{x,n}) - s_x*i_x + (c_{x,1} + c_{x,2} + ...  + c_{x,n}) > 0$, or, more succinctly:
 \begin{equation}
@@
 
-We could conclude here if a censor engaged in censorship solely using a singular method of censorship - however, censors engage in multiple methods of censorship, and the benefit of succesfully blocking a site is not distributed multiple times if it's blocked by multiple methods, the benefit is only achieved based on new users blocked by a method, or, in short, a singular censorship system $x$ will be implemented if:
+We could conclude here if a censor engaged in censorship solely using a singular method of censorship - however, censors engage in multiple methods of censorship, and the benefit of successfully blocking a site is not distributed multiple times if it's blocked by multiple methods, the benefit is only achieved based on new users blocked by a method, or, in short, a singular censorship system $x$ will be implemented if:
 \begin{equation}
@@
 
-We have now established an equation used to determine if a censor will enable an individual system, taking existing sytems (or lack thereof) as a given.
-This is not reflective of reality, where a rational censor will evaluate \emph{all} of their active and potentical circumvention systems in conjunction.
+We have now established an equation used to determine if a censor will enable an individual system, taking existing systems (or lack thereof) as a given.
+This is not reflective of reality, where a rational censor will evaluate \emph{all} of their active and potential circumvention systems in conjunction.
 
@@
 
-\subsection{Real world vs. academic theory}
+\subsection{Real world and academic theory}
 
@@
 While we support usage of Tor, it slows down web browsing even without circumvention tools in use, and usage can [result in broken behavior on some websites/some sites block Tor TODO: explore and cite either in fn or related work].
-  \item Barriers to entry: Every system we've explored that are usable by a layperson require usage in conjunction with Tor - and a layperson must be aware Tor exists, not be biased against it,\footnote{Some individuals believe that Tor is only used by criminals, and while we do not believe this is true, dispelling misinformation at a large scale is a herculean task that we will assume is not accomplishable in the short and medium term [TODO: Citing this would be good]} know how to get it, and not be censored when getting it.\footnote{Acquiring Tor is frequently censored for users, which means that a user \emph{must} acquire it prior to being under a censorship regime, or must have some out of band channel for acquisition.
+  \item Barriers to entry: Every system we've explored that are usable by a layperson require usage in conjunction with Tor - and a layperson must be aware Tor exists, not be biased against it,\footnote{Some individuals believe that Tor is only used by criminals, and while we do not believe this is true, dispelling misinformation at a large scale is a herculean task that we will assume is not possible in the short and medium term [TODO: Citing this would be good]} know how to get it, and not be censored when getting it.\footnote{Acquiring Tor is frequently censored for users, which means that a user \emph{must} acquire it prior to being under a censorship regime, or must have some out of band channel for acquisition.
 [TODO: Worth citing, may be worth bumping up importance]}
@@
 
-Below, we propose a system with a clear theoretical backing and acheivable goals based on both theory and real-world observations. [TODO: xref] We also address these other key issues.
+Below, we propose a system with a clear theoretical backing and achievable goals based on both theory and real-world observations. [TODO: xref] We also address these other key issues.
 
@@
 
-We are \emph{not} aiming to provide anonymity.\footnote{Perhaps our system could be used to access an anonymity system, but we do not want to guarentee anonymity or guarentee that the system will not leak information that may break anonymity, though we are not delibrately trying to break anonymity, we are also not evaluating our system for it at this point.} We feel the need to emphasize this, as most current systems that are functional in the real world are used purely as a PT by Tor.\footnote{Our system could be used as a PT, as we do have a golang implementation, however, evaluating this system for usage as a PT is reserved for future work.
+We are \emph{not} aiming to provide anonymity.\footnote{Perhaps our system could be used to access an anonymity system, but we do not want to guarantee anonymity or guarantee that the system will not leak information that may break anonymity, though we are not deliberately trying to break anonymity, we are also not evaluating our system for it at this point.} We feel the need to emphasize this, as most current systems that are functional in the real world are used purely as a PT by Tor.\footnote{Our system could be used as a PT, as we do have a Golang implementation, however, evaluating this system for usage as a PT is reserved for future work.
 [TODO: XREF PTs]}
@@
 Earlier, [TODO: xref] we discussed a variety of censorship circumvention systems.
-Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to acheive, working techniques we may use, and a theory for our systems function.
-We present a short summary of previous systems in [TODO: xref table], comparing and contrasting their succesful techniques and transports, and their individual drawbacks.
+Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to achieve, working techniques we may use, and a theory for our systems function.
+We present a short summary of previous systems in [TODO: xref table], comparing and contrasting their successful techniques and transports, and their individual drawbacks.
 
@@
 We first note that systems with deployment difficulty (refraction networking) as their primary limitation rely on either a single or handful of \emph{large}, \emph{continuously cooperative} entities (all very large tech corporations).
-This makes the circumvention method brittle - ie, a change of heart of very few entities could negate the effectiveness of this method.
-We believe that not only is this a possibility, but it is a \emph{likely} possibility - we note that adversaries may be as large as a collective of nations in our model - and given the profit maximization of corporations, these entitites will want to perform business in the sphere of influence of our adversary.
+This makes the circumvention method brittle - IE, a change of heart of very few entities could negate the effectiveness of this method.
+We believe that not only is this a possibility, but it is a \emph{likely} possibility - we note that adversaries may be as large as a collective of nations in our model - and given the profit maximization of corporations, these entities will want to perform business in the sphere of influence of our adversary.
 The adversary could pressure the entity to shut down the system in order to perform business within, with, and with citizens of the sphere of influence of the adversary.
@@
 We see that Snowflake is the only remaining existing system.
-Snowflake was developped primarily in the real world - and we know it works in the real world - but to build off of this success we want to formalize that success and that system design.
+Snowflake was developed primarily in the real world - and we know it works in the real world - but to build off of this success we want to formalize that success and that system design.
 
@@
 \begin{itemize}
-  \item $S_{new}$ does not include $s_{new}$ - ie, $S_{new} = S$. In this case, the censor is not engaging any new censorship sytems.
-  \item $S_{new}$ includes $s_{new}$ - ie, they engaged the new system.
+  \item $S_{new}$ does not include $s_{new}$ - IE, $S_{new} = S$. In this case, the censor is not engaging any new censorship systems.
+  \item $S_{new}$ includes $s_{new}$ - IE, they engaged the new system.
 In this case we will assume that they will never disable an old system.
@@
 
+[TODO: Cite raven email study]
+
 \chapter{Conclusion}

### 2023-02-27 paper.tex
Some more notes
Intro work

@@
 \usepackage{lib/style/guthesis} % Must be the last package
+\usepackage{hyperref}
+\hypersetup{
+  colorlinks   = true, %Colours links instead of ugly boxes
+  urlcolor     = blue, %Colour for external hyperlinks
+  linkcolor    = black, %Colour of internal links
+  citecolor   = black %Colour of citations
+}
 
 \newtheorem{theorem}{Theorem}[section]
+\newtheorem{question}{Research Question}
+\newtheorem*{keyq}{Key Research Question}
 \newtheorem{adversary}{Adversary Model}
@@
 
-People us the internet to communicate and share a variety of content.
-Some entities choose to censor internet connections.
-These entities may range from individual network administrators to a full nation-state.
-In this paper, we explore the state of censorship, existing circumvention systems, and we design and build a system which tackles several of the limitations present in state of the art systems.
-[LATER: Add xrefs to sections]
+The internet has become a staple of the modern world, used by nearly every person on Earth.[CITE] The internet is a collection of independently managed networks which can route arbitrary traffic between said networks.
+It is built upon numerous \emph{protocols} which have been designed and iterated upon both academically and through practical usage over decades.
+Traffic on the internet travels from the edge of one network into another.\footnote{\emph{See} \ref{networking} for more on networking and key networking concepts.} This high level view loses some key context: networks are run by entities who have their own desires and are free to operate their network as they see fit.
+In an ideal world, all of these entities would run the same algorithms and would move traffic in a content-agnostic fashion, but we do not live in an ideal world.
+A variety of confounding factors result in a web that looks very different in practice from idealized theory: malicous entities use the web to perform attacks, bugs cause unforseen issues to arise, entities want to tightly control traffic and content in their network, among other complicating factors.
 
-We begin by exploring what we mean by censorship circumvention and establishing baseline terminology for this discipline.
-We then explore the present theory behind approaches to censorship circumvention.
-We address the ethics of censorship circumvention as a field, and how the field originated and how that affects the current state of the field.
+The more complicated web that actually exists leads to a variety of issues that don't arise in pure networking theory, one of which is \emph{censorship circumvention}.\footnote{\emph{See} \ref{circumvention} for our full definition and further discussion.} Censorship circumvention arises because some network-controlling entities choose to engage in censorhip.
+Censorship has become a loaded term in the current political context, and we do \emph{not} mean the coloquial usage of censorship.
+Censorship, as we discuss it, refers to entities censoring web traffic (either through complete blocking or other manipulation) at nodes (frequently routers) in the network(s) that they control.
+Censorship may be done for a variety of reasons - most censors will claim they are solely removing malicious traffic, however, an entity may operate their own definition of malicious which would differ from coloquial usage of the term.
+We see some entities that choose to block social media sites, news sources, or any site that they deem as block-worthy.
+Censors have a variety of justifications for their actions: economic protectionism, removing unsavory content, blocking dangerous content, maintaining law and order, and others.
+We see this and ask our key reasearch question:
+\begin{keyq}
+Can we circumvent censorship?
+\end{keyq}
+This is a very broad question - to be able to address it in a scientific manner we must refine it and break out some more specific and actionable research questions.
+To circumvent censorship, we must address what it is:
 
-We then propose several ways to classify existing systems to allow for some comparison between them, and we then explore existing and past systems to understand where the field stands, and where limitations occur.
-We emphasize systems that are either cutting edge or in active use in the real world.
+\begin{question}
+What do existing censorship systems look like?
+\end{question}
+
+We explore previous work to answer this question.[XREF] [TODO: Add more] This allows us to refine our key question:
+
+\begin{keyq}
+Can we circumvent existing censorship systems? If so, how?
+\end{keyq}
+
+As we discussed above, we note that some entity is performing censorship - censorship is not occuring spontaneously.
+Systems are not deployed magically, and do not arise without a concerted action undertaken by an entity.
+This leads us to our next research question:
+
+\begin{question}
+Can we define an adversary and model their censorship systems?
+\end{question}
+
+Previous work has spent significant time defining adversaries in order to posit new methods of circumvention, and we define our adversary in a similar fashion.
+Our adversary has unlimited resources, constrained only by physics and algorithmic limitations.\footnote{\emph{See} \ref{adversary} for our full definition and further discussion.} In our model, we also assume there is at least 1 location \emph{not} under the control of any censoring adversary.
+Our theoretical adversary is informed by both real world observations and theories developped in prior work.
+In the real world, we frequently see adversaries perform basic censorship actions, such as blocking IPs and DNS resolutions.
+We also see adversaries taking more extreme actions, such as performing fingerprinting attacks or other techniques involving deep packet inspection (DPI).\footnote{\emph{See} \ref{real} for our exploration of real-world adversaries.} In theory, we see formulations that involved the adversary either attacking specific protocols [TODO e.g.
+xref Wang discussion] or employing a specific method of attack.
+[TODO: xref Salmon discussion] In prior work, most adversarial actions are discussed in a vacuum - rather than looking at how an adversary may choose the full setup of a censorship suite, adversary modelling focuses on an adversary trying to tackle just one method of circumvention, and the broader picture is ignored.
+We formulate a model for evaluating an adversaries actions that looks at the \emph{whole} of their censorship apparatus:\footnote{\emph{See} \ref{theory} for more details and the derivation.}
+
+\begin{equation}
+[TODO: insert the final equation after cleaning notation]
+\end{equation}
+
+This model of an adversary is a novel contribution and allows for rooting research in the field to both existing theory and the real world.
+With an adversary and adequate model defined, we can further refine the key research question tackled in this paper:
+
+\begin{keyq}
+Can we circumvent our adversaries censorship systems?
+\end{keyq}
+
+We cannot immeadiately answer this question - as we see in our model, an adversary has some utility function.
+Using both observations and a hypothetical, consider a utility function where an adversary does not care about blocking access to sites they deem legitimate (i.e., blocking an allowed site has a utility to the adversary of $0$), but they strongly do not want anyone to access a non-legitimate site (i.e.
+a user accessing a non-legitimate site has a utility of $-\infty$).
+This adversary would simply disable the internet.
+This would provide them with $0$ utility, which is their maximal utility.
+In fact, in some instances censors have had real-world utility functions that result in actions like this, though those instances have been short lived.[CITE] However, in practice, we see that no censor has continually provided 0 internet access - indicating that real world adversaries place a non-zero value on allowing access to legitimate sites, but they might place a very negative value on some non-legitimate sites.
+The key point is that, while we can come up with infinite theoretical utility functions, we should focus on real and realistically possible utility functions, leading us to one research question:
+
+\begin{question}
+What does a realistic utility function look like for a censor?
+\end{question}
+
+We rely on looking at previous work focusing on real world adversaries to tackle this question, as well as novel contemporary observations.
+We find that most censors, in most circumstances, wish to censor users while providing access to acceptable sites.
+We also see that censors frequently fail to block some traffic that they could block using some known methods.
+This brings us to the key concept of \emph{collateral damage}.
+A censor can employ censorship techniques to stop some traffic that they wish to stop, but many methods of censorship would result in shutting down access to some allowed traffic as a result of using those methods.
+We see several real world adversaries who employ some similar and some differing techniques, with varying defgrees of collateral damage.
+As such, we refine our key research question:
+
+\begin{keyq}
+Can we circumvent our adversaries censorship system, given a realistic adversarial utility function?
+\end{keyq}
+
+First, if we \emph{only} look at \emph{current} censorship apparatuses and real-world adversarial utility functions, we could conclude and say yes - based entirely on previous work.
+In practice, we see that the circumvention system Snowflake is currently working under all adversaries.
+However, while, for analysis sake, we fix a utility function at a given point in time, adversaries \emph{do} change their utility functions, and new censorship systems arise.
+Adversaries are frequently trying to develop new systems, and so we cannot assume a system will last indefinitely.\footnote{We note that a circumvention system which is provably able to survive could arise, however \emph{all} existing tools either do not have a strong scientific proof (e.g.
+Snowflake) or proofs are frequently constrained beyond a reasonable point (e.g.
+Obfs).} We choose to look ahead to an adversary either adopting a different, more constraining utility function or the development of a new censorship system that is more optimal than currently deployed systems.
+This leads us to our next research question:
+
+\begin{question}
+What might censorship look like in the near future?
+\end{question}
+
+We note that stronger censorship in the near future may emerge due to either a utility function less sensitive to collateral damage, or using a more advanced censorship system.
+We review related work and synthesize some possibilities for actions an adversary may take in the future.
+We focus on currently succesful circumvention techniques, and provide some methods of censorship an adversary may engage in to further restrict these systems using existing techniques that might increase collateral damage.
+We also explore censorship techniques, and we observe that deep packet inspection and bridge enumeration are the two broad techniques an adversary may use in a more advanced censorship system.
+We discuss some directions that these techniques may proceed in.
+[TODO: More] We use this to refine our overarching research question into an approachable question:
+
+\begin{question}
+Can we circumvent our adversaries existing or potential censorship systems, given a realistic adversarial utility function?
+\end{question}
+
+We address this question head on. We design and build a system to do this.
+
+[TODO: Remove old intro]
 
@@
 \section{Networking concepts}
+\label{networking}
 
@@
 \end{center}
-\caption{A model of networking, sufficient for exploring censorship circumvention [TODO: Add final arrows, some sample traffic]}
+\caption[Basic networking]{A model of networking, sufficient for exploring censorship circumvention [TODO: Add final arrows, some sample traffic]}
 \end{figure}
@@
 \section{What is censorship circumvention?}
+\label{circumvention}
 
@@
 \subsection{Threat model and adversary}
+\label{adversary}
 
@@
 \end{center}
-\caption{A model of networking, with our adversary model overlaid [TODO: Once networking diagram is finalized, add an adversary]}
+\caption[Basic networking, with an adversary]{A model of networking, with our adversary model overlaid [TODO: Once networking diagram is finalized, add an adversary]}
 \end{figure}
@@
 \end{center}
-\caption{A model of networking, with our adversary performing basic censorship [TODO: Once networking diagram is finalized, show blocking]}
+\caption[Basic networking, with an adversary performing censorship]{A model of networking, with our adversary performing basic censorship [TODO: Once networking diagram is finalized, show blocking]}
 \end{figure}
@@
 
+[TODO: Rework]
+
 Present censorship circumvention is currently built on two techniques: proxying traffic \emph{out} of the adversaries sphere of influence, and providing access to those proxies.
@@
 [TODO: Discuss collateral damage more]
-
-\subsubsection{Modeling collateral damage}
-
-We begin with a basic model - an adversary will engage in the censorship of service $x$ if $B_x - C_x > 0$, where $B_x$ is the average benefit per user of engaging in censorship of service $x$ and $C_x$ is the average cost of engaging in censorship of service $x$.
-We will refine this formula by switching to a focus on censorship techniques - $(b_{x,1} + b_{x,2} + ...
-+ b_{x,n}) - C_x > 0$, where $b_{x,n}$ is the average benefit per user of censoring service $n$ using method $x$.
-A censor will engage in any censorship method where the average benefit reaped by censoring \emph{any} desired services using that method is greater than the cost.
-Also note that these benefits and costs are based on how they are \emph{perceived} by the censor, not by an objective, bird-eye view of good and bad, and they may account for a variety of benefits/cost, including direct financial costs, but also including less tangible value such as "stability".
-
-We now note that each method may only stop a fraction of users accessing a service using a method - so a more realistic formulation would be $(u_{x,1}*b_{x,1} + u_{x,2}*b_{x,2} + ...
-+ u_{x,n}*b_{x,n}) - C_x > 0$, where $u_{x,n}$ is the fraction of users accessing service $n$ that are blocked from accessing service $n$ using method $x$.
-
-We will now break down cost further.
-$C_x = f_x + m_x$ - where $f_x$ is the fixed cost per user of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$ per user.
-We will drop $f_x$ from further consideration (IE, $C_x = m_x$) - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost averages to $0$ over the long run.
-We will now explore the marginal cost of $x$.
-Censorship tools may slow down "good" traffic, and they may erroneously block access to good services.
-Therefore, $C_x = s_x*i_x + (u_{x,1}*c_{x,1} + u_{x,2}*c_{x,2} + ...
-+ u_{x,n}*c_{x,n})$, where $c_{x,n}$ is the average cost of blocking service $n$ per user, $u_{x,n}$ is the same as above, $s_x$ is the average fraction of the total value of unblocked traffic retained (due to the reduction in speed caused by enabling method $x$),\footnote{Note that an adversary may engage in multiple stages of filtering, so some subsets of unblocked traffic may experience no slowdown, while some might experience more.
-For the purposes of our analysis, we can use the average across all allowed traffic.}, and $i_x$ is the value per user of access to all unblocked sites.
-Combining the above, we see
-$(u_{x,1}*b_{x,1} + u_{x,1}*b_{x,2} + ... + u_{x,n}*b_{x,n}) - s_x*i_x + (c_{x,1} + c_{x,2} + ...  + c_{x,n}) > 0$, or, more succinctly:
-\begin{equation}
--s_x*i_x + \sum_{s=1}^{n}u_{x,s}*v_{x,s} > 0
-\end{equation}
-where $v_{x,s} = b_{x,s} - c_{x,s}$.
-
-We could conclude here if a censor engaged in censorship solely using a singular method of censorship - however, censors engage in multiple methods of censorship, and the benefit of successfully blocking a site is not distributed multiple times if it's blocked by multiple methods, the benefit is only achieved based on new users blocked by a method, or, in short, a singular censorship system $x$ will be implemented if:
-\begin{equation}
--s_x*i_x + \sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} > 0
-\end{equation}
-Note that all variables are the same, except $i_x$ is now the value per user of access to all unblocked sites prior to enabling censorship system $x$ and $\Delta u_{x,s}$ is the change in the fraction of users who can access service $s$ after enabling $x$.
-
-We have now established an equation used to determine if a censor will enable an individual system, taking existing systems (or lack thereof) as a given.
-This is not reflective of reality, where a rational censor will evaluate \emph{all} of their active and potential circumvention systems in conjunction.
-
-The valuation of a system consisting of censorship systems $1$ through $m$ is as follows:
-\begin{equation}
-\sum_{x=1}^{m}\sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} - i_{x} * \prod_{x=1}^{m}s_x
-\end{equation}
-All variables are the same as previously, except $i_x$ is the value per user of access to all unblocked sites again, $s_x$ is the average fraction of the total value of unblocked traffic retained after enabling all systems $y$ with $0\leq y<x$, and $\Delta  u_{x,s}$ change in fraction of all users blocked using method $x$ that were not already blocked after enabling all systems $y$ with $0\leq y<x$.
-We will define $x=0$ such that this "censorship" system is the null (non-existent) censorship system, and therefore $s_0 = 1$, and $u_{0,s} = 0$.
-
-We assert that a censor is picking from a number of censorship systems that is small enough such that the censor can evaluate the above equation for every possible set of censorship systems in every permutation such that each set only has one of each censorship system in a reasonable amount of time.
-[TODO: Maybe justify a bit more?]
-
-A rational censor will enable the set of censorship systems such that the above equation is maximized given every potential set of circumvention systems.
-
-[TODO: Dig into the base rate fallacy, and expound on that with an equation based expansion that fits in the above model]
 
@@
 \section{Real world observations}
+\label{real}
 
 [TODO - a bunch of case studies]
+ ,
+[Important to hit: recent OBFS entropy attack, Iran study that shows slowdown, China, DNS/IP censorship, DNSSEC failure]
 
@@
 TODO
+
+\chapter{Theory}
+\label{theory}
+
+We begin with a basic model - an adversary will engage in the censorship of service $x$ if $B_x - C_x > 0$, where $B_x$ is the average benefit per user of engaging in censorship of service $x$ and $C_x$ is the average cost of engaging in censorship of service $x$.
+We will refine this formula by switching to a focus on censorship techniques - $(b_{x,1} + b_{x,2} + ...
++ b_{x,n}) - C_x > 0$, where $b_{x,n}$ is the average benefit per user of censoring service $n$ using method $x$.
+A censor will engage in any censorship method where the average benefit reaped by censoring \emph{any} desired services using that method is greater than the cost.
+Also note that these benefits and costs are based on how they are \emph{perceived} by the censor, not by an objective, bird-eye view of good and bad, and they may account for a variety of benefits/cost, including direct financial costs, but also including less tangible value such as "stability".
+
+We now note that each method may only stop a fraction of users accessing a service using a method - so a more realistic formulation would be $(u_{x,1}*b_{x,1} + u_{x,2}*b_{x,2} + ...
++ u_{x,n}*b_{x,n}) - C_x > 0$, where $u_{x,n}$ is the fraction of users accessing service $n$ that are blocked from accessing service $n$ using method $x$.
+
+We will now break down cost further.
+$C_x = f_x + m_x$ - where $f_x$ is the fixed cost per user of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$ per user.
+We will drop $f_x$ from further consideration (IE, $C_x = m_x$) - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost averages to $0$ over the long run.
+We will now explore the marginal cost of $x$.
+Censorship tools may slow down "good" traffic, and they may erroneously block access to good services.
+Therefore, $C_x = s_x*i_x + (u_{x,1}*c_{x,1} + u_{x,2}*c_{x,2} + ...
++ u_{x,n}*c_{x,n})$, where $c_{x,n}$ is the average cost of blocking service $n$ per user, $u_{x,n}$ is the same as above, $s_x$ is the average fraction of the total value of unblocked traffic retained (due to the reduction in speed caused by enabling method $x$),\footnote{Note that an adversary may engage in multiple stages of filtering, so some subsets of unblocked traffic may experience no slowdown, while some might experience more.
+For the purposes of our analysis, we can use the average across all allowed traffic.}, and $i_x$ is the value per user of access to all unblocked sites.
+Combining the above, we see
+$(u_{x,1}*b_{x,1} + u_{x,1}*b_{x,2} + ... + u_{x,n}*b_{x,n}) - s_x*i_x + (c_{x,1} + c_{x,2} + ...  + c_{x,n}) > 0$, or, more succinctly:
+\begin{equation}
+-s_x*i_x + \sum_{s=1}^{n}u_{x,s}*v_{x,s} > 0
+\end{equation}
+where $v_{x,s} = b_{x,s} - c_{x,s}$.
+
+We could conclude here if a censor engaged in censorship solely using a singular method of censorship - however, censors engage in multiple methods of censorship, and the benefit of successfully blocking a site is not distributed multiple times if it's blocked by multiple methods, the benefit is only achieved based on new users blocked by a method, or, in short, a singular censorship system $x$ will be implemented if:
+\begin{equation}
+-s_x*i_x + \sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} > 0
+\end{equation}
+Note that all variables are the same, except $i_x$ is now the value per user of access to all unblocked sites prior to enabling censorship system $x$ and $\Delta u_{x,s}$ is the change in the fraction of users who can access service $s$ after enabling $x$.
+
+We have now established an equation used to determine if a censor will enable an individual system, taking existing systems (or lack thereof) as a given.
+This is not reflective of reality, where a rational censor will evaluate \emph{all} of their active and potential circumvention systems in conjunction.
+
+The valuation of a system consisting of censorship systems $1$ through $m$ is as follows:
+\begin{equation}
+\sum_{x=1}^{m}\sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} - i_{x} * \prod_{x=1}^{m}s_x
+\end{equation}
+All variables are the same as previously, except $i_x$ is the value per user of access to all unblocked sites again, $s_x$ is the average fraction of the total value of unblocked traffic retained after enabling all systems $y$ with $0\leq y<x$, and $\Delta  u_{x,s}$ change in fraction of all users blocked using method $x$ that were not already blocked after enabling all systems $y$ with $0\leq y<x$.
+We will define $x=0$ such that this "censorship" system is the null (non-existent) censorship system, and therefore $s_0 = 1$, and $u_{0,s} = 0$.
+
+We assert that a censor is picking from a number of censorship systems that is small enough such that the censor can evaluate the above equation for every possible set of censorship systems in every permutation such that each set only has one of each censorship system in a reasonable amount of time.
+[TODO: Maybe justify a bit more?]
+
+A rational censor will enable the set of censorship systems such that the above equation is maximized given every potential set of circumvention systems.
+
+[TODO: Dig into the base rate fallacy, and expound on that with an equation based expansion that fits in the above model]
+
+[TODO: Walk through one example using this]
 
@@
 
+[TODO: Finish this section]
+
 \chapter{System evaluation}
@@
 
-\chapter{Conclusion}
+\chapter{Conclusions}
 
@@
 
-\appendices  % Indicates that appendices follow.
-% If there's only one, use \appendix instead.
+[Could use salmon stuff still, even if not perfect, especially since we are not an anonymity system]
 
-\chapter{Sample appendix}
-SAMPLE
-\section{Sample section}
-SAMPLE
-
-\chapter{Second sample appendix}
-SAMPLE
+[Killer app/other uses/etc]
 

### 2023-02-27 paper.tex
Work it

@@
 In an ideal world, all of these entities would run the same algorithms and would move traffic in a content-agnostic fashion, but we do not live in an ideal world.
-A variety of confounding factors result in a web that looks very different in practice from idealized theory: malicous entities use the web to perform attacks, bugs cause unforseen issues to arise, entities want to tightly control traffic and content in their network, among other complicating factors.
+Various confounding factors result in a web that looks drastically different in practice from idealized theory: malicious entities use the web to perform attacks, bugs cause unforeseen issues to arise, entities want to tightly control traffic and content in their network, among other complicating factors.
 
-The more complicated web that actually exists leads to a variety of issues that don't arise in pure networking theory, one of which is \emph{censorship circumvention}.\footnote{\emph{See} \ref{circumvention} for our full definition and further discussion.} Censorship circumvention arises because some network-controlling entities choose to engage in censorhip.
-Censorship has become a loaded term in the current political context, and we do \emph{not} mean the coloquial usage of censorship.
+The more complicated web that exists in the real world leads to issues that do not arise in pure networking theory, one of which is \emph{censorship}.
+Censorship has become a loaded term in the current political context, and we do \emph{not} mean the colloquial usage of censorship.
 Censorship, as we discuss it, refers to entities censoring web traffic (either through complete blocking or other manipulation) at nodes (frequently routers) in the network(s) that they control.
-Censorship may be done for a variety of reasons - most censors will claim they are solely removing malicious traffic, however, an entity may operate their own definition of malicious which would differ from coloquial usage of the term.
+Censorship may be done for a variety of reasons - most censors claim they are solely removing malicious traffic, however, an entity may use their own definition of malicious which differs from colloquial usage of the term.
 We see some entities that choose to block social media sites, news sources, or any site that they deem as block-worthy.
 Censors have a variety of justifications for their actions: economic protectionism, removing unsavory content, blocking dangerous content, maintaining law and order, and others.
-We see this and ask our key reasearch question:
+We see this and ask our key research question:
 \begin{keyq}
@@
 \end{keyq}
-This is a very broad question - to be able to address it in a scientific manner we must refine it and break out some more specific and actionable research questions.
+This is a very broad question - to be able to address it in a concrete and scientific manner we must refine it and break out more specific and actionable research questions.
 To circumvent censorship, we must address what it is:
@@
 \begin{question}
-What do existing censorship systems look like?
+What do censorship systems look like?
 \end{question}
@@
 \begin{keyq}
-Can we circumvent existing censorship systems? If so, how?
+Can we circumvent censorship systems? If so, how?
 \end{keyq}
 
-As we discussed above, we note that some entity is performing censorship - censorship is not occuring spontaneously.
+As we discussed above, we note that some entity is performing censorship - censorship is not occurring spontaneously.
 Systems are not deployed magically, and do not arise without a concerted action undertaken by an entity.
+These systems are being designed and implemented by some entity to achieve a specific purpose.
 This leads us to our next research question:
@@
 Previous work has spent significant time defining adversaries in order to posit new methods of circumvention, and we define our adversary in a similar fashion.
-Our adversary has unlimited resources, constrained only by physics and algorithmic limitations.\footnote{\emph{See} \ref{adversary} for our full definition and further discussion.} In our model, we also assume there is at least 1 location \emph{not} under the control of any censoring adversary.
-Our theoretical adversary is informed by both real world observations and theories developped in prior work.
+Our adversary has unlimited resources, constrained only by physics and algorithmic limitations.\footnote{\emph{See} \ref{adversary} for our full definition and further discussion.} In our model, we also assume there is at least 1 location \emph{not} under the control of any censoring adversary.[XREF sphere of influence] Our theoretical adversary is informed by both real world observations and theories developed in prior work.
 In the real world, we frequently see adversaries perform basic censorship actions, such as blocking IPs and DNS resolutions.
 We also see adversaries taking more extreme actions, such as performing fingerprinting attacks or other techniques involving deep packet inspection (DPI).\footnote{\emph{See} \ref{real} for our exploration of real-world adversaries.} In theory, we see formulations that involved the adversary either attacking specific protocols [TODO e.g.
-xref Wang discussion] or employing a specific method of attack.
+xref Wang discussion] or employing a specific technique of attack applicable to several systems.
 [TODO: xref Salmon discussion] In prior work, most adversarial actions are discussed in a vacuum - rather than looking at how an adversary may choose the full setup of a censorship suite, adversary modelling focuses on an adversary trying to tackle just one method of circumvention, and the broader picture is ignored.
@@
 This model of an adversary is a novel contribution and allows for rooting research in the field to both existing theory and the real world.
-With an adversary and adequate model defined, we can further refine the key research question tackled in this paper:
+With an adversary and model defined, we can further refine the key research question tackled in this paper:
 
@@
 
-We cannot immeadiately answer this question - as we see in our model, an adversary has some utility function.
-Using both observations and a hypothetical, consider a utility function where an adversary does not care about blocking access to sites they deem legitimate (i.e., blocking an allowed site has a utility to the adversary of $0$), but they strongly do not want anyone to access a non-legitimate site (i.e.
+We cannot immediately answer this question - as we see in our model, an adversary has some utility function.
+We start by bounding our potential utility functions with one of the [edge possibilites]: Consider a utility function where an adversary does not care about blocking access to sites they deem legitimate (i.e., blocking an allowed site has a utility to the adversary of $0$), but they strongly do not want anyone to access a non-legitimate site (i.e.
 a user accessing a non-legitimate site has a utility of $-\infty$).
-This adversary would simply disable the internet.
+This adversary would simply shut down \emph{all} traffic.
 This would provide them with $0$ utility, which is their maximal utility.
-In fact, in some instances censors have had real-world utility functions that result in actions like this, though those instances have been short lived.[CITE] However, in practice, we see that no censor has continually provided 0 internet access - indicating that real world adversaries place a non-zero value on allowing access to legitimate sites, but they might place a very negative value on some non-legitimate sites.
-The key point is that, while we can come up with infinite theoretical utility functions, we should focus on real and realistically possible utility functions, leading us to one research question:
+In fact, in some instances censors have had real-world utility functions that result in actions like this, though those instances have been short lived.[CITE] However, in practice, we also see that no censor has continually provided 0 internet access - indicating that real world adversaries place a non-zero value on allowing access to legitimate sites, but they might place a very negative value on some non-legitimate sites.
+While we can come up with infinite theoretical utility functions, we should focus on real and realistically possible utility functions, leading us to another research question:
 
@@
 We find that most censors, in most circumstances, wish to censor users while providing access to acceptable sites.
-We also see that censors frequently fail to block some traffic that they could block using some known methods.
-This brings us to the key concept of \emph{collateral damage}.
-A censor can employ censorship techniques to stop some traffic that they wish to stop, but many methods of censorship would result in shutting down access to some allowed traffic as a result of using those methods.
-We see several real world adversaries who employ some similar and some differing techniques, with varying defgrees of collateral damage.
-As such, we refine our key research question:
+We also see that censors frequently fail to block some traffic that they could block using known methods.
+This brings us to the key concept of \emph{collateral damage}.[TODO: xref] A censor can employ censorship techniques to stop some traffic that they wish to stop, [but many methods of censorship would result in shutting down access to some allowed traffic].
+We see several real world adversaries each employ unique censorship systems with varying degrees of collateral damage.
+[TODO: Add a bit more] As such, we refine our key research question:
 
@@
 In practice, we see that the circumvention system Snowflake is currently working under all adversaries.
-However, while, for analysis sake, we fix a utility function at a given point in time, adversaries \emph{do} change their utility functions, and new censorship systems arise.
-Adversaries are frequently trying to develop new systems, and so we cannot assume a system will last indefinitely.\footnote{We note that a circumvention system which is provably able to survive could arise, however \emph{all} existing tools either do not have a strong scientific proof (e.g.
-Snowflake) or proofs are frequently constrained beyond a reasonable point (e.g.
-Obfs).} We choose to look ahead to an adversary either adopting a different, more constraining utility function or the development of a new censorship system that is more optimal than currently deployed systems.
+However, adversaries \emph{do} change their utility functions, and new censorship systems arise.
+Adversaries are trying to develop new systems, and so we cannot assume a system will function as well as it does currently indefinitely.\footnote{We note that a circumvention system which is provably able to survive could arise, however existing tools either do not have a strong scientific proof (e.g.
+Snowflake [XREF]) or proofs are frequently constrained to such an extent that they work in theory, but neglect an attack outside of the scope of that theory (e.g.
+Obfs and the bridge distribution problem [XREF]).} We look ahead to a potential adversary either adopting a different utility function with a higher toleracne for collateral damage or the development of a new censorship system that is more optimal than currently deployed systems.
 This leads us to our next research question:
@@
 
-We note that stronger censorship in the near future may emerge due to either a utility function less sensitive to collateral damage, or using a more advanced censorship system.
 We review related work and synthesize some possibilities for actions an adversary may take in the future.
-We focus on currently succesful circumvention techniques, and provide some methods of censorship an adversary may engage in to further restrict these systems using existing techniques that might increase collateral damage.
+We focus on currently successful circumvention techniques, and provide some methods of censorship an adversary may engage in to further restrict these systems using existing techniques that might increase collateral damage.
 We also explore censorship techniques, and we observe that deep packet inspection and bridge enumeration are the two broad techniques an adversary may use in a more advanced censorship system.
@@
 
-We address this question head on. We design and build a system to do this.
+We address this by combining several observations which result from the answers to our previous questions:
+\begin{itemize}
+  \item A realistic censorship system should be based upon \emph{real} censorship systems and \emph{real} adversaries, with some further constraining beyond real-world adversaries allowed.
+  \item Circumvention systems that thwart real censorship systems exist both in theory and the real world, but that some functional systems \emph{primarily} exist in theory.
+    \begin{itemize}
+    \item There must be some limitation(s) to systems that only exist in theory.
+    \item Real world circumvention systems function by combining a bootstrapping channel and a circumvention channel.
+      \begin{itemize}
+      \item We see that bootstrapping is generally done using a high value channel that has reasonable latency, but may have low bandwidth.
+      \item We see that the circumvention channels must have reasonable latency \emph{and} bandwidth.
+      \end{itemize}
+    \end{itemize}
+\end{itemize}
+We build our system based upon the following principles derived from those observations:
+\begin{itemize}
+  \item A novel circumvention system must be functional.
+    \begin{itemize}
+    \item Functional means both not blocked, and having practical latency and bandwidth.
+    \item The system must function both when bootstrapping and relaying traffic.
+    \end{itemize}
+  \item A novel circumvention system must improve upon an existing system in at least one of the following ways:
+    \begin{itemize}
+    \item Increase collateral damage\footnote{This also includes using a novel method of circumvention, though that is not required - a system may be iterative.}
+    \item Scalability
+    \item Usability
+    \end{itemize}
+  \item A novel circumvention system should not face the limitations that primarily theoretical systems face
+\end{itemize}
 
-[TODO: Remove old intro]
+We choose to build a system that iterates on the success of Snowflake.
+We do this by using the same type of channel (WebRTC) to relay our main traffic.
+We also use a bootstrapping channel in a similar fashion to Snowflake.\footnote{We use a stand-in in our demo system.} This is where the similarities end.
+We build our system as a standalone P2P system, which allows us to improve on Snowflake in several ways:
 
-We also provide an overview of the state of peer to peer (P2P) networking, focusing on successful project operating in the real world.
-We provide a deeper dive into the Interplanetary File System (IPFS) and the underlying networking library, LibP2P.
-These programs are used extensively in out proposed system.
+\begin{itemize}
+  \item Increase collateral damage
+    \begin{itemize}
+    \item As a P2P system, adversaries need to perform censorship solely at international gateways, but they must also expand their censorship apparatus to cover intranational traffic as well.
+This drastically increases collateral damage, as adversaries have not been observed performing notable on-the-wire censorship within their borders.
+Adding intranational censorship will take any collateral damage that would have occurred solely to international endpoints and expands that to intranational end points as well.
+    \item We use IPFS as a library for our channel, and any blocking of our system would result in blockking IPFS as well, blocking a protocol that is in use across the globe.
+    \end{itemize}
+  \item Scalability
+    \begin{itemize}
+    \item Snowflake is entirely volunteer run, and has encountered scalability issues in the real world in the last year as a result.
+There is some evidence that the volunteer base is largely saturated, and growing the network further is difficult.
+We address this by having every user of our network \emph{also} act as a provider of our network.
+This means that each node in our network does not solely drain system bandwidth, instead they use some bandwidth and also provide some bandwidth.\footnote{A user may provide more bandwidth than they use, however, an exploration of average users of our network would require numerous real users.}
+    \end{itemize}
+  \item Usability
+    \begin{itemize}
+    \item We build our system as a standalone system, allowing users to use our system without the reduction of usability that comes with using Tor.\footnote{We emphasize that users could potentially use our system to access Tor, but they are not required to, increasing usability in instances where a user does not need anonymity.}
+    \item Our system can be transferred and run as a singular HTML file in any relatively up to date web browser.
+    \end{itemize}
+\end{itemize}
+[END TODO: If any of these remain single bullet points, switch to `ITEM: TEXT` instead of nested lists]
 
-Having outlined what is and has succeeded in censorship circumvention in both the real world and theory, we propose a system that addresses the flaws of the current cutting edge systems.
-We call this system CN.
-[TODO: fn code name] We discuss the architecture of this system, putting a particular emphasis on the underlying data structure and network topology.
+In practical terms, we build a system by using LibP2P and IPFS as libraries, and building a dynamically updating tree which contains metadata and pointers to hashes of files - which can then be retrieved over IPFS.
+We also outline some attacks a censor may take against IPFS, and we modify our usage of IPFS to mitigate these attacks.
+We build both golang and python libraries which are used to access and update the aformentioned tree, as well as to establish uplink channels.
+We build a benchmarking app on top of our network, as well as some demo apps [TODO: list final apps].
 
-We build this system and build a benchmarking tool and other apps on top of this system.
-We use this benchmarking tool to show that the system functions with strong performance.
-We then begin to simulate a censor based upon theoretical and real world adversaries, and then benchmark the system again, showing that even under severely censored circumstances, we are able to maintain [adequate/good/strong] performance.
-We also explore what regions of the world would have to operate in more censored circumstances at present.
+We then use our benchmarking app to demonstrate how our system works in a variety of conditions, based upon some of the potential actions a censor may take:
+\begin{itemize}
+  \item No censorship
+  \item Censoring fixed nodes
+  \item Censoring fixed nodes \emph{and} all traffic except WebRTC and email.
+\end{itemize}
 
-We then conclude and offer some opportunities for future work.
+The second test is in line with how adversaries currently function in the real world, and the third test posits an adversary which has a utility function more extreme than existing adversaries.
+We note that we do not spend extensive time looking at DPI attacks on WebRTC - this is because these are generally fingerprinting attacks, and because we use the built in WebRTC from standard web browsers, there should not be any fingerprint distinct from standard usage of WebRTC.\footnote{An adversary may perform \emph{content} fingerprinting attacks, however, we relegate these attacks to future work, and note that adversaries do not appear to do these in practice, and they have false positive rates too high for usage.
+[CITE] [XREF false positives]}
+
+[TODO: Explore speed results]
+
+We then conclude and offer a discussion on ethics of our system and potential future work.[XREF]
+
+[END TODO: Check paragraph indentation]
+[END TODO: Add xrefs throughout]
 
@@
 [TODO - a bunch of case studies]
- ,
+
 [Important to hit: recent OBFS entropy attack, Iran study that shows slowdown, China, DNS/IP censorship, DNSSEC failure]

### 2023-02-27 paper.tex
Intro

@@
 
-The more complicated web that exists in the real world leads to issues that do not arise in pure networking theory, one of which is \emph{censorship}.
+The complicated, real internet leads to issues that do not arise in pure networking theory, one of which is \emph{censorship}.
 Censorship has become a loaded term in the current political context, and we do \emph{not} mean the colloquial usage of censorship.
@@
 Censorship may be done for a variety of reasons - most censors claim they are solely removing malicious traffic, however, an entity may use their own definition of malicious which differs from colloquial usage of the term.
-We see some entities that choose to block social media sites, news sources, or any site that they deem as block-worthy.
-Censors have a variety of justifications for their actions: economic protectionism, removing unsavory content, blocking dangerous content, maintaining law and order, and others.
+We see some entities that choose to block social media sites, news sources, or any site that they deem block-worthy.
+Censors have a variety of justifications for their actions such as economic protectionism, removing unsavory content, blocking dangerous content, and maintaining law and order.
 We see this and ask our key research question:
@@
 This is a very broad question - to be able to address it in a concrete and scientific manner we must refine it and break out more specific and actionable research questions.
-To circumvent censorship, we must address what it is:
-
+To circumvent censorship, we must address what censorship is:
 \begin{question}
@@
 
-We explore previous work to answer this question.[XREF] [TODO: Add more] This allows us to refine our key question:
+We explore previous work to answer this question.
+In the real world, we frequently see adversaries perform basic censorship actions, such as blocking IPs and DNS resolutions.
+We also see adversaries taking more extreme actions, such as performing fingerprinting attacks or other techniques involving deep packet inspection (DPI).\footnote{\emph{See} \ref{real} for our exploration of real-world adversaries.} In theory, we see formulations that involve either attacking specific protocols [TODO e.g.
+xref Wang discussion] or employing a specific technique of attack applicable to several systems.
+[TODO: xref Salmon discussion] This allows us to refine our key question to focus on concrete systems:
 
@@
 Our adversary has unlimited resources, constrained only by physics and algorithmic limitations.\footnote{\emph{See} \ref{adversary} for our full definition and further discussion.} In our model, we also assume there is at least 1 location \emph{not} under the control of any censoring adversary.[XREF sphere of influence] Our theoretical adversary is informed by both real world observations and theories developed in prior work.
-In the real world, we frequently see adversaries perform basic censorship actions, such as blocking IPs and DNS resolutions.
-We also see adversaries taking more extreme actions, such as performing fingerprinting attacks or other techniques involving deep packet inspection (DPI).\footnote{\emph{See} \ref{real} for our exploration of real-world adversaries.} In theory, we see formulations that involved the adversary either attacking specific protocols [TODO e.g.
-xref Wang discussion] or employing a specific technique of attack applicable to several systems.
-[TODO: xref Salmon discussion] In prior work, most adversarial actions are discussed in a vacuum - rather than looking at how an adversary may choose the full setup of a censorship suite, adversary modelling focuses on an adversary trying to tackle just one method of circumvention, and the broader picture is ignored.
+In prior work, most adversarial models are highly focused - rather than looking at how an adversary may choose the full setup of a censorship suite, adversary modelling focuses on an adversary trying to tackle just one method of circumvention, and the broader picture is ignored.
 We formulate a model for evaluating an adversaries actions that looks at the \emph{whole} of their censorship apparatus:\footnote{\emph{See} \ref{theory} for more details and the derivation.}
@@
 
-This model of an adversary is a novel contribution and allows for rooting research in the field to both existing theory and the real world.
+This model of an adversary is a novel contribution and allows for rooting research in the field to both the real world and existing theory.
 With an adversary and model defined, we can further refine the key research question tackled in this paper:
@@
 \begin{keyq}
-Can we circumvent our adversaries censorship systems?
+Can we circumvent our adversary's censorship systems? If so, how?
 \end{keyq}
@@
 We cannot immediately answer this question - as we see in our model, an adversary has some utility function.
-We start by bounding our potential utility functions with one of the [edge possibilites]: Consider a utility function where an adversary does not care about blocking access to sites they deem legitimate (i.e., blocking an allowed site has a utility to the adversary of $0$), but they strongly do not want anyone to access a non-legitimate site (i.e.
+We start by bounding our potential utility functions with one of the [edge possibilites]: Consider a utility function where an adversary does not care about blocking access to sites they deem legitimate (i.e., blocking an allowed site has a utility to the adversary of $0$), but they feel strongly that no user should access a non-legitimate site (i.e.
 a user accessing a non-legitimate site has a utility of $-\infty$).
@@
 This would provide them with $0$ utility, which is their maximal utility.
-In fact, in some instances censors have had real-world utility functions that result in actions like this, though those instances have been short lived.[CITE] However, in practice, we also see that no censor has continually provided 0 internet access - indicating that real world adversaries place a non-zero value on allowing access to legitimate sites, but they might place a very negative value on some non-legitimate sites.
+In fact, in some instances censors have had real-world utility functions that result in actions like this, though those instances have been short lived.[CITE] However, in practice, we also see that no censor has continually provided 0 internet access - indicating that real world adversaries place a positive, non-zero value on allowing access to legitimate sites, even if they place a very negative value on some non-legitimate sites.
 While we can come up with infinite theoretical utility functions, we should focus on real and realistically possible utility functions, leading us to another research question:
@@
 \begin{keyq}
-Can we circumvent our adversaries censorship system, given a realistic adversarial utility function?
+Can we circumvent our adversaries censorship system, given a realistic adversarial utility function? If so, how?
 \end{keyq}
@@
 First, if we \emph{only} look at \emph{current} censorship apparatuses and real-world adversarial utility functions, we could conclude and say yes - based entirely on previous work.
-In practice, we see that the circumvention system Snowflake is currently working under all adversaries.
+In practice, we see that the circumvention system Snowflake is currently working under all real-world adversaries.
 However, adversaries \emph{do} change their utility functions, and new censorship systems arise.
@@
 Snowflake [XREF]) or proofs are frequently constrained to such an extent that they work in theory, but neglect an attack outside of the scope of that theory (e.g.
-Obfs and the bridge distribution problem [XREF]).} We look ahead to a potential adversary either adopting a different utility function with a higher toleracne for collateral damage or the development of a new censorship system that is more optimal than currently deployed systems.
+Obfs and the bridge distribution problem [XREF]).} We look ahead to a potential adversary either adopting a different utility function with a higher tolerance for collateral damage or the development of a new censorship system that is more optimal than currently deployed systems.
 This leads us to our next research question:
@@
 We discuss some directions that these techniques may proceed in.
-[TODO: More] We use this to refine our overarching research question into an approachable question:
+[TODO: More + be more concrete] We use this to refine our overarching research question into an approachable question:
 
 \begin{question}
-Can we circumvent our adversaries existing or potential censorship systems, given a realistic adversarial utility function?
+Can we circumvent our adversaries existing or potential censorship systems, given a realistic adversarial utility function? If so, how?
 \end{question}
@@
   \item A realistic censorship system should be based upon \emph{real} censorship systems and \emph{real} adversaries, with some further constraining beyond real-world adversaries allowed.
-  \item Circumvention systems that thwart real censorship systems exist both in theory and the real world, but that some functional systems \emph{primarily} exist in theory.
+  \item Circumvention systems that thwart real censorship systems exist both in theory and the real world, but some functional systems \emph{primarily} exist in theory.
     \begin{itemize}
     \item There must be some limitation(s) to systems that only exist in theory.
-    \item Real world circumvention systems function by combining a bootstrapping channel and a circumvention channel.
+    \item The practicality of real-world systems is crucial.
+    \end{itemize}
+  \item Circumvention systems function by combining a bootstrapping channel and a circumvention channel.
     \begin{itemize}
-      \item We see that bootstrapping is generally done using a high value channel that has reasonable latency, but may have low bandwidth.
-      \item We see that the circumvention channels must have reasonable latency \emph{and} bandwidth.
-      \end{itemize}
+    \item We see that successful bootstrapping is generally done using a high value channel that has reasonable latency, but may have low bandwidth.
+    \item We see that the circumvention channels that are used in the real world must have reasonable latency \emph{and} bandwidth.
     \end{itemize}
@@
 \begin{itemize}
-  \item A novel circumvention system must be functional.
+  \item A novel circumvention system should be functional.
     \begin{itemize}
@@
     \end{itemize}
-  \item A novel circumvention system must improve upon an existing system in at least one of the following ways:
+  \item A novel circumvention system should improve upon an existing system in at least one of the following ways:
     \begin{itemize}
@@
     \begin{itemize}
-    \item As a P2P system, adversaries need to perform censorship solely at international gateways, but they must also expand their censorship apparatus to cover intranational traffic as well.
+    \item In existing systems, adversaries need to perform censorship solely at international gateways, but our system requires them to expand their censorship apparatus to cover intranational traffic as well.
 This drastically increases collateral damage, as adversaries have not been observed performing notable on-the-wire censorship within their borders.
-Adding intranational censorship will take any collateral damage that would have occurred solely to international endpoints and expands that to intranational end points as well.
-    \item We use IPFS as a library for our channel, and any blocking of our system would result in blockking IPFS as well, blocking a protocol that is in use across the globe.
+Adding intranational censorship will take any collateral damage that would have occurred solely to international endpoints and expands that to intranational end points as well.[TODO: mention/cite that most traffic is intranational]
+    \item We use IPFS as a library for our channel, and any blocking of our system would result in blocking IPFS as well, blocking a protocol that is in use across the globe.
     \end{itemize}
@@
 We address this by having every user of our network \emph{also} act as a provider of our network.
-This means that each node in our network does not solely drain system bandwidth, instead they use some bandwidth and also provide some bandwidth.\footnote{A user may provide more bandwidth than they use, however, an exploration of average users of our network would require numerous real users.}
+This means that each node in our network does not solely drain system bandwidth, instead they use some bandwidth and also provide some bandwidth.\footnote{A user may provide more bandwidth than they use, however, an exploration of the bandwidth provided vs the bandwidth used of users of our network would require numerous real users.}
     \end{itemize}
@@
 We also outline some attacks a censor may take against IPFS, and we modify our usage of IPFS to mitigate these attacks.
-We build both golang and python libraries which are used to access and update the aformentioned tree, as well as to establish uplink channels.
+We build both Golang and Javascript libraries which are used to access and update the aformentioned tree, as well as to establish uplink channels.
 We build a benchmarking app on top of our network, as well as some demo apps [TODO: list final apps].
@@
 The second test is in line with how adversaries currently function in the real world, and the third test posits an adversary which has a utility function more extreme than existing adversaries.
-We note that we do not spend extensive time looking at DPI attacks on WebRTC - this is because these are generally fingerprinting attacks, and because we use the built in WebRTC from standard web browsers, there should not be any fingerprint distinct from standard usage of WebRTC.\footnote{An adversary may perform \emph{content} fingerprinting attacks, however, we relegate these attacks to future work, and note that adversaries do not appear to do these in practice, and they have false positive rates too high for usage.
+We note that we do not spend extensive time looking at DPI attacks on WebRTC - this is because these are generally fingerprinting attacks, and because we use the built in WebRTC from standard web browsers, there should not be any fingerprint distinct from standard usage of WebRTC.\footnote{An adversary may perform \emph{content} fingerprinting attacks, however, we relegate these attacks to future work, and note that adversaries do not appear to do these in practice in the realm of censorship, and they have false positive rates too high for usage.
 [CITE] [XREF false positives]}
@@
 [END TODO: Add xrefs throughout]
+[END TODO: Add cites throughout]
 

### 2023-05-16 paper.tex
Typing

@@
 
-[TODO: Rework]
-
-Present censorship circumvention is currently built on two techniques: proxying traffic \emph{out} of the adversaries sphere of influence, and providing access to those proxies.
-If you can provide access to a proxy, then using existing proxying technology is trivial.
-The majority of censorship circumvention theory is, therefore, focused on providing access to proxies.
+[TODO: Maybe cut? Or just point to next section]
 
@@
 
-\section{Prior techniques}
+\chapter{Related Work}
+
+Censorship circumvention has developped over several decades.
+Originating out of anonymity research, censorship resistance is a less difficult problem than full anonymity,\footnote{Anonymity generally requires censorship resistance (or a non-censoring adversary) to bootstrap.} and has become a topic studied on it's own independent of anonymity.\footnote{Though anonymity and censorship are distinct problems and are often approached independently in research, there is notable interaction between the two fields - many censorship circumvention techniques target the pluggable transport (PT) spec for deployment of censorship systems.
+The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence.
+
+[TODO: Add in new paper re: obfs]
+
+\section{Prior proxying theory and techniques}
+
+Most proxying techniques fall into one of three broad categories: looking like an unknown protocol, mimicing an existing protocol, or using an existing protocol as intended.
+Of these, mimicry was eliminated as a functional technique.
+Houmansadr et al established requirements that a mimicry system must meet to succeed - the imitated protocol must be mimiced in full, the imitation protocol must react properly to errors and network conditions, the imitation protocol must have traffic typical of the imitated protocol, and the imitation protocol must imitate artifacts from implementations of the imitated protocol properly.\cite{parrot} They continued by showing that none of the cutting edge mimicry protocols of the time were able to fulfill these requirements.\footnote{The authors explore SkypeMorph, StegoTorus, and CensorSpoofer - they quickly find passive attacks for these transports.\cite{skypemorph}\cite{stegotorus}\cite{censorspoofer}\cite{parrot}} The authors finally show that even with the initial attacks they find, hypothetical, improved transports that patch those would still fail as there are attacks that could not be prevented when imitating a proprietary protocol.
+The authors have a damning conclusion that has held until today: "unobservability by imitation is a fundamentally flawed approach, unlikely to ever suceed due to the daunting list of reqirements that an imitator must satisfy.
+The failure of all proposed [imitation] circumvention systems to achiever unobservability confirms this conclusion."\cite{parrot}
+
+[TODO: Break down into high bandwidth/low bandwidth]
 
@@
 
-[TODO: Mention parrot is dead]
-
 TODO
-
-[TODO: Mention Tor PTs independently of specific methods]
 
@@
 
-[TODO: Mention stego]
-
 [TODO: Discuss fingerprinting, including contemporary examples w/ snowflake]
 
-\subsection{[Point to point obfuscation]}
+\subsection{Unknown Protocols}
 
@@
 \subsection{High-reliability channels}
+
+[TODO: Mention stego]
 

### 2023-05-18 paper.tex
Writing, some refs

@@
 \section{Prior proxying theory and techniques}
+\label{prior}
 
-Most proxying techniques fall into one of three broad categories: looking like an unknown protocol, mimicing an existing protocol, or using an existing protocol as intended.
+Most proxying techniques fall into one of three broad categories: looking like an unknown protocol, mimicing an existing protocol/service, or using an existing protocol/service as intended.
 Of these, mimicry was eliminated as a functional technique.
@@
 
-[TODO: Break down into high bandwidth/low bandwidth]
+Beyond mimicry, most systems fall into either looking like an unkown protocol, or using an existing protocol as intended.
+We can also break down proxying techniques into low-bandwidth and high-bandwidth techniques.
+High-bandwidth, on it's own, is generally preferred to lower bandwidth, however, in censorship circumvention other tradeoffs exist - most notably, the cost of censoring many low-bandwidth channels is higher than many high bandwidth channels.
+These channels frequently use an existing protocol/service as intended, which means that censoring these channels may require taking down a high value service, e.g.
+if a circumvention system uses email effectively, it may only be possible to block by blocking email.
+We discuss several examples of both low and high bandwidth channels in the following sections.
+[TODO: Discuss the notion of signalling]
+
+[TODO: Discuss DPI, xref real world section]
+
+[TODO: Discuss fingerprinting, including contemporary examples w/ snowflake]
 
@@
 
-TODO
-
 [TODO: Do mention some things like shadowsocks that are in use but are even further from academics]
 
-[TODO: Discuss fingerprinting, including contemporary examples w/ snowflake]
+\subsection{High-bandwidth channels}
 
-\subsection{Unknown Protocols}
+Several high-bandwidth channels have been created, and at least two are in active use in real world situations.
+We first discuss channels that attempt to look like an unknown protocol, and then discuss ones that attempt to use existing protocols and services as intended.
 
-TODO
+\subsubsection{Unknown protocols}
 
-\subsubsection{OBFS and Scramblesuit}
+As censorship apparati developped, DPI began being used.
+DPI caused issues for several protocols - as it was able to selectively censor unencrypted or partially encrypted data streams based on parameters that a censor sets.
+[TODO: xref DPI] OBFS2 was developped by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI.
+Obfs2 was vulnerable however, as a passive MITM [TODO: make sure this is defined earlier] could listen and decrypt the transport.\cite{obfs3} In addition to DPI, active probing arose as a technique that earlier circumvention techniques could be detected (and subsequently blocked) using.
+Active probing involves an adversary sending data of their choice to a server of their choice, and observing the response.
+They may potentially continue probing depending on the response.
+[TODO: Give an example] obfs2 was vulnerable to active probes as well.\footnote{And, indeed, it was actively probed by China.\cite{TODO https://gitlab.torproject.org/legacy/trac/-/issues/8591}}
 
-TODO
+obfs3 was developped to patch issues with obfs2.
+The main issue it addressed was the ability to perform passive decryption of the flow.
+This was done by using a custom Diffie-Hellman handshake.\cite{obfs3} obfs3 was still vulnerable to active probing.\cite{scramblesuit} Scramblesuit was designed to address this flaw, as well as several other identified tells of obfs3.\cite{scramblesuit} Scramblesuit defined a strong adversary, similar to the one proposed in this paper, and aimed to tackle active probing while also introducing basic traffic shaping via padding as well as inter-arrival times - introducing the concept of a polymorphic traffic shape for a protocol.\footnote{Polymorphic shaping is a promising defense for circumventors.
+The basic concept is that if every server has a unique traffic shape, then even if an adversary is able to identify a single server effectively, they will be unable to use that information in blocking other servers.
+This concept has not been fully exploited by a published circumvention technique at the time of writing.} Scramblesuit introduced the addition of a shared secret distributed \emph{out-of-band} to enable these improvements.
+From a usability and deployment standpoint, this was not a drastic departure from previous techniques: the older transports required basic info such as the bridge's IP address to be transmitted out of band, and this simply extended the amount of out-of-band information that needs to be transmitted by several characters.\footnote{Usability and deployment were specific considerations in the development of Scramblesuit - it was designed to be used by Tor and in the real world.\cite{scramblesuit}} Scramblesuit consists of two phases: a uniform diffie-hellman key exchange, and then a data exchange phases.
+
+Scramblesuit performed some evaluation, however, they identified a key problem with evaluating circumvention techniques that affects all protocols that attempt to look like unknown protocols: evaluation is very difficult due to the lack of good datasets and effective experimental setups.
+The authors opted to show that the transport differs from the carried protocol (in this case, Tor).\cite{scramblesuit} Regardless, Scramblesuit became widely deployed.\footnote{Notably, inter-arrival time manipulation was off by default and could optionally be turned on.
+This was because inter-arrival time manipulation introduced significant overhead.
+With hindsight, we have seen other issues with Scramblesuit and have not seen issues caused by inter-arrival time manipulation being disable.
+These other issues are discussed directly below.}
+
+Scramblesuit had notable overhead from it's andshake phases.
+The UniformDH used modlar exponentiation, which is an expensive operation.\cite{obfs4} Additionally, Scramblesuit was vulnerable to some MitM attacks if the attacker knew the shared secret.\cite{obfs4} obfs4 replaced the UniformDH with use of Tor's ntor handshake, with obfuscation done by Elligator 2.\cite{obfs4} obfs4 is still in use today, and is one of the main two circumvention techniques used for circumventing censorship in the Tor browser.
+
+[TODO: Wang et al, new censorship]
 
@@
 
-[TODO: Mention this w/ raven, bridgedb, etc]
+[TODO: Mention this w/ sweet, raven, bridgedb, etc]
 
@@
 
-[Important to hit: recent OBFS entropy attack, Iran study that shows slowdown, China, DNS/IP censorship, DNSSEC failure]
+[TODO: Important to hit: recent OBFS entropy attack, Iran study that shows slowdown, China, DNS/IP censorship, DNSSEC failure]
 
@@
 \subsection{The bridge distribution problem}
+\label{distribution}
 
@@
 
-Earlier, [TODO: xref] we discussed a variety of censorship circumvention systems.
+In Section \ref{prior} we discussed a variety of censorship circumvention systems.
 Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to achieve, working techniques we may use, and a theory for our systems function.
@@
 \begin{itemize}
-  \item The bridge distribution problem [TODO: Xref]
+  \item The bridge distribution problem (\emph{see} Section \ref{distribution})
   \item Scalability

### 2023-05-22 paper.tex
werk

@@
 Originating out of anonymity research, censorship resistance is a less difficult problem than full anonymity,\footnote{Anonymity generally requires censorship resistance (or a non-censoring adversary) to bootstrap.} and has become a topic studied on it's own independent of anonymity.\footnote{Though anonymity and censorship are distinct problems and are often approached independently in research, there is notable interaction between the two fields - many censorship circumvention techniques target the pluggable transport (PT) spec for deployment of censorship systems.
-The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence.
+The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\label{pt}\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence.
 
@@
 We discuss several examples of both low and high bandwidth channels in the following sections.
-[TODO: Discuss the notion of signalling]
+
+Lower and higher bandwidth transports can be combined to work together and gain benefits of both.
+Most higher-bandwidth channels require conveying some less-fixed \emph{out-of-band} information (e.g.
+an IP address) to use a higher bandwidth channel.
+Low bandwidth channels, generally being more costly to block, still require out-of-band information, but frequently this information is valid as long as the channel is functional.
+For example, an email-based channel will require a recipient email address, but this email address could be effectively constant due to the way email itself functions.
+As a result, an email based channel may effectively hard-code this information in the transport itself, allowing the channel to be used as long as you have the code and an adversary that does not block email.
+This highly resiliant but low-bandwidth setup may be used to bootstrap higher bandwidth channels.
+An email channel may be used to convey an IP address of a point to point high bandwidth channel, and could be used for important messages or to get another channel if the recieved point-to-point channel is blocked.
+With this synergy between the low and high bandwidth channels, discussing and understanding both is crucial to a modern circumvention system.
 
 [TODO: Discuss DPI, xref real world section]
+
+[TODO: Discuss IP blocking]
 
@@
 
+[TODO: Discuss false positives and base-rate fallacy]
+
 \subsection{High-bandwidth channels}
@@
 Several high-bandwidth channels have been created, and at least two are in active use in real world situations.
-We first discuss channels that attempt to look like an unknown protocol, and then discuss ones that attempt to use existing protocols and services as intended.
+We first discuss channels that attempt to look like an unknown protocol (UP), and then discuss ones that properly use protocols (PUP).
 
@@
 
-Scramblesuit had notable overhead from it's andshake phases.
-The UniformDH used modlar exponentiation, which is an expensive operation.\cite{obfs4} Additionally, Scramblesuit was vulnerable to some MitM attacks if the attacker knew the shared secret.\cite{obfs4} obfs4 replaced the UniformDH with use of Tor's ntor handshake, with obfuscation done by Elligator 2.\cite{obfs4} obfs4 is still in use today, and is one of the main two circumvention techniques used for circumventing censorship in the Tor browser.
+Scramblesuit had notable overhead from it's handshake phases.
+The UniformDH used modular exponentiation, which is an expensive operation.\cite{obfs4} Additionally, Scramblesuit was vulnerable to some MitM attacks if the attacker knew the shared secret.\cite{obfs4} obfs4 replaced the UniformDH with use of Tor's ntor handshake, with obfuscation done by Elligator 2.\cite{obfs4} obfs4 is still in use today, and is one of the main two circumvention techniques used for circumventing censorship in the Tor browser.
+[TODO: cite] obfs4 requires some out of band info to function - which is done through hard-coding, email, telegram, or domain fronting.
+[TODO: xref]
 
-[TODO: Wang et al, new censorship]
+Even though obfs4 is still functional and in use, that does not mean it is not vulnerable to attack.
+Wang et al demonstrated that obfs4 is vulnerable to entropy based attacks: conventional and often used web protocols, even if encrypted, usually have some control messages unencrypted - e.g.
+TLS and SSH both have unencrypted portions of the header.
+This means that the entropy of these flows is lower than that of obfs4 flows - because obfs4 attempts to look-like-nothing, it ends up looking like a fully encrypted stream with no plaintext, resulting in very high entropy - but, no well known protocol does this.
+By attempting to look like a hypothetical unknown protocol, obfs4 may actually look unique.\cite{wang} Obfs4 can be reliably detected and blocked as a result, with relatively low computational costs.
+There are some drawbacks to this - most notably the base-rate fallacy, discussed in Section \ref{base-rate}.
+This paper was published in 2015, though for over 5 years this attack was not observed by any adversaries.
+In 2021, these attacks were observed on the live internet, discussed further in Section \ref{entropy}.
+
+Obfs4 also faces another problem: the bridge distribution problem, discussed further in Section \ref{bridge}.
+Bridges, once known by an adversary, can be blocked at the IP level, and the software is difficult for basic users to spin up.
+Some of these issues are addressed by Snowflake in Section \ref{snowflake}.
 
@@
 
-\subsection{[P2P and P2P-like]}
+\subsection{Properly using protocols}
 
-TODO
+Several transports attempt to use protocols as intended. Snowflake is in real world usage, and several others have been developed in the literature.
 
 \subsubsection{Snowflake}
+\label{snowflake}
 
-TODO
+Snowflake is a transport designed for usage by the Tor browser,\footnote{Though, it conforms to the PT spec spec, and as such could be used by other systems.
+See Section \ref{PT} for more on PTs.} and is currently in use in the real world.
+Snowflake seeks to offer an alternative way of spinning up proxies compare to obfs and other transports that rely on proxies with fixed IP addresses, as well as using a different transport.
+Snowflake does this by taking advantage of how modern browsers are setup to ease proxy deployment and transport development.
+These concepts were introduced by Flashproxy and other related work.
+Flashproxy defined three key problems that this class of transport must address: how to create proxies, how to rendezvous, and how to actually hide when in use.\cite{flashproxy} Flashproxy addresses proxy creation by allowing volunteers to embed code in their sites that turn any visitor into a proxy for censored users.
+These proxies are ephemeral, and are regular web users, changing up the cost and benefits a censor reaps if they were to be blocked.
+Rendezvous is handled by setting up a well-known connection broker.
+Hiding in use is not explored deeply, but is justified by simply using a frequently used web browser transport (WebSockets).
 
@@
 TODO
+
+\subsubsection{Decoy routing}
+
+[Tapdance]
 
@@
 
-\subsection{Decoy routing}
-
-TODO
-
-\subsubsection{Tapdance}
-
 \subsection{Tunneling and realistic behavior}
@@
 [TODO - a bunch of case studies]
+
+[https://gfw.report/publications/usenixsecurity23/data/paper/paper.pdf]
 

### 2023-05-23 paper.tex
Spelling pass

@@
 
-Censorship circumvention has developped over several decades.
+Censorship circumvention has developed over several decades.
 Originating out of anonymity research, censorship resistance is a less difficult problem than full anonymity,\footnote{Anonymity generally requires censorship resistance (or a non-censoring adversary) to bootstrap.} and has become a topic studied on it's own independent of anonymity.\footnote{Though anonymity and censorship are distinct problems and are often approached independently in research, there is notable interaction between the two fields - many censorship circumvention techniques target the pluggable transport (PT) spec for deployment of censorship systems.
@@
 
-Most proxying techniques fall into one of three broad categories: looking like an unknown protocol, mimicing an existing protocol/service, or using an existing protocol/service as intended.
+Most proxying techniques fall into one of three broad categories: looking like an unknown protocol, mimicking an existing protocol/service, or using an existing protocol/service as intended.
 Of these, mimicry was eliminated as a functional technique.
-Houmansadr et al established requirements that a mimicry system must meet to succeed - the imitated protocol must be mimiced in full, the imitation protocol must react properly to errors and network conditions, the imitation protocol must have traffic typical of the imitated protocol, and the imitation protocol must imitate artifacts from implementations of the imitated protocol properly.\cite{parrot} They continued by showing that none of the cutting edge mimicry protocols of the time were able to fulfill these requirements.\footnote{The authors explore SkypeMorph, StegoTorus, and CensorSpoofer - they quickly find passive attacks for these transports.\cite{skypemorph}\cite{stegotorus}\cite{censorspoofer}\cite{parrot}} The authors finally show that even with the initial attacks they find, hypothetical, improved transports that patch those would still fail as there are attacks that could not be prevented when imitating a proprietary protocol.
-The authors have a damning conclusion that has held until today: "unobservability by imitation is a fundamentally flawed approach, unlikely to ever suceed due to the daunting list of reqirements that an imitator must satisfy.
+Houmansadr et al established requirements that a mimicry system must meet to succeed - the imitated protocol must be mimicked in full, the imitation protocol must react properly to errors and network conditions, the imitation protocol must have traffic typical of the imitated protocol, and the imitation protocol must imitate artifacts from implementations of the imitated protocol properly.\cite{parrot} They continued by showing that none of the cutting edge mimicry protocols of the time were able to fulfill these requirements.\footnote{The authors explore SkypeMorph, StegoTorus, and CensorSpoofer - they quickly find passive attacks for these transports.\cite{skypemorph}\cite{stegotorus}\cite{censorspoofer}\cite{parrot}} The authors finally show that even with the initial attacks they find, hypothetical, improved transports that patch those would still fail as there are attacks that could not be prevented when imitating a proprietary protocol.
+The authors have a damning conclusion that has held until today: "unobservability by imitation is a fundamentally flawed approach, unlikely to ever succeed due to the daunting list of requirements that an imitator must satisfy.
 The failure of all proposed [imitation] circumvention systems to achiever unobservability confirms this conclusion."\cite{parrot}
 
-Beyond mimicry, most systems fall into either looking like an unkown protocol, or using an existing protocol as intended.
+Beyond mimicry, most systems fall into either looking like an unknown protocol, or using an existing protocol as intended.
 We can also break down proxying techniques into low-bandwidth and high-bandwidth techniques.
-High-bandwidth, on it's own, is generally preferred to lower bandwidth, however, in censorship circumvention other tradeoffs exist - most notably, the cost of censoring many low-bandwidth channels is higher than many high bandwidth channels.
+High-bandwidth, on it's own, is generally preferred to lower bandwidth, however, in censorship circumvention other trade-offs exist - most notably, the cost of censoring many low-bandwidth channels is higher than many high bandwidth channels.
 These channels frequently use an existing protocol/service as intended, which means that censoring these channels may require taking down a high value service, e.g.
@@
 As a result, an email based channel may effectively hard-code this information in the transport itself, allowing the channel to be used as long as you have the code and an adversary that does not block email.
-This highly resiliant but low-bandwidth setup may be used to bootstrap higher bandwidth channels.
-An email channel may be used to convey an IP address of a point to point high bandwidth channel, and could be used for important messages or to get another channel if the recieved point-to-point channel is blocked.
+This highly resilient but low-bandwidth setup may be used to bootstrap higher bandwidth channels.
+An email channel may be used to convey an IP address of a point to point high bandwidth channel, and could be used for important messages or to get another channel if the received point-to-point channel is blocked.
 With this synergy between the low and high bandwidth channels, discussing and understanding both is crucial to a modern circumvention system.
@@
 
-As censorship apparati developped, DPI began being used.
+As various censorship apparatuses developed, DPI began being used.
 DPI caused issues for several protocols - as it was able to selectively censor unencrypted or partially encrypted data streams based on parameters that a censor sets.
-[TODO: xref DPI] OBFS2 was developped by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI.
-Obfs2 was vulnerable however, as a passive MITM [TODO: make sure this is defined earlier] could listen and decrypt the transport.\cite{obfs3} In addition to DPI, active probing arose as a technique that earlier circumvention techniques could be detected (and subsequently blocked) using.
+[TODO: xref DPI] OBFS2 was developed by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI.
+Obfs2 was vulnerable however, as a passive MitM [TODO: make sure this is defined earlier] could listen and decrypt the transport.\cite{obfs3} In addition to DPI, active probing arose as a technique that earlier circumvention techniques could be detected (and subsequently blocked) using.
 Active probing involves an adversary sending data of their choice to a server of their choice, and observing the response.
@@
 
-obfs3 was developped to patch issues with obfs2.
+obfs3 was developed to patch issues with obfs2.
 The main issue it addressed was the ability to perform passive decryption of the flow.
@@
 This concept has not been fully exploited by a published circumvention technique at the time of writing.} Scramblesuit introduced the addition of a shared secret distributed \emph{out-of-band} to enable these improvements.
-From a usability and deployment standpoint, this was not a drastic departure from previous techniques: the older transports required basic info such as the bridge's IP address to be transmitted out of band, and this simply extended the amount of out-of-band information that needs to be transmitted by several characters.\footnote{Usability and deployment were specific considerations in the development of Scramblesuit - it was designed to be used by Tor and in the real world.\cite{scramblesuit}} Scramblesuit consists of two phases: a uniform diffie-hellman key exchange, and then a data exchange phases.
+From a usability and deployment standpoint, this was not a drastic departure from previous techniques: the older transports required basic info such as the bridge's IP address to be transmitted out of band, and this simply extended the amount of out-of-band information that needs to be transmitted by several characters.\footnote{Usability and deployment were specific considerations in the development of Scramblesuit - it was designed to be used by Tor and in the real world.\cite{scramblesuit}} Scramblesuit consists of two phases: a uniform Diffie-Hellman key exchange, and then a data exchange phases.
 

### 2023-05-23 paper.tex
Some writing

@@
 
-[TODO: Others]
+[TODO: Others?]
 
@@
 
+Snowflake took the concepts presented in Flashproxy and iterated on them and deployed them widely.
+Snowflake switched the transport in use from Websockets to WebRTC.\footnote{WebRTC is a commonly used standard across a variety of digital applications.
+Notably, it is supported in the web browser via Javascript.
+WebRTC is used for a variety of tasks, including video, audio, and other data, and is used by most video/audio chatting applications.} WebRTC was designed for P2P usage, and an ecosystem of utility protocols and standards has arisen around it, including tools to do NAT puncturing and establishing connections between users in various, differing networks, which provides significant utility to Snowflake compared to Websockets.\footnote{Snowflake uses Interactive Connectivity Establishment (ICE) to connect users behind NATs.
+ICE uses STUN and TURN relays as tools to ensure a connection can be established.
+STUN is commonly used and is available widely on the web, and is required for innocuous services to function as well.
+TURN services are less common, as they require significantly more infrastructure and are not generally permissionless like STUN.\cite{snowflake-tech}} Snowflake iterated on the rendezvous by creating a broker.
+The broker is reached by using a high-reliability, low-bandwidth channel (domain fronting in practice, see Section \ref{domain fronting} for further details).
+The broker is able to match volunteers and users to each other, in order to provide service.
+Snowflake then makes several usability improvements, setting up usage such that a client can fail over to a backup volunteer should their primary one fail, as well as maintaining a session across numerous volunteers using Turbotunnel.\footnote{Turbotunnel is a concept most completely implemented in Snowflake.
+It is a session/reliability layer that exists above an obfuscation layer.\cite{turbotunnel} Many transports exist above a reliability layer (e.g.
+obfs4 uses TCP), so adding an additional reliablilty layer adds notable overhead.
+In some cases, such as Snowflake, where the transports used are very unreliable, the benefits outweigh the costs.
+Turbotunnel also addresses several other issues - for example, a censor could close any long-running connections to disable obfs4.\cite{turbotunnel} Without any internal reliability layer, the connection must restart from scratch, effectively preventing usage of the transport, even if an adversary did not identify a specific bridge.}
+
 [TODO: Add a diagram which will be used later to start to show "modifications" from the snowflake model to get our system]
@@
 
-\subsubsection{MassBrowser}
-
-TODO
-
 \subsubsection{Decoy routing}
 
-[Tapdance]
+[TODO: Tapdance] [TODO: Cirripede] [TODO: Telex]
+
+\subsubsection{MassBrowser}
 
@@
 
-[TODO: Mention stego]
-
-TODO
+Most of the previously mentioned channels require either a shared secret (e.g.
+obfs4) or a rendezvous (e.g.
+snowflake).
+Distributing a secret or setting up a rendezvous cannot be punted indefinitely, and as such there must be a way to perform these actions, even in a censored region.
+High-reliability channels may be used for these actions.
+Though all high-reliability channels vary in numerous ways, they can generally be characterized as low-bandwidth, highly available, and sticky addresses.
+Each of these characteristics is important for differing reasons.
+Most of these channels are considered low-bandwidth - were they not, we could simply use the channel as the primary transport.\footnote{And, this can still be done, see section \ref{meek} for some discussion of using one for a full connection.} A channel must be highly available, or it could not be relied upon.
+Finally, sticky addresses (e.g.
+an email address, a social media handle) are important, as a more temporary address would leave us punting on distributing a secret or setting up a rendezvous channel - a sticky address allows one (or several) addresses to be hard-coded in a transports default config for the long run, allowing for usage without acquiring more info out-of-band.
 
 \subsubsection{Domain fronting}
+\label{domain fronting}
 
@@
 
+[Raven] [Sweet]
+
 [TODO: Mention this w/ sweet, raven, bridgedb, etc]
 
-\subsection{Tunneling and realistic behavior}
+\subsubsection{Steganography}
 
-\subsubsection{Raven}
+\subsubsection{Realistic behavior}
 

### 2023-05-25 paper.tex
Added some sections

@@
 
+[TODO: add stuff on bridge enumeration]
+
 \subsubsection{Decoy routing}
@@
 
+\subsubsection{CacheBrowsing}
+
+[TODO: Discuss cachebrowser]
+
 \subsubsection{MassBrowser}
+
+Massbrowser is a P2P circumvention system.
+Massbrowser was designed to address flaws of existing systems - specifically, that systems that rely on limited, well known bridges (such as obfs4) are easily blocked, [TODO: xref] certain systems are expensive (such as using domain fronting for a full web session), many systems offer poor quality of service due to poor scalability, several systems force a user to add additional overhead to their web session by using another tool such as Tor,\footnote{Many web users do not care about anonymity and would prefer simply to get around web blocks regardless of anonymity guarentees.} and many systems (particularly decoy routing) are difficult to deploy.\cite{massbrowser}
+
+Massbrowser attempts to address these flaws by relying on volunteer proxies in both censored and uncensored regions to circumvent censorship.
+These proxies are supposed to be regular web users.
+A Massbrowser session begins by connecting to a central broker (via domain fronting) to match users with a proxy.
+These proxies then connect (after performing NAT punching) and use a modified version of obfs to communicate.
+
+On top of this, because proxies may be in censored regions, MassBrowser maintains a complex whitelist on a per proxy basis - if a proxy is in a censored region, it cannot acquire certain content for the connected circumvention user.\footnote{MassBrowser simply tunnels through Tor in this case - creating a chicken vs egg problem.} This is costly - measurements must be performed to maintain this whitelist, and it assumes accesibility to CacheBrowser and Tor, and the maintinence of this whitelist does not benefit from economies of scale.
+On top of this, proxy providers may heavily tailor the loads they wish to support, employing whitelisting, destination whitelisting (which varies from the basic whitelisting behavior previously mentioned), loads, and other options.\cite{massbrowser} On top of this, MassBrowser uses custom software - either GUI software or a modified version of Firefox.
 
@@
 
-TODO
+Domain fronting arose through exploiting the differences between the plaintext and encrypted portions of an HTTPS connection sequence.
+Though implementation varies slightly depending on the provider, at a high level domain fronting is accomplished by setting up a server behind the networks of a key piece of internet infrastructure,\footnote{Usually large providers of either direct services (e.g.
+Google) or CDNs (e.g.
+Cloudflare).} and initializing DNS and server name indication (SNI) using a whitelisted domain from that same provider.
+After that, the HTTP host header is set to the proper destination (as this field is encrypted by TLS, the censor is unable to see it).
+Domain fronting is relatively simple to setup, and does not require direct participation from the provider (though, they cannot explicitly disallow it).\cite{domain fronting} Domain fronting is used extensively, from full sessions,\cite{meek} to bootstrapping in Snowflake, or passing out of band secrets for Obfs4.
+
+Domain fronting works well for small tasks, however, domain fronting costs a significant amount of money, proportional to bandwidth and machines used, limiting it's uses for more heavyweight tasks.
+Additionally, while it can be setup without cooperation from providers, they may choose to disable it.
+Google, Cloudflare, Amazon, and others have disabled it or take actions against users performing it.
+Currently, Azure (Microsoft) does not block meek, and Snowflake uses both fastly and Google's AMP cache to perform signalling.
+
+https://gitlab.torproject.org/tpo/anti-censorship/pluggable-transports/snowflake/-/blob/main/client/README.md
+https://gitlab.torproject.org/tpo/applications/tor-browser-build/-/blob/main/projects/common/bridges_list.meek-azure.txt
+
+[https://petsymposium.org/2015/papers/03_Fifield.pdf]
+[https://signal.org/blog/looking-back-on-the-front/]
+[https://arstechnica.com/information-technology/2018/04/google-disables-domain-fronting-capability-used-to-evade-censors/]
 

### 2023-05-26 paper.tex
More writing

@@
 
-Domain fronting works well for small tasks, however, domain fronting costs a significant amount of money, proportional to bandwidth and machines used, limiting it's uses for more heavyweight tasks.
+Domain fronting works well for small tasks, however, domain fronting costs a significant amount of money, proportional to bandwidth and machines used, limiting it's uses for more heavyweight tasks (particularly proxying full web sessions).
 Additionally, while it can be setup without cooperation from providers, they may choose to disable it.
@@
 
-[Raven] [Sweet]
-
-[TODO: Mention this w/ sweet, raven, bridgedb, etc]
+Email has become essential to modern life in a way few other protocols have.
+It functions as a good channel because it is generally encrypted using TLS, and it is widely available with third party clients allowed for most major servers, including companies such as Google and Yahoo.
+A censor would have to block a major email provider entirely if they wanted to prevent users using it as a channel.
+This has been exploited by several circumvention systems, including Sweet, Raven, and Tor's Bridgedb.
+
+Sweet introduced the concept of channels with high availability guarentees.
+Sweet chooses to use email to build on the concepts presented in "The Parrot is Dead" by Housmandr et al.\cite{parrot} Using the email protocol properly is trivial to do given the wide variety of available codebases and the numerous email servers in existence on the web.
+Sweet tunnels a full connection via email - however, it comes with increased latencies as a result.
+Sweet is explicitly vulnerable to traffic analysis, as most users do not tunnel a full web connection via email.\cite{sweet}
+
+Raven introduces the concept of behavioral realism to a circumvention channel.
+Raven offers an exemplar implementation written using email as the transport.
+This was done by using the authors actual emailing patterns and machine learning to craft a realistic sending pattern for the transport.
+As a result, Raven suffers from being drastically slower and higher latency than Sweet, to the extent it is usable for very little besides basic signalling.\footnote{Realistic behaviour is likely necessary for more transports beyond email to remain secure against a strong adversary in the long run, however, this is an area of open research.}\cite{raven}
+
+In reality, no censors appear to be doing behavioral analysis of web traffic - however, that does not mean they could not start doing so.
+In reality, it's likely that email could be used in a manner more strict than Sweet and less strict than Raven for small messages correlated with a real person accessing a system - ie, when a user is actually touching their web browser, shooting off and recieving a few email might not conform to a precisely real behavior, but it might be close enough that a censor could not detect it without significant false positives causing the blocking of regular email traffic.
+
+In the real world, Tor uses email as a channel for distributing obfs4 bridges.
+This works to succesfully provide users with bridges, though this runs into the bridge distribution problem limiting effectiveness, discussed in \ref{distribution}.
 
@@
 
-\subsubsection{Realistic behavior}
+[TODO]
+
+\subsubsection{Other channels}
+
+Tor uses telegram to distribute obfs4 bridges.\cite{telegram}
 
@@
 
+Peer to peer networking has existed since the early web, but has fallen into and out of favor over time.
+The web was originally envisioned as many small networks interlinking to form the full web, but as the internet developped, many services such as email, web hosting, server provision, etc.
+have become centralized by large companies.
+For example, if two users message on a site like Twitter, their messages are going to Twitter, being stored on Twitter, and passed to the recipient via Twitter, rather than directly (even if both users have no desire for Twitter to have access to the content).
+Generally, unless a user is delibrately using a specific P2P protocol, only select activities are augmented with P2P connections (usually voice/videochat and gaming).
+The most notable uses of P2P networks are torrents, some cryptocurrencies, and IPFS.
+
+BitTorrent originated in 2001.\footnote{We use torrent and BitTorrent interchangebly throughout this paper.} It was designed to make provision of common, large files more effecient.
+"When a file is made available using HTTP, all upload cost is placed on the hosting machine.
+With BitTorrent, when multiple people are downloading the same file at the same time, they upload pieces of the file to each other.
+This redistributes the cost of upload to downloaders, (where it is often not even metered), this making hosting a file with a potentially unlimited number of downloaders affordable."\cite{torrent} Publishers of files choose to make their file available as a torrent, where anyone with the proper software can download it.\footnote{Nowadays, even web browsers can use extensions to access torrents.\cite{webtorrent}} At launch, users would make .torrent files available - these files contained basic info about a file - the size, name, a tracker,\footnote{"Trackers are responsible for helping downloaders find each other.
+They speak a very simple protocol layered on top of HTTP in which a downloader sends information about what file it’s downloading, what port it’s listening on, and similar information, and the tracker responds with a list of contact information for peers which are downloading the same file."\cite{torrent}} and hashing info.\footnote{Since then, magnet links have become an option as well.
+These are specifically formatted links that provide the data needed to bootstrap a torrent download without pulling a file separate from the magnet link.}\cite{torrent} The original uploader must send out at least one copy of the file being shared (or it must already be distributed out of band), but after that, the file can be reconstructed from anyone sharing the torrent rather than the original provider.
+Users acquire peers in a random manner from trackers, ensuring robustness.
+Bittorrent divides files into small pieces of fixed size, which allows users to upload before a download is completed, and these pieces are known via their SHA1 hash, ensuring file integrity.
+Peers announce what files they have, resulting "in less than a tenth of a percent bandwidth overhead [while] reliably utiliz[ing] all available upload capacity.\cite{torrent} BitTorrent
+
+https://support.brave.com/hc/en-us/articles/360035025231-What-extensions-are-built-into-Brave-
+https://www.bittorrent.org/bittorrentecon.pdf
+https://www.usenix.org/legacy/events/imc05/tech/full_papers/guo/guo.pdf
+
+[TODO: Torrents, Crypto, ???]
+
+\subsection{IPFS}
+
+IPFS is a P2P system where files are shared based on the content of the files, rather than URLs (uniform resource locaters).
+URLs point to specific locations, which may host whatever those in charge of the location choose to serve, assuming you can route to the specific location to acquire a file.\footnote{Routing to blocked content is indeed the primary problem that we seek to solve in the censorship circumvention sphere.} Users of IPFS (either directly or an app that performs content acquisition under the hood using IPFS) request specific files, based upon the hash of the files.
+
 TODO
 
-[TODO: Torrents, Crypto, ???]
-
-\subsection{IPFS}
-
-TODO
+https://arxiv.org/pdf/2208.05877.pdf
+https://arxiv.org/pdf/2205.14927.pdf
+https://arxiv.org/pdf/1407.3561.pdf
+https://arxiv.org/pdf/2102.12737.pdf
 

### 2023-06-01 paper.tex
werk

@@
 
-https://gitlab.torproject.org/tpo/anti-censorship/pluggable-transports/snowflake/-/blob/main/client/README.md
-https://gitlab.torproject.org/tpo/applications/tor-browser-build/-/blob/main/projects/common/bridges_list.meek-azure.txt
-
-[https://petsymposium.org/2015/papers/03_Fifield.pdf]
-[https://signal.org/blog/looking-back-on-the-front/]
-[https://arstechnica.com/information-technology/2018/04/google-disables-domain-fronting-capability-used-to-evade-censors/]
-
 \subsubsection{Email}
@@
 [TODO - a bunch of case studies]
-
-[https://gfw.report/publications/usenixsecurity23/data/paper/paper.pdf]
 
@@
 The most notable uses of P2P networks are torrents, some cryptocurrencies, and IPFS.
+
+\subsection{BitTorrent}
+\label{torrent}
 
@@
 Bittorrent divides files into small pieces of fixed size, which allows users to upload before a download is completed, and these pieces are known via their SHA1 hash, ensuring file integrity.
-Peers announce what files they have, resulting "in less than a tenth of a percent bandwidth overhead [while] reliably utiliz[ing] all available upload capacity.\cite{torrent} BitTorrent
-
-https://support.brave.com/hc/en-us/articles/360035025231-What-extensions-are-built-into-Brave-
-https://www.bittorrent.org/bittorrentecon.pdf
-https://www.usenix.org/legacy/events/imc05/tech/full_papers/guo/guo.pdf
+Peers announce what files they have, resulting "in less than a tenth of a percent bandwidth overhead [while] reliably utiliz[ing] all available upload capacity.\cite{torrent} BitTorrent generally prioritizes the "rarest" pieces of a file first, based upon which peers have which pieces.\footnote{Though, users can customize the ordering if they choose to do so.
+Selecting the rarest first both ensures a full file is available, and it maximizes the sharing speed of a torrent, as once the rarest piece is acquired by a second peer, that peer can share that piece further.} BitTorrent reaches a relatively optimum end result through a mechanism known as choking: BitTorrent downloads from several peers - the fastest known peers - and optimistically probes for faster peers as well.\cite{torrent} BitTorrent effectively uses "tit-for-tat" exchange mechanisms to allow for a relatively distributed system which generally reaches optimal or near-optimal outcomes.
+
+[TODO: mention more swap algorithms, see ipfs paper]
 
 [TODO: Torrents, Crypto, ???]
+
+[TODO: MainlineDHT]
+
+\subsection{Crypto currencies}
+
+[TODO]
 
@@
 URLs point to specific locations, which may host whatever those in charge of the location choose to serve, assuming you can route to the specific location to acquire a file.\footnote{Routing to blocked content is indeed the primary problem that we seek to solve in the censorship circumvention sphere.} Users of IPFS (either directly or an app that performs content acquisition under the hood using IPFS) request specific files, based upon the hash of the files.
-
-TODO
-
-https://arxiv.org/pdf/2208.05877.pdf
-https://arxiv.org/pdf/2205.14927.pdf
-https://arxiv.org/pdf/1407.3561.pdf
-https://arxiv.org/pdf/2102.12737.pdf
+A key assumption of IPFS is that no nodes are priveleged or trusted specially, which leads to several design decisions based upon prior work.
+At it's core, IPFS provides basic utilities for identities, networking, routing, file exchange, object acquisition, file ststem management, and basic naming capabilities.\cite{ipfs}
+
+A node in IPFS can be thought of as having an identity.\footnote{This identity can be refreshed as often as a user wants, though there is some benefit to using the same identity in the long run.} This identity is very basic: it's simply a lone node ID, which is the hash of a nodes public key.
+These keys are built using primitives from the S/Kademlia DHT.\footnote{S/Kademlia is an iteration of the Kademlia DHT.
+Kademlia DHT is designed to minimize the number of hops needed to learn the location of a desired address.\cite{kademlia} A large network of 10,000,000 nodes could be searched with 20 hops on average - queries are resolved in $\lceil log_2(n) \rceil$, where $n$ is the number of nodes in the network.\cite{ipfs} Additionally, Kademlia has low overhead for control messages, and had prior large usage.\cite{ipfs} S/Kademlia builds on Kademlia to reduce Sybil attacks by requiring some proof of work work (signatures) and allows for lookups in a more adversarial network - "S/Kademlia achieves a [lookup success] rate of .85 even with an adversarial fraction as large as half of the nodes."\cite{ipfs} S/Kademlia assumes an adversary similar to one which we do - an adversary can manipulate packets, do observation, etc.
+They can also generate an arbitrary number of adversarial nodes, and might attempt an eclipse attack.\cite{skademlia} The proof of work for generating a node-id is based upon putting some basic constraints on node-ids (e.g.
+certain bits must be 0), and therfore generating a valid node-id is doable for users, but is a configurable variable to stop an adversary.\cite{skademlia}} IPFS is designed to be transport agnostic - this is done using a \emph{multiaddr}, which is an identifier similar to a URL in terms of hierarchy, but providing networking information.
+For routing, IPFS must allow nodes to find other peers, and the location of specific content.
+IPFS draws on S/Kademlia and Coral DSHT's (distributed sloppy hash table) extensions to Kademlia for this - Coral DSHT notably reduces the overhead needed to find content by allowing for acquisition of just a single peer to acquire content, rather than needing to acquire every peer (hence, the \emph{sloppy} in the name).
+Coral also organizes content into clusters, which allows for more focused searching for content and reducing the latency of the network.
+
+Content acquisition builds on BitTorrent.
+(See Section \ref{torrent} for more.) IPFS effectively uses the file sharing technology of torrenting, but instead of focusing on the pieces contained in a singular torrent, IPFS simply annonces all pieces it has, regardless of the original file.
+This means that files which share content may be acquired from multiple users, even if they don't have the exact same file as the user looking for the content (e.g.
+a user may be seeking a music album, but they may acquire a song from that album from a user who only has that song).
+A notable change from BitTorrent, BitSwap (the name of the content swapping protocol of IPFS) also encourages acquisition of generally rare files that users want, as by decoupling desired files from a torrent, users are incentivized to provide content that providers of the content they want are in search of, which results in a spread of rarer, more desired files in order to recieve better download speeds.\cite{ipfs}
+
+IPFS builds a Merkle DAG on top of the DHT and content swapping technology.
+This DAG links via hashes of content - a generalization of the Git data structure.\cite{ipfs} Using this dag of hashes, IPFS has \emph{unique} identification of any objects, it is tamper resistent, and it allows for easy deduplication.\cite{ipfs} Content can be acquired using a very basic path format: /ipfs/<HASH>/<PATH TO OBJECT>.
+This format allows for easy integration into existing file systems, and for minor changes to allow for web browser usage (set up as: ipfs://<HASH>/<PATH TO OBJECT>).
+Users can add any object to the DHT, and may choose to \emph{pin} an object - marking it as an object that should be kept for the long run.
+Files are represented similar to Git files, with some minor additions added to improve performance.
+These changes include fast size lookups, deduplication of large files, and organizing commits into a tree.\cite{ipfs} A Git object can actually be converted to IPFS without losing any info, but not vice-versa.
+
+So far, all of IPFS has been presented as immutable objects with a mutable networking structure, however, many applications require mutable objects to function properly, but IPFS would not support this, and would require extensive out-of-band communication in order to run anything using IPFS.
+A basic, mutable file addressing schema was introduces to provide every node-key to publish a single mutable file.
+This is done by allowing nodes to insert an arbitrary IPFS hash as /ipns/<Node ID>.
+The only mutable portion of IPFS is the routing system, which is used to publish this by adding the data as a singular, small metadata value.\cite{ipfs}
+
+IPFS has been in use for several years, and has been used to run some services and provide some data on the web.
+[TODO: any censorship circumvention uses?] It has been implemented in both Golang and Javascript (with other languages in various states of completion), and is available in some prominent web browsers (Brave and Opera).\cite{ipfs-measure} The current version of IPFS uses a CID (content identifier) to point to objects - this is a variant of the hashes used to point to object.
+These CIDs include a multibase prefix - a prefix used to indicate the base the encoding used, a version identifier, a codec identifier (e.g.
+protobuf, JSON, etc), and a \emph{multihash} - a hah that indicates the hash algorithm used, and the length of the hash.\cite{ipfs-measure} IPFS uses a multiaddress to provide network addresses of peers - a flexible structure that allows conveying a full network address by first outlining the peer, their network protocol (and any data needed to use), the transport layer, and any additional transports that may reside on top of that.\cite{ipfs-measure} A couple sample multiaddresses are /ip4/<ip address>/tcp/<PORT>/ipfs/<Node ID> and /dns4/site.com/tcp/<PORT>/tls/ipfs/<Node ID>.
+
+[TODO: Add stuff about current transports]
+
+[TODO: Add section on uploading/retrieval]
+
+[TODO: Mention gateways]
+
+[TODO: SFS - self certified filesystems]
+
+[TODO: Add chart from measurement paper]
 

### 2023-06-02 paper.tex
Werk

@@
 We also outline some attacks a censor may take against IPFS, and we modify our usage of IPFS to mitigate these attacks.
-We build both Golang and Javascript libraries which are used to access and update the aformentioned tree, as well as to establish uplink channels.
+We build both Golang and Javascript libraries which are used to access and update the aforementioned tree, as well as to establish uplink channels.
 We build a benchmarking app on top of our network, as well as some demo apps [TODO: list final apps].
@@
 The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\label{pt}\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence.
-
-[TODO: Add in new paper re: obfs]
+Additionally, observing real world censors are frequently observed to see how theory plays out in the real world, as well as if other censorship techniques are in place that have not been suggested in the literature, or were not significantly explored in the literature.
+We discuss real world observations and censorship techniques in \ref{real}.
 
@@
 DPI caused issues for several protocols - as it was able to selectively censor unencrypted or partially encrypted data streams based on parameters that a censor sets.
-[TODO: xref DPI] OBFS2 was developed by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI.
+[TODO: xref DPI] obfs2 was developed by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI.
 Obfs2 was vulnerable however, as a passive MitM [TODO: make sure this is defined earlier] could listen and decrypt the transport.\cite{obfs3} In addition to DPI, active probing arose as a technique that earlier circumvention techniques could be detected (and subsequently blocked) using.
@@
 Some of these issues are addressed by Snowflake in Section \ref{snowflake}.
+
+[TODO: Add in new paper re: obfs]
 
@@
 STUN is commonly used and is available widely on the web, and is required for innocuous services to function as well.
-TURN services are less common, as they require significantly more infrastructure and are not generally permissionless like STUN.\cite{snowflake-tech}} Snowflake iterated on the rendezvous by creating a broker.
+TURN services are less common, as they require significantly more infrastructure and are not generally permissionless like STUN.\cite{snowflake}} Snowflake iterated on the rendezvous by creating a broker.
 The broker is reached by using a high-reliability, low-bandwidth channel (domain fronting in practice, see Section \ref{domain fronting} for further details).
@@
 It is a session/reliability layer that exists above an obfuscation layer.\cite{turbotunnel} Many transports exist above a reliability layer (e.g.
-obfs4 uses TCP), so adding an additional reliablilty layer adds notable overhead.
+obfs4 uses TCP), so adding an additional reliability layer adds notable overhead.
 In some cases, such as Snowflake, where the transports used are very unreliable, the benefits outweigh the costs.
@@
 Massbrowser is a P2P circumvention system.
-Massbrowser was designed to address flaws of existing systems - specifically, that systems that rely on limited, well known bridges (such as obfs4) are easily blocked, [TODO: xref] certain systems are expensive (such as using domain fronting for a full web session), many systems offer poor quality of service due to poor scalability, several systems force a user to add additional overhead to their web session by using another tool such as Tor,\footnote{Many web users do not care about anonymity and would prefer simply to get around web blocks regardless of anonymity guarentees.} and many systems (particularly decoy routing) are difficult to deploy.\cite{massbrowser}
+Massbrowser was designed to address flaws of existing systems - specifically, that systems that rely on limited, well known bridges (such as obfs4) are easily blocked, [TODO: xref] certain systems are expensive (such as using domain fronting for a full web session), many systems offer poor quality of service due to poor scalability, several systems force a user to add additional overhead to their web session by using another tool such as Tor,\footnote{Many web users do not care about anonymity and would prefer simply to get around web blocks regardless of anonymity guarantees.} and many systems (particularly decoy routing) are difficult to deploy.\cite{massbrowser}
 
@@
 
-On top of this, because proxies may be in censored regions, MassBrowser maintains a complex whitelist on a per proxy basis - if a proxy is in a censored region, it cannot acquire certain content for the connected circumvention user.\footnote{MassBrowser simply tunnels through Tor in this case - creating a chicken vs egg problem.} This is costly - measurements must be performed to maintain this whitelist, and it assumes accesibility to CacheBrowser and Tor, and the maintinence of this whitelist does not benefit from economies of scale.
+On top of this, because proxies may be in censored regions, MassBrowser maintains a complex whitelist on a per proxy basis - if a proxy is in a censored region, it cannot acquire certain content for the connected circumvention user.\footnote{MassBrowser simply tunnels through Tor in this case - creating a chicken vs egg problem.} This is costly - measurements must be performed to maintain this whitelist, and it assumes accessibility to CacheBrowser and Tor, and the maintinence of this whitelist does not benefit from economies of scale.
 On top of this, proxy providers may heavily tailor the loads they wish to support, employing whitelisting, destination whitelisting (which varies from the basic whitelisting behavior previously mentioned), loads, and other options.\cite{massbrowser} On top of this, MassBrowser uses custom software - either GUI software or a modified version of Firefox.
@@
 Finally, sticky addresses (e.g.
-an email address, a social media handle) are important, as a more temporary address would leave us punting on distributing a secret or setting up a rendezvous channel - a sticky address allows one (or several) addresses to be hard-coded in a transports default config for the long run, allowing for usage without acquiring more info out-of-band.
+an email address, a social media handle) are important, as a more temporary address would leave us punting on distributing a secret or setting up a rendezvous channel - a sticky address allows one (or several) addresses to be hard-coded in a transports default configuration for the long run, allowing for usage without acquiring more info out-of-band.
 
@@
 After that, the HTTP host header is set to the proper destination (as this field is encrypted by TLS, the censor is unable to see it).
-Domain fronting is relatively simple to setup, and does not require direct participation from the provider (though, they cannot explicitly disallow it).\cite{domain fronting} Domain fronting is used extensively, from full sessions,\cite{meek} to bootstrapping in Snowflake, or passing out of band secrets for Obfs4.
+Domain fronting is relatively simple to setup, and does not require direct participation from the provider (though, they can explicitly disallow it).\cite{domain fronting} Domain fronting is used extensively, from full sessions,\cite{meek} to bootstrapping in Snowflake, or passing out of band secrets for Obfs4.
 
@@
 
-Sweet introduced the concept of channels with high availability guarentees.
+Sweet introduced the concept of channels with high availability guarantees.
 Sweet chooses to use email to build on the concepts presented in "The Parrot is Dead" by Housmandr et al.\cite{parrot} Using the email protocol properly is trivial to do given the wide variety of available codebases and the numerous email servers in existence on the web.
@@
 In reality, no censors appear to be doing behavioral analysis of web traffic - however, that does not mean they could not start doing so.
-In reality, it's likely that email could be used in a manner more strict than Sweet and less strict than Raven for small messages correlated with a real person accessing a system - ie, when a user is actually touching their web browser, shooting off and recieving a few email might not conform to a precisely real behavior, but it might be close enough that a censor could not detect it without significant false positives causing the blocking of regular email traffic.
+In reality, it's likely that email could be used in a manner more strict than Sweet and less strict than Raven for small messages correlated with a real person accessing a system - IE, when a user is actually touching their web browser, shooting off and receiving a few email might not conform to a precisely real behavior, but it might be close enough that a censor could not detect it without significant false positives causing the blocking of regular email traffic.
 
 In the real world, Tor uses email as a channel for distributing obfs4 bridges.
-This works to succesfully provide users with bridges, though this runs into the bridge distribution problem limiting effectiveness, discussed in \ref{distribution}.
+This works to successfully provide users with bridges, though this runs into the bridge distribution problem limiting effectiveness, discussed in \ref{distribution}.
 
@@
 
-[TODO - a bunch of case studies]
+[TODO - a bunch of case studies - lox has several]
 
@@
 
-\subsection{Real world and academic theory}
+\subsection{Observing adversaries}
 
 [TODO - may cut this, but this will be drawing conclusions from our examples above, and comparing those adversaries to the adversary model we outlined, and will transition our discussion to OBFS/the bridge distribution problem]
+
+\subsubsection{Attacks on specific channels}
 
@@
 
+[This subsection is being substatially revised]
+
+We have discussed how channels work on the wire, and how specific protocols may be blocked, but we've deferred discussing the main problem with how many transports like obfs are frequently blocked: an adversary attempts to pose as a non-malicious user and requests access to an obfs bridge.
+They then attempt to probe the bridge, and if the connection succeeds, they block the bridge.
+This can be done quickly and easily by an adversary with resources, allowing for the blocking of numerous bridges if no countermeasures are put in place.
+This problem arises because connection info must be disseminated to users who have no connection to those providing the circumvention techniques.
+There is no trust and effectively no communication between the parties.
+Circumvention must allow all users, even those who do not have technical contacts in areas where the internet is not censored, to access the web to succeed.
+We term this problem \emph{the bridge distribution problem}.
+
+Salmon, proposed by Douglas et al., formalized this notion of bridge distribution
+
+, and formulated one potential solution.\cite{distribution} Nasr et al build on the \emph{college admissions game} framework - a framework used in game theory to analyze and optimize solutions to certain problems of a certain form.
+The game is formulated such that there are effectively two entities - the bridge distributor, and the adversary.
+Nasr et al.
+show that the optimal distribution strategy is to provide clients with arbitrary proxies, but then track which clients request proxies again, and then new proxies are distributed based upon the \emph{deferred acceptance algorithm}.
+This is done until all bridges are full or all clients have a bridge and are no longer requesting bridges.\cite{distribution} The authors then show that an optimal censor will attempt to enumerate bridges, but will delay blocking a bridge to observe it for some time.
+The authors then demonstrate several bridge distributions strategies, but ultimately conclude that if new bridges do not come online often enough, then a censor will inevitably be able to block the full network of proxies.\cite{distribution}
+
+[TODO: Fix the above]
+
+Lox, by Tulloch and Goldberg, builds on Salmon by introducing a social graph based bridge-distribution scheme. They also provide protection for the topology of the social network used.\cite{lox} 
 [TODO - Salmon + that followup paper]
@@
 Peer to peer networking has existed since the early web, but has fallen into and out of favor over time.
-The web was originally envisioned as many small networks interlinking to form the full web, but as the internet developped, many services such as email, web hosting, server provision, etc.
+The web was originally envisioned as many small networks interlinking to form the full web, but as the internet developed, many services such as email, web hosting, server provision, etc.
 have become centralized by large companies.
 For example, if two users message on a site like Twitter, their messages are going to Twitter, being stored on Twitter, and passed to the recipient via Twitter, rather than directly (even if both users have no desire for Twitter to have access to the content).
-Generally, unless a user is delibrately using a specific P2P protocol, only select activities are augmented with P2P connections (usually voice/videochat and gaming).
+Generally, unless a user is deliberately using a specific P2P protocol, only select activities are augmented with P2P connections (usually voice/videochat and gaming).
 The most notable uses of P2P networks are torrents, some cryptocurrencies, and IPFS.
@@
 
-BitTorrent originated in 2001.\footnote{We use torrent and BitTorrent interchangebly throughout this paper.} It was designed to make provision of common, large files more effecient.
+BitTorrent originated in 2001.\footnote{We use torrent and BitTorrent interchangeably throughout this paper.} It was designed to make provision of common, large files more efficient.
 "When a file is made available using HTTP, all upload cost is placed on the hosting machine.
@@
 Users acquire peers in a random manner from trackers, ensuring robustness.
-Bittorrent divides files into small pieces of fixed size, which allows users to upload before a download is completed, and these pieces are known via their SHA1 hash, ensuring file integrity.
+BitTorrent divides files into small pieces of fixed size, which allows users to upload before a download is completed, and these pieces are known via their SHA1 hash, ensuring file integrity.
 Peers announce what files they have, resulting "in less than a tenth of a percent bandwidth overhead [while] reliably utiliz[ing] all available upload capacity.\cite{torrent} BitTorrent generally prioritizes the "rarest" pieces of a file first, based upon which peers have which pieces.\footnote{Though, users can customize the ordering if they choose to do so.
@@
 
-IPFS is a P2P system where files are shared based on the content of the files, rather than URLs (uniform resource locaters).
+IPFS is a P2P system where files are shared based on the content of the files, rather than URLs (uniform resource locators).
 URLs point to specific locations, which may host whatever those in charge of the location choose to serve, assuming you can route to the specific location to acquire a file.\footnote{Routing to blocked content is indeed the primary problem that we seek to solve in the censorship circumvention sphere.} Users of IPFS (either directly or an app that performs content acquisition under the hood using IPFS) request specific files, based upon the hash of the files.
-A key assumption of IPFS is that no nodes are priveleged or trusted specially, which leads to several design decisions based upon prior work.
-At it's core, IPFS provides basic utilities for identities, networking, routing, file exchange, object acquisition, file ststem management, and basic naming capabilities.\cite{ipfs}
+A key assumption of IPFS is that no nodes are privileged or trusted specially, which leads to several design decisions based upon prior work.
+At it's core, IPFS provides basic utilities for identities, networking, routing, file exchange, object acquisition, file system management, and basic naming capabilities.\cite{ipfs}
 
@@
 They can also generate an arbitrary number of adversarial nodes, and might attempt an eclipse attack.\cite{skademlia} The proof of work for generating a node-id is based upon putting some basic constraints on node-ids (e.g.
-certain bits must be 0), and therfore generating a valid node-id is doable for users, but is a configurable variable to stop an adversary.\cite{skademlia}} IPFS is designed to be transport agnostic - this is done using a \emph{multiaddr}, which is an identifier similar to a URL in terms of hierarchy, but providing networking information.
+certain bits must be 0), and therefore generating a valid node-id is doable for users, but is a configurable variable to stop an adversary.\cite{skademlia}} IPFS is designed to be transport agnostic - this is done using a \emph{multiaddr}, which is an identifier similar to a URL in terms of hierarchy, but providing networking information.
 For routing, IPFS must allow nodes to find other peers, and the location of specific content.
@@
 Content acquisition builds on BitTorrent.
-(See Section \ref{torrent} for more.) IPFS effectively uses the file sharing technology of torrenting, but instead of focusing on the pieces contained in a singular torrent, IPFS simply annonces all pieces it has, regardless of the original file.
+(See Section \ref{torrent} for more.) IPFS effectively uses the file sharing technology of torrenting, but instead of focusing on the pieces contained in a singular torrent, IPFS simply announces all pieces it has, regardless of the original file.
 This means that files which share content may be acquired from multiple users, even if they don't have the exact same file as the user looking for the content (e.g.
 a user may be seeking a music album, but they may acquire a song from that album from a user who only has that song).
-A notable change from BitTorrent, BitSwap (the name of the content swapping protocol of IPFS) also encourages acquisition of generally rare files that users want, as by decoupling desired files from a torrent, users are incentivized to provide content that providers of the content they want are in search of, which results in a spread of rarer, more desired files in order to recieve better download speeds.\cite{ipfs}
+A notable change from BitTorrent, BitSwap (the name of the content swapping protocol of IPFS) also encourages acquisition of generally rare files that users want, as by decoupling desired files from a torrent, users are incentivized to provide content that providers of the content they want are in search of, which results in a spread of rarer, more desired files in order to receive better download speeds.\cite{ipfs}
 
 IPFS builds a Merkle DAG on top of the DHT and content swapping technology.
-This DAG links via hashes of content - a generalization of the Git data structure.\cite{ipfs} Using this dag of hashes, IPFS has \emph{unique} identification of any objects, it is tamper resistent, and it allows for easy deduplication.\cite{ipfs} Content can be acquired using a very basic path format: /ipfs/<HASH>/<PATH TO OBJECT>.
+This DAG links via hashes of content - a generalization of the Git data structure.\cite{ipfs} Using this dag of hashes, IPFS has \emph{unique} identification of any objects, it is tamper resistant, and it allows for easy deduplication.\cite{ipfs} Content can be acquired using a very basic path format: /ipfs/<HASH>/<PATH TO OBJECT>.
 This format allows for easy integration into existing file systems, and for minor changes to allow for web browser usage (set up as: ipfs://<HASH>/<PATH TO OBJECT>).
@@
 These CIDs include a multibase prefix - a prefix used to indicate the base the encoding used, a version identifier, a codec identifier (e.g.
-protobuf, JSON, etc), and a \emph{multihash} - a hah that indicates the hash algorithm used, and the length of the hash.\cite{ipfs-measure} IPFS uses a multiaddress to provide network addresses of peers - a flexible structure that allows conveying a full network address by first outlining the peer, their network protocol (and any data needed to use), the transport layer, and any additional transports that may reside on top of that.\cite{ipfs-measure} A couple sample multiaddresses are /ip4/<ip address>/tcp/<PORT>/ipfs/<Node ID> and /dns4/site.com/tcp/<PORT>/tls/ipfs/<Node ID>.
+protobuf, JSON, etc), and a \emph{multihash} - a hash that indicates the hash algorithm used, and the length of the hash.\cite{ipfs-measure} IPFS uses a multiaddress to provide network addresses of peers - a flexible structure that allows conveying a full network address by first outlining the peer, their network protocol (and any data needed to use), the transport layer, and any additional transports that may reside on top of that.\cite{ipfs-measure} A couple sample multiaddresses are /ip4/<ip address>/tcp/<PORT>/ipfs/<Node ID> and /dns4/site.com/tcp/<PORT>/tls/ipfs/<Node ID>.
 
